### 2013-10-21 paper1/paper1.tex
Uploading the LaTeX version of the paper. Sorry for a little delay.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\begin{document}

\title{Re-Allocation of Resources during Releases for Better Outcome in Software Development \titlenote{Copyright information will go here.}}
\numberofauthors{2} %  in this sample file, there are a *total*
\author{
% 1st. author
\alignauthor
Md Tajmilur Rahman\\
       \affaddr{Concordia University}\\
       \affaddr{Montreal, QC H3G 1M8}\\
       \affaddr{438-932-2288, +1}\\
       \email{rupak.karmadhar@gmail.com}
% 2nd. author
\alignauthor
Peter C. Rigby\\
       \affaddr{Concordia University}\\
       \affaddr{Montreal, QC H3G 1M8}\\
       \affaddr{514-848-2424, +1}\\
       \email{peter.rigby@concordia.ca}
}
\date{20 Oct 2013}
\maketitle
\begin{abstract}
This section will be written at the end.
\end{abstract}
\category{K.6.3}{Software Management}{Software Development; Software Resource Management, Resource Reallocation}
\terms{Experimentation, Human Factors, Resource Management, Reallocation.}
\keywords{Resource Reallocation, Software Releases} % NOT required for Proceedings
\section{Introduction}
Software projects are notorious for going over budget and schedule. Rush periods are often gets seen before a major release that turns the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{brooks:mythical}. This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor. Alternatively, the rush may simply be due to inappropriate or unrealistic scheduling. Whatever the reason is it is an obvious. Regardless of the causes, the rush to release stresses developers and often requires developers to work on unusual, high priority or critical areas of the system. In this paper we study how RTR effects project organization and introduces technical debt. The key research questions that we expect to answer with our methodology are as follows:
\begin{enumerate}
\item Do developers work on different areas of the system around the time of release?
\item Are there certain areas of the system that receive increased attention (i. e. do developers focus on a smaller set of files around releases)?
\item Do the areas of code that are modified around the time of release have higher defect densities than code that is modified during normal development?
\end{enumerate}

We observe a reallocation of the resources among the software development teams in a large project to identify that an improper reallocation or inappropriate reorganization causes a disruptive event take place in a software development process. We attempt to identify a project’s different release times and calculate the difference between two consecutive releases to discover which are the new areas have been worked between two consecutive releases. The commit log data that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release. This information will help us to identify the criteria of the resources, their roles, file ownership and nativeness (∆ƞ) in the domain. This knowledge of nativeness (∆ƞ) will guide us understanding the method of reallocation.
Very few research works have been performed regarding the re-allocation of resources.  Robert van Engelen worked for similar kind of a research to understand the resource allocation dynamics across the software projects \cite{datta:pentropy}. He mainly tried to reallocate development resources amongst projects for increasing the satisfactory level of consumer or customer while we are focusing on the impact on code-base like the complexity of script files. Robert proposed a project-entropy metric in his work to understand if there is any limit for a particular reallocation does not lead to user satisfaction. Here entropy is to represent disorder and chaos to understand degradation of software and its inherent complexity. In his work resources may not just be the developers but also can be any other resources necessary for a software project development.
We have organized this paper as follows. In Section 2, we describe some background and motivations followed by some summaries of related works in section 3. Section 4 will describe about the ownership of files and ownership of a set of files or a directories. We will try to understand how native a code-base is to a developer or a development team. In Section 5, some analysis to determine reallocation has been performed in a release or where reallocation needs to be performed will be presented. What changes in nativeness (∆ƞ) occurs after the reallocation. Section 6 will give us the result to show how change in ∆ƞ puts impact on the outcome of a software. Finally section 7 will give us an idea of our future work followed by the conclusion in section 8.

\section{Background}
Sometimes project members with interdependent tasks usually may not communicate effectively; coordination breakdowns occur, which results in integration failures \cite{kwan:stechnical}. There may have lower developers productivity \cite{cataldo:identification, damian:awareness} which may cause inefficient run in the rush moments in a release period. There is a substantial and important body of literature on risk in software engineering. Boehm identified the most important risks encountered by software project managers and described successful risk management practices [6, 7, 8]. Some of the risks identified are related to disruptive events, such as the introduction of a new technology, but most are macro risks associated with running a project, such as developing the wrong functionality. General risk mitigation strategies can be difficult to apply to specific disruptive events. There may be various kinds of disruptive events for example, as a release approaches; developers take shortcuts that introduce technical debt. If it is not repaired, the long term quality of the system will suffer. Another example can be placed, if a lead developer who owns an important part of the code-base leaves and if steps to train other developers were not taken, it will become a dead area of the system and will be difficult to modify and maintain. Also often management reorganizes the developers on a company’s projects, with the result that developers move to code-bases for which they have less experience. The reorganization introduces new perspectives and expertise that can lead to innovation; however, it can also result in a drop in productivity and the unnecessary re-writing of large portions of the system that the new developers do not understand.
In this paper, we plan to take the measures on this last example among them mentioned above. We want to study that proper re-organization or efficient re-allocation of resources based on meaningful criteria can bring better outcome of a software development project by identifying quantify outcomes (Example: number of defects found).

\section{Related Works}
Many people have worked with pretty relevant ideas but I didn't find many very similar to our motivation. Hindle worked on release pattern discovery via partitioning [9]. In this research they proposed a method of observing, analyzing and summarizing the results of metrics of revisions found near releases. They have characterized a project's behavior around the time of major and minor releases. This is done by partitioning the observed activities like the art-effect check-ins around the dates of major and minor releases, then look for reasonable patterns. Hindle divided the revisions in each release in 4 different classes, Source Code, Testing, Building, and Documentations. Actually this paper worked in a reverse way than Cook did [10]. Cook inserted sensors and monitors into the development process but Hindle and Michael analyzed the data to understand what happened in the past.
Another research work we would like to mention was done by  Damian where they have worked on the role of domain knowledge and cross functional communication among the OOS development teams [11]. Posnett did some dual ecological measures of focus in software development [12]. Posnett's measure was for the more general view that unifies developer focus and artifact ownership. Posnett analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from echology to produce a novel and iii) conceptually unified view of measuring focus and ownership. Another study was done by F. Rahman about the authorship of the code-bases in OSS development [13].

\section{Methodology and Data}
This section presents our methodology for discovering information which can give us the idea to get the answers to our research questions. We have collected the development history data of Linux kernel. Actually it is a database containing the all the commit log records by the Linux kernel developers since 2005. We are going to present the steps involved in this process and then we will follow up with an application of our methodology in a case study.
Our methodology can be summarized as: Extracting Data for revisions and releases (Section 4.1); Partitioning the version numbers (Section 4.2); Get time-span between each release (Section 4.3); Calculate developer areas (Section 4.4); Finding code area owners (Section 4.5). Finding merging time and development time within a release period that we found in section 4.1 (Section 4.6).

\subsection{Extracting Data}
... ... ...

\subsection{Partioning Version Numbers}
... ... ...
\subsubsection{Inline (In-text) Equations}
... ... ... ... ... ...

\subsection{Get Time-Span Between Release}
... ... ...

\subsection{Calculate Developers' Area}
... ... ...

\subsection{Finding Code-Area Owners}
... ... ...

\subsection{Extracting Data}
... ... ...
\subsubsection{Display Equations}
... ... ... ... ... ...

\section{Conclusions}
This section will be written at the end.
%\end{document}  % This is where a 'short' article might terminate

\section{Acknowledgments}
... ... ...
\bibliographystyle{abbrv}
\bibliography{paper1} 
\appendix
%Appendix A
\section{Headings in Appendices}
Apendix section will be written later with the following subsections may be:
\subsection{Introduction}
...
\subsection{Background and Motivation}
\subsubsection{Related Works}
...
\subsubsection{Methodology and Data}
...
\subsection{Conclusions}
...
\subsection{Acknowledgments}
...

\subsection{References}
... ...

\balancecolumns
\end{document}

### 2013-10-22 paper1/paper1.tex
updating paper in latex

@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{acm_proc_article-sp}
@@
 
-\title{Re-Allocation of Resources during Releases for Better Outcome in Software Development \titlenote{Copyright information will go here.}}
-\numberofauthors{2} %  in this sample file, there are a *total*
+\title{Re-Allocation of Resources during Releases \titlenote{Copyright information will go here.}}
+\numberofauthors{2}
 \author{
@@
 \category{K.6.3}{Software Management}{Software Development; Software Resource Management, Resource Reallocation}
-\terms{Experimentation, Human Factors, Resource Management, Reallocation.}
+\terms{Experiment, Human Factors, Resource Management, Reallocation}
 \keywords{Resource Reallocation, Software Releases} % NOT required for Proceedings
@@
 Software projects are notorious for going over budget and schedule.
-Rush periods are often gets seen before a major release that turns the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{brooks:mythical}.
+Rush periods are often gets seen before a major release that turns the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{1_brooks}.
 This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor.
@@
 \item Do developers work on different areas of the system around the time of release?
-\item Are there certain areas of the system that receive increased attention (i. e. do developers focus on a smaller set of files around releases)?
+\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?
 \item Do the areas of code that are modified around the time of release have higher defect densities than code that is modified during normal development?
@@
 Very few research works have been performed regarding the re-allocation of resources.
-Robert van Engelen worked for similar kind of a research to understand the resource allocation dynamics across the software projects \cite{datta:pentropy}.
+Robert van Engelen worked for similar kind of a research to understand the resource allocation dynamics across the software projects \cite{2_datta}.
 He mainly tried to reallocate development resources amongst projects for increasing the satisfactory level of consumer or customer while we are focusing on the impact on code-base like the complexity of script files.
@@
 \section{Background}
-Sometimes project members with interdependent tasks usually may not communicate effectively; coordination breakdowns occur, which results in integration failures \cite{kwan:stechnical}.
-There may have lower developers productivity \cite{cataldo:identification, damian:awareness} which may cause inefficient run in the rush moments in a release period.
+Sometimes project members with interdependent tasks usually may not communicate effectively; coordination breakdowns occur, which results in integration failures \cite{3_kwan}.
+There may have lower developers productivity \cite{4_cataldo, 5_damian} which may cause inefficient run in the rush moments in a release period.
 There is a substantial and important body of literature on risk in software engineering.
-Boehm identified the most important risks encountered by software project managers and described successful risk management practices [6, 7, 8].
+Boehm identified the most important risks encountered by software project managers and described successful risk management practices \cite{6_boehm, 7_keil, 8_boehm}.
 Some of the risks identified are related to disruptive events, such as the introduction of a new technology, but most are macro risks associated with running a project, such as developing the wrong functionality.
@@
 Many people have worked with pretty relevant ideas but I didn't find many very similar to our motivation.
-Hindle worked on release pattern discovery via partitioning [9].
+Hindle worked on release pattern discovery via partitioning \cite{9_hindle}.
 In this research they proposed a method of observing, analyzing and summarizing the results of metrics of revisions found near releases.
@@
 Hindle divided the revisions in each release in 4 different classes, Source Code, Testing, Building, and Documentations.
-Actually this paper worked in a reverse way than Cook did [10].
+Actually this paper worked in a reverse way than Cook did \cite{10_cook}.
 Cook inserted sensors and monitors into the development process but Hindle and Michael analyzed the data to understand what happened in the past.
-Another research work we would like to mention was done by  Damian where they have worked on the role of domain knowledge and cross functional communication among the OOS development teams [11].
-Posnett did some dual ecological measures of focus in software development [12].
+Another research work we would like to mention was done by  Damian where they have worked on the role of domain knowledge and cross functional communication among the OOS development teams \cite{11_damian}.
+Posnett did some dual ecological measures of focus in software development \cite{12_posnett}.
 Posnett's measure was for the more general view that unifies developer focus and artifact ownership.
-Posnett analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from echology to produce a novel and iii) conceptually unified view of measuring focus and ownership.
+Posnett analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from ehology to produce a novel and iii) conceptually unified view of measuring focus and ownership.
 Another study was done by F.
-Rahman about the authorship of the code-bases in OSS development [13].
+Rahman about the authorship of the code-bases in OSS development \cite{13_rahman}.
 
@@
 \subsection{Extracting Data}
-... ... ...
+We went for the VCS of a target project and either mirror the repository or download each revision and commit log history data individually.
+From VCSs such as CVS we extract the revisions and release information.
+We then put them into a database.
+We have used here PSQL database to create tables in, to store our extracted data.
+These extracted will be analyzed by us later on.
+Per each revision the information extracted includes the commit id, tree id, author of the revision, date of revision, the name of the revised file, parent and child info for the revision and the detail log information.
+Once extraction is complete we are ready to partition the version numbers (Section 4.2) and duration  of each release (Section 4.3).
 
-\subsection{Partioning Version Numbers}
-... ... ...
-\subsubsection{Inline (In-text) Equations}
-... ... ... ... ... ...
+\subsection{Partioning Release Numbers}
+We stored the git commit log extracted data into a table named git commit and git revision where all the basic and log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
+By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can get determine which commit belongs to which version and release, and also what type of release that is as well.
+Figure 1 shows the picture of the data how it looks like.
+
+\begin{figure}
+\centering
+\psfig{file=versions.png, height=1in, width=3in,}
+\caption{Releases extracted from Version}
+\end{figure}
+We are getting the release dates also with every commit record.
+So we can understand which commit belongs to which version of release, is this a major release or minor or minor.
+Another information we have captured that is \textbf{rc} which means that the particular commit was for a release candidate.
+
+\subsubsection{Explanation}
+A Linux kernel development release version having maximum length of information looks like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
+If a release looks like linuxv2.6.13 it tells us that this particular release is the 13th minor release  under  the 6th major release of kernel version 2.
+linuxv2.6.13\textbf{-rc1} says that after the 13th minor release been released development for the next release has been started and rc1 is the first candidate on the way to the next release.
+It doesn't ensure that next release is also going to be another minor release.
 

### 2013-10-23 paper1/paper1.tex
updating paper and some script files

@@
 \documentclass{acm_proc_article-sp}
-
+\usepackage{algorithmic}
+\usepackage{algorithm}
+\usepackage{listings}
+\usepackage{booktabs}
 \begin{document}
@@
 Software projects are notorious for going over budget and schedule.
-Rush periods are often gets seen before a major release that turns the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{1_brooks}.
+Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{1_brooks}.
 This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor.
@@
 Figure 1 shows the picture of the data how it looks like.
-
 \begin{figure}
@@
 \end{figure}
+
+\begin{lstlisting}
+Find out the release candidates:
+update git_refs_tags set rc = cast(
+  substring(
+    path from
+      position( '-rc' in path )
+        + 3 for 2 
+  ) as integer
+) where path ~ E'-rc';
+\end{lstlisting}
+Find out major release version number:
+\begin{lstlisting}
+update git_refs_tags set major = cast(
+  substring(
+    path, 'v([0-9]+)\.?'
+      ) as integer
+);
+\end{lstlisting}
+Find out minor release version number:
+\begin{lstlisting}
+update git_refs_tags set minor = cast(
+  substring(
+    path, 'v[0-9]+\.([0-9]+)\.?'
+      ) as integer
+);
+\end{lstlisting}
+Find out micro release version number:
+\begin{lstlisting}
+update git_refs_tags set micro = cast(
+  substring(
+    path, 'v[0-9]+\.[0-9]+\.([0-9]+)\-?'
+      ) as integer
+);
+\end{lstlisting}
+
 We are getting the release dates also with every commit record.
-So we can understand which commit belongs to which version of release, is this a major release or minor or minor.
+So we can understand which commit belongs to which version of release, is this a major release or minor or micro.
 Another information we have captured that is \textbf{rc} which means that the particular commit was for a release candidate.
@@
 A Linux kernel development release version having maximum length of information looks like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
-If a release looks like linuxv2.6.13 it tells us that this particular release is the 13th minor release  under  the 6th major release of kernel version 2.
-linuxv2.6.13\textbf{-rc1} says that after the 13th minor release been released development for the next release has been started and rc1 is the first candidate on the way to the next release.
+If a release versioning looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release  under  the 6th major release of kernel version 2.
+``linuxv2.6.13\textbf{-rc1}'' says that after the 13th minor release been released development for the next release has been started and rc1 is the first candidate on the way to the next release.
 It doesn't ensure that next release is also going to be another minor release.
@@
 \subsection{Get Time-Span Between Release}
-... ... ...
+Another information that we require is what are the durations of the releases of Linux kernel development.
+To achieve that we joined the table shown in figure 1 and git\_commit.
+The following psql query did the job pretty easily for us:
+\begin{lstlisting}
+select
+grt.path as release, grt.major, grt.minor,
+grt.micro, grt.rc, gc.committer_dt
+from
+git_refs_tags grt, git_commit gc
+where
+gc.commit = grt.commit
+order by
+gc.committer_dt
+\end{lstlisting}
+This query gives us all the dates of commit for each and every release, so we can easily find out the duration between two consecutive releases.
+This information is more important to us because we need to see what is the actual development period and what is the merging or other fixing period within a release time-span and also we need to understand how developers are working, what is the impact of their changes made in the code-base during a particular release period.
+Table 1 shows a small portion of this information.
+Preior to calculate the areas of the developers in secion 4.4 we require this information.
+
+\begin{table}[ht]
+\caption{Nonlinear Model Results}	 % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Release & Type & Start Date & End Date \\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+linuxv2.6.12-rc2 & rc       & 2005-04-16 & 2005-04-16 \\
+linuxv2.6.12-rc3 & rc       & 2005-04-16 & 2005-04-20 \\
+linuxv2.6.12-rc4 & rc       & 2005-04-20 & 2005-05-07 \\
+linuxv2.6.12-rc5 & rc       & 2005-05-07 & 2005-05-24 \\
+linuxv2.6.12-rc6 & rc       & 2005-05-24 & 2005-06-06 \\
+linuxv2.6.12        & micro & 2005-06-06 & 2005-06-17 \\
+linuxv2.6.13-rc1 & rc       & 2005-06-17 & 2005-06-29 \\
+linuxv2.6.13-rc2 & rc       & 2005-06-29 & 2005-07-05 \\
+linuxv2.6.13-rc3 & rc       & 2005-07-05 & 2005-07-13 \\
+linuxv2.6.13-rc4 & rc       & 2005-07-13 & 2005-07-28 \\
+linuxv2.6.13-rc5 & rc       & 2005-07-28 & 2005-08-02 \\
+linuxv2.6.13-rc6 & rc       & 2005-08-02 & 2005-08-07 \\
+linuxv2.6.13-rc7 & rc       & 2005-08-07 & 2005-08-23 \\
+linuxv2.6.13        & micro & 2005-08-23 & 2005-08-28 \\
+linuxv2.6.14-rc1 & rc       & 2005-08-28 & 2005-09-12 \\
+linuxv2.6.14-rc2 & rc       & 2005-09-12 & 2005-09-19 \\
+linuxv2.6.14-rc3 & rc       & 2005-09-19 & 2005-09-30 \\
+linuxv2.6.14-rc4 & rc       & 2005-09-30 & 2005-10-10 \\
+linuxv2.6.14-rc5 & rc       & 2005-10-10 & 2005-10-20 \\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
 
 \subsection{Calculate Developers' Area}
-... ... ...
+Developers are working throughout the release time.
+Developers' are means the files developers work in.
+But it doesn't refer the to file itself but to understand which files are being touched by which developers.
+We see that authors are committing files almost everyday throughout a release.
+We have the commit log data in our hand and we know what is the duration of each releases (i.e.\ start and end dates).
+Now it is possible to find out which commits were made for which files by a developer within a given time range of a release.
+
+We select all the release information from the table where we stored the releases with their corresponding time-span.
+After that we select author name and other relevant information from the joining of ``git\_revision'' and ``git\_commits'' tables for every release.
+We insert these information into a table named ``dev\_area\_rel'' so that we can use the data for our further analysis.
+
+The following pseudo code may show the path to achieve the desired result in this section:
+
+\begin{algorithm}
+\caption{Calculate Developers Area}
+\begin{algorithmic}
+\REQUIRE $ $\\
+$commit\_date \geq  release\_start\_date$\\
+$commit\_date < release\_end\_date$
+\ENSURE
+\STATE $get all releases$
+
+\WHILE{$prev\_release\_date \leftarrow release\_start\_date and release \leftarrow release\_version$}
+\IF{$release$}
+	\IF{$commit\_date \geq  release\_start\_date$ and $commit\_date < release\_end\_date$}
+		\STATE $select author, path, commits, churn$
+		\STATE $insert data into table dev\_area\_rel$
+	\ENDIF
+\ENDIF
+\ENDWHILE
+\end{algorithmic}
+\end{algorithm}
 
@@
 
-\subsection{Extracting Data}
-... ... ...
-\subsubsection{Display Equations}
-... ... ... ... ... ...
+\subsection{Jaccard Distance}
+Once we found different releases and the release periods as well we calculate the developers' are to see what changes developers are doing in releases.
+We also want to know what is the difference being created by making changes between two consecuitive releases.
+If I explain it more then I can say, developers are working in many different files in a release and may work in a same file again for the next release or releases.
 

### 2013-10-26 paper1/paper1.tex
updating paper

@@
 
-\title{Re-Allocation of Resources during Releases \titlenote{Copyright information will go here.}}
+\title{Re-Allocation of Resources during Releases \titlenote{Copyright note}}
 \numberofauthors{2}
@@
        \affaddr{438-932-2288, +1}\\
-       \email{rupak.karmadhar@gmail.com}
+       \email{mdt\_rahm@encs.concordia.ca}
 % 2nd. author
@@
 \subsection{Extracting Data}
-We went for the VCS of a target project and either mirror the repository or download each revision and commit log history data individually.
-From VCSs such as CVS we extract the revisions and release information.
+We went for the VCS of a target project and either mirror the repository or download every revision and commit log history data.
+From DVCSs such as Git we extract the revisions and release information.
+We wrote Perl scripts to extract date that was further processed to obtain details.
+Manual inspection was used to resolve problems and things like that in cases where all automated techniques failed.
 We then put them into a database.
-We have used here PSQL database to create tables in, to store our extracted data.
+We have used PSQL database to create tables in, to store our extracted data.
 These extracted will be analyzed by us later on.
@@
 
-\subsection{Partioning Release Numbers}
+\subsection{Partitioning Release Numbers}
 We stored the git commit log extracted data into a table named git commit and git revision where all the basic and log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
@@
 Another information that we require is what are the durations of the releases of Linux kernel development.
-To achieve that we joined the table shown in figure 1 and git\_commit.
-The following psql query did the job pretty easily for us:
+To achieve that we joined the table in figure 1 and the table ``git\_commit''.
+The following psql did the job pretty easily for us:
 \begin{lstlisting}
@@
 \end{lstlisting}
-This query gives us all the dates of commit for each and every release, so we can easily find out the duration between two consecutive releases.
+This query gives us all the dates of commit for each and every release, so we can easily find out the duration between two consecutive releases (all including release candidates RC).
 This information is more important to us because we need to see what is the actual development period and what is the merging or other fixing period within a release time-span and also we need to understand how developers are working, what is the impact of their changes made in the code-base during a particular release period.
@@
 \begin{table}[ht]
-\caption{Nonlinear Model Results}	 % title of Table
+\caption{Different Releases}  % title of Table
 \centering 						% used for centering table
@@
 % inserting body of the table
-linuxv2.6.12-rc2 & rc       & 2005-04-16 & 2005-04-16 \\
+linuxv2.6.12-rc2 & rc       & - & 2005-04-16 \\
 linuxv2.6.12-rc3 & rc       & 2005-04-16 & 2005-04-20 \\
@@
 
+Note that the very first row has no information for the ``Start Date'' because we don't have any data prior to release ``linuxv2.6.12''.
+From the extraction we found complete records for releases ``linuxv2.6.13'' to ``linuxv2.6.39'' then ``linuxv3.0'' to ``linuxv3.11''.
+We have last couple of release candidates and the release date for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
+So we are having 340 releases including major, minor, micro and rc; 40 complete releases from ``linuxv2.6.12'' to ``linuxv3.11''.
+We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers.
+
 \subsection{Calculate Developers' Area}
 Developers are working throughout the release time.
-Developers' are means the files developers work in.
-But it doesn't refer the to file itself but to understand which files are being touched by which developers.
+Developers' Are (DA) means the files developers work in.
+It doesn't refer the to file itself but it is important to understand which files are being touched by which developers.
 We see that authors are committing files almost everyday throughout a release.
-We have the commit log data in our hand and we know what is the duration of each releases (i.e.\ start and end dates).
+We have the commit log data in our hand and we know what is the duration for each and every releases (i.e.\ start and end dates).
 Now it is possible to find out which commits were made for which files by a developer within a given time range of a release.
 
+\subsubsection{DA in a Release Period}
 We select all the release information from the table where we stored the releases with their corresponding time-span.
 After that we select author name and other relevant information from the joining of ``git\_revision'' and ``git\_commits'' tables for every release.
-We insert these information into a table named ``dev\_area\_rel'' so that we can use the data for our further analysis.
+We insert these information into another table so that we can use the data for our further analysis.
 
-The following pseudo code may show the path to achieve the desired result in this section:
+The following pseudo code shows us the way of achieving the desired result in this section:
 
@@
 
-\WHILE{$prev\_release\_date \leftarrow release\_start\_date and release \leftarrow release\_version$}
+\WHILE{$prev\_release\_date \leftarrow release\_start\_date\ and\ release \leftarrow release\_version$}
 \IF{$release$}
@@
 \end{algorithm}
+
+A relatively straightforward discipline of Linux Kernel Development team is followed with regard to the merging of patches for each release \cite{14_kernel}.
+At the beginning of each development cycle, the "merge window" is said to be opened.
+At that time, code which is deemed to be sufficiently stable (and which is accepted by the development community) is merged into the mainline kernel.
+The bulk of changes for a new development cycle (and all of the major changes) will be merged during this time, at a rate approaching 1,000 changes ("patches," or "changesets") per day.
+Strategically linux starts a new kernel release with the merging and fixing to get their development branch ready to start development for the next release.
+So there are two main segments in a release period, one is merge window or merge period (MP) and another is development window what we are going to call Release Development Period (RDP).
+
+Similarly we have calculated DA in both MP and RDP as described in the following subsections.
+
+\subsubsection{DA in a Merge Period}
+Merge Perid can be determined from the previous release (any of major, minor or micro releases) date to the first RC date.
+For example if the date of release for ``linuxv2.6.12''  is 2005-06-17 and date of pushing the first RC for the next release ``linuxv2.6.13-rc1'' is 2005-06-29 then this time period of of 12 days is being called the merge window \cite{14_kernel} or MP.
+Table 2 shows some merging periods of different releases.
+
+\begin{table}[ht]
+\caption{Release Merging Periods}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Release 			& Start Date		& RC Date \\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+linuxv2.6.13		& 2005-06-17	& 2005-06-29 \\
+linuxv2.6.14		& 2005-08-28	& 2005-09-12 \\
+linuxv2.6.15		& 2005-10-27	& 2005-11-11 \\
+linuxv2.6.16		& 2006-01-02	& 2006-01-17 \\
+linuxv2.6.17		& 2006-03-20	& 2006-04-02 \\
+linuxv2.6.18		& 2006-06-17	& 2006-07-06 \\
+linuxv2.6.19		& 2006-09-19	& 2006-10-04 \\
+linuxv2.6.20  		& 2006-11-29	& 2006-12-13 \\
+linuxv2.6.21		& 2007-02-04	& 2007-02-20 \\
+linuxv2.6.22		& 2007-04-25	& 2007-05-12 \\
+linuxv2.6.23		& 2007-07-08	& 2007-07-22 \\
+linuxv2.6.24		& 2007-10-09	& 2007-10-23 \\
+linuxv2.6.25		& 2008-01-24	& 2008-02-10 \\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+
+We understand DA or Developers' Area is the files in the code-base, developers are working from the dataset that we have in our hand.
+We have the commit logs and every record says about who committed the file when did he/she worked on the file.
+If we run an SQL query then we can easily find out for every author and for every particular file how many times it's been committed by an author and what changes (here, addition + deletion = churn) he/she has been made.
+So we are calculating the DA and storing the information into a table.
+A part of that table is shown in table 3.
+
+\begin{table}[ht]
+\caption{DA in Merge Period}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Author		& File Path			& Commits		& Churn \\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+D. S. Miller	& include/.../pci.h		& 1				& 8 \\
+V. Hanquez	& arch/.../cpu.c		& 1				& 14 \\
+A. Bunk		& drivers/.../shmem.c	& 1				& 2 \\
+J. Juhl		& arch/.../generic.c		& 1				& 3 \\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+
+In this table we see in a merging period inside a release period D.
+S.
+Miller has made change in pci.h file only once wich the churn number 8.
+In the similar way we calculate DA in RDP and RTR period as well.
+
+\subsubsection{DA in a RD Period and RTR}
+As like MP we can extract the RDP from the.
+RDP here in Linux Kernel development process is being considered as from the release date of RC1 (i.e.\ first release candidate opening the gate for the development of the next release) to the next release (major, minor or micro) date.
+For example if the date of release for ``linuxv2.6.13-rc1'' after releasing ``linuxv2.6.12''  is 2005-06-29 and date of publishing the next release ``linuxv2.6.13'' is 2005-08-28 then this time period of of 60 days is being called the RDP.
+Table 4 is showing some development periods of different releases.
+
+\begin{table}[ht]
+\caption{Release Development Periods}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Release 			& RD Start Date	& Release Date \\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+linuxv2.6.13		& 2005-06-29	& 2005-08-28 \\
+linuxv2.6.14		& 2005-09-12	& 2005-10-27 \\
+linuxv2.6.15		& 2005-11-11	& 2006-01-02 \\
+linuxv2.6.16		& 2006-01-17	& 2006-03-20 \\
+linuxv2.6.17		& 2006-04-02	& 2006-06-17 \\
+linuxv2.6.18		& 2006-07-06	& 2006-09-19 \\
+linuxv2.6.19		& 2006-10-04	& 2006-11-29 \\
+linuxv2.6.20  		& 2006-12-13	& 2007-02-04 \\
+linuxv2.6.21		& 2007-02-20	& 2007-04-25 \\
+linuxv2.6.22		& 2007-05-12	& 2007-07-08 \\
+linuxv2.6.23		& 2007-07-22	& 2007-10-09 \\
+linuxv2.6.24		& 2007-10-23	& 2008-01-24 \\
+linuxv2.6.25		& 2008-02-10	& 2008-04-16 \\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+
+So along these RDs of each release period developers get involved in the development for the next release.
+As we mentioned earlier RTR may happen as the release approaches.
+Keeping this in our aim list we noticed an important slot in these RDs of releases.
+We see in between two consecutive releases there is a merging period of time, after that development starts by pushing RCs and once RC releases stops and it takes some days of time for the preperation to publish the release.
+We are calling this last part as RTR Period because we asume RTR may happen in this period of time before release.
+Table 5 represents some releases with their corresponding RTR (i.e.\ from end date to rc and date of release).
+
+\begin{table}[ht]
+\caption{RTR Periods}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Release 			& RC End Date	& Release Date	& Days \\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+linuxv2.6.13		& 2005-06-29	& 2005-08-28	& 5 \\
+linuxv2.6.14		& 2005-09-12	& 2005-10-27	& 8 \\
+linuxv2.6.15		& 2005-11-11	& 2006-01-02	& 9 \\
+linuxv2.6.16		& 2006-01-17	& 2006-03-20	& 8 \\
+linuxv2.6.17		& 2006-04-02	& 2006-06-17	& 12 \\
+linuxv2.6.18		& 2006-07-06	& 2006-09-19	& 7 \\
+linuxv2.6.19		& 2006-10-04	& 2006-11-29	& 14 \\
+linuxv2.6.20  		& 2006-12-13	& 2007-02-04	& 10 \\
+linuxv2.6.21		& 2007-02-20	& 2007-04-25	& 7 \\
+linuxv2.6.22		& 2007-05-12	& 2007-07-08	& 8 \\
+linuxv2.6.23		& 2007-07-22	& 2007-10-09	& 9 \\
+linuxv2.6.24		& 2007-10-23	& 2008-01-24	& 5 \\
+linuxv2.6.25		& 2008-02-10	& 2008-04-16	& 8 \\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
 

### 2013-10-26 scripts/jaccard/dev_area_dev.pl
including scripts and references cleaning up generated files

@@ -1,0 +1,59 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_rc_dates = $dbh_ref->prepare(q{
+	select	release, rc_date, rel_date
+	from	rd_period
+});
+
+my $dev_area = $dbh_ref->prepare(q{
+	insert into dev_area_dev
+        select 
+		author,
+		?,
+		r.new_path,
+		count(*) as commits,
+		sum(add+remove) as churn,
+		0 as ownership
+	from 
+		git_revision r, git_commit c
+                                    
+	where 
+		c.commit = r.commit 
+		and c.committer_dt > ?
+		and c.committer_dt <= ?
+	group by
+		author, r.new_path
+});
+#This will insert the information about the changes that developers are making in a period of merging in a release.
+
+$get_rc_dates->execute() or die;
+
+while ( my($release, $rc_date, $rel_date) = $get_rc_dates->fetchrow_array) {
+	print "$release -- $rc_date --  $rel_date\n";
+
+	$dev_area->execute($release, $rc_date, $rel_date) or die; 
+}
+
+$get_rc_dates->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see dev_jac_releases.sql

### 2013-10-26 scripts/jaccard/dev_area_merge.pl

@@ -1,0 +1,59 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_merge_dates = $dbh_ref->prepare(q{
+	select	release, previous, rc_date
+	from	merge_period order by major, minor, micro
+});
+
+my $dev_area = $dbh_ref->prepare(q{
+	insert into dev_area_merge
+        select 
+		author,
+		?,
+		r.new_path,
+		count(*) as commits,
+		sum(add+remove) as churn,
+		0 as ownership
+	from 
+		git_revision r, git_commit c
+                                    
+	where 
+		c.commit = r.commit 
+		and c.committer_dt > ?
+		and c.committer_dt <= ?
+	group by
+		author, r.new_path
+});
+#This will insert the information about the changes that developers are making in a period of merging in a release.
+
+$get_merge_dates->execute() or die;
+
+while ( my($release, $prev_date, $rc_date) = $get_merge_dates->fetchrow_array) {
+	print "$release -- $prev_date --  $rc_date\n";
+
+	$dev_area->execute($release, $prev_date, $rc_date) or die; 
+}
+
+$get_merge_dates->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see dev_jac_releases.sql

### 2013-10-26 scripts/jaccard/dev_area_rel.pl

@@ -1,0 +1,72 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+#This file calculates the area of developers during release period. How many commits are made
+#by an author for a particular file, how many churns are made and what is the percentage of his/her 
+#ownership to that file.
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_release_dates = $dbh_ref->prepare(q{
+	select	committer_dt, path as release
+	from	git_refs_tags r, git_commit c
+	where	c.commit = r.commit
+		and r.rc = 0
+	order by committer_dt
+});
+#we are avoiding rc because we want the release dates. rc dates are not release dates.
+
+my $dev_area = $dbh_ref->prepare(q{
+	insert into dev_area_rel
+        select 
+		author,
+		?,
+		r.new_path,
+		count(*) as commits,
+		sum(add+remove) as churn,
+		0
+	from 
+		git_revision r, git_commit c
+                                    
+	where 
+		c.commit = r.commit 
+		and c.committer_dt > ? 
+		and c.committer_dt <= ?
+	group by
+		author, r.new_path
+});
+#This will insert the information about the changes that developers are making in a release period.
+
+$get_release_dates->execute() or die;
+
+my($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
+
+while ( my($date, $release) = $get_release_dates->fetchrow_array) {
+	print "$release -- $prev_date --  $date\n";
+
+	$dev_area->execute($release, $prev_date, $date) or die; 
+
+	$prev_date = $date;
+	$prev_release = $release;
+}
+
+$get_release_dates->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see dev_jac_releases.sql

### 2013-10-26 scripts/jaccard/dev_area_rtr.pl

@@ -1,0 +1,56 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_rc_dates = $dbh_ref->prepare(q{select release, rc_end_date, rel_date from rtr_period});
+
+my $dev_area = $dbh_ref->prepare(q{
+	insert into dev_area_rtr
+        select 
+		author,
+		?,
+		r.new_path,
+		count(*) as commits,
+		sum(add+remove) as churn,
+		0 as ownership
+	from 
+		git_revision r, git_commit c
+                                    
+	where 
+		c.commit = r.commit 
+		and c.committer_dt > ?
+		and c.committer_dt <= ?
+	group by
+		author, r.new_path
+});
+#This will insert the information about the changes that developers are making in a period of merging in a release.
+
+$get_rc_dates->execute() or die;
+
+while ( my($release, $rc_end_date, $rel_date) = $get_rc_dates->fetchrow_array) {
+	print "$release -- $rc_end_date --  $rel_date\n";
+
+	$dev_area->execute($release, $rc_end_date, $rel_date) or die; 
+}
+
+$get_rc_dates->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see dev_jac_releases.sql

### 2013-10-26 scripts/jaccard/dev_jac.pl

@@ -1,0 +1,87 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_release_dates = $dbh_ref->prepare(q{
+	select committer_dt, path as release 
+	from git_refs_tags r, git_commit c
+	where c.commit = r.commit
+	order by committer_dt
+});
+
+my $dev_union = $dbh_ref->prepare(q{
+	select count(*) 
+	from (
+		select author, path 
+		from dev_area_rel
+		where release = ? 
+		union
+		select author, path 
+		from dev_area_rel 
+		where release = ?
+	) as r
+});
+my $dev_intersection = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path
+		from dev_area_rel
+		where release = ?
+		INTERSECT
+		select author, path 
+		from dev_area_rel
+		where release = ?
+	) as r
+});
+
+$get_release_dates->execute() or die;
+
+#throw away the first because nothing is before it
+my($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
+
+($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
+
+while ( my($date, $release) = $get_release_dates->fetchrow_array) {
+
+	$dev_union->execute($prev_release, $release) or die;
+	my $union = $dev_union->fetchrow_array;
+	
+	$dev_intersection->execute($prev_release, $release) or die;
+	my $intersection = $dev_intersection->fetchrow_array;
+	
+	my $jac = $intersection/$union;
+	my $jac_dist = ($union - $intersection) / $union;
+	print " $prev_release ~ $release => $jac_dist\n";
+	
+	my $query_insert = $dbh_ref->prepare(q{
+		insert into rel_jac_dist values(?,?,?)
+	});
+	$query_insert->execute($prev_release, $release, $jac_dist) or die("Could not insert into rel_jac_dist");
+
+	$prev_date = $date;
+	$prev_release = $release;
+}
+
+$dev_intersection->finish;
[…]

### 2013-10-26 scripts/jaccard/get_release_period.pl

@@ -1,0 +1,83 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_release_dates = $dbh_ref->prepare(q{
+	select
+		grt.path as release,
+		grt.major,
+		grt.minor,
+		grt.micro,
+		grt.rc,
+		gc.committer_dt
+	from 	
+		git_refs_tags grt, git_commit gc 
+	where 	
+		gc.commit = grt.commit 
+	order by
+		gc.committer_dt
+});
+
+$get_release_dates->execute() or die;
+
+my $prev_release = '';
+my $release = '';
+my $major = '';
+my $minor = '';
+my $micro = '';
+my $rc = '';
+my $release_date = '';
+my $prev_release_date = '';
+my $start_date = '';
+my $end_date = '';
+my ($query,$query_handler) = '';
+my $type = '';
+
+$get_release_dates->bind_columns(undef, \$release, \$major, \$minor, \$micro, \$rc, \$release_date);
+
+while ( $get_release_dates->fetchrow_array ){
+	print "$release :: $major - $minor - ".($micro ? $micro : "")." - ".($rc ? $rc : "")." - $release_date\n";
+	if(!$rc){
+		if($micro){
+			$type = 'micro';
+		}else{
+			if($minor){
+				 $type = 'minor';
+			}else{
+				 $type = 'major';
+			}
+		}
+	}else{
+		$type = 'rc';
+	}
+	$end_date = $release_date;
+	$start_date = $prev_release_date ? $prev_release_date : $release_date;
+
+	$query = "insert into git_rel_period(release, type, start_date, end_date) values('".$release."','".$type."','".$start_date."','".$end_date."')";
+	$query_handler = $dbh_ref->prepare($query);
+	$query_handler->execute() or die('Could not insert into git_rel_period');
+	
+	$prev_release_date = $release_date;
+	$prev_release = $release;
+}
+
+$get_release_dates->finish;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-10-26 scripts/ownership/ownership_rel.pl

@@ -1,0 +1,40 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_file_info = $dbh_ref->prepare(q{
+	select	path, churn from file_info
+});
+
+my $update_ownership = $dbh_ref->prepare(q{
+	update dev_area_rel set ownership = ((churn/?)*100) where author = author and path=?
+});
+
+$get_file_info->execute() or die;
+
+while ( my($path, $churn) = $get_file_info->fetchrow_array) {
+	$update_ownership->execute($churn, $path) or die; 
+}
+
+$get_file_info->finish;
+$update_ownership->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see ownership.sql

### 2013-10-26 scripts/release_times/merge_period.pl

@@ -1,0 +1,49 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist"
+	unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $query1 = $dbh_ref->prepare(q{select r.major, r.minor, r.micro, r.rc, r.date from git_refs_tags r, git_commit c where r.commit=c.commit order by c.committer_dt });
+
+my $insert = $dbh_ref->prepare(q{insert into merge_period values (?,?,?,?,?,?)});
+
+$query1->execute or die;
+
+my $prev_date;
+while ( my($major, $minor, $micro, $rc, $date) = $query1->fetchrow_array) {
+	if(not defined $prev_date){
+		 $prev_date = $date;
+	}
+	if (defined $rc and $rc == 1) {
+		my $release = 'linuxv'.$major.'.'.$minor.'.'.$micro;
+		print "$release -- $prev_date -- $date\n";
+		$insert->execute($release, $major, $minor, $micro, $prev_date, $date);
+	}
+	$prev_date = $date;
+}
+
+$update = $dbh_ref->prepare(q{update merge_period set days = extract(epoch from rc_date - previous)/86400});
+$update->execute;
+
+$query1->finish;
+$insert->finish;
+$update->finish;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-10-26 scripts/release_times/rd_period.pl

@@ -1,0 +1,51 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my($query1, $query2);
+
+$query1 = $dbh_ref->prepare(q{select release, major, minor, micro, rc_date from merge_period});
+
+my $insert = $dbh_ref->prepare(q{insert into rd_period values (?,?,?,?,?,?)});
+
+$query1->execute or die(pg_last_error());
+
+while ( my($release, $major, $minor, $micro, $rc_date) = $query1->fetchrow_array) {
+
+	$query2 = $dbh_ref->prepare(q{select max(date) from git_refs_tags where major=? and minor=? and micro=? group by major, minor, micro});
+	$query2->execute($major, $minor, $micro) or die(pg_last_error());
+	my $release_date = $query2->fetchrow_array;
+	
+	if(defined $release_date){
+		my $release = 'linuxv'.$major.'.'.$minor.'.'.$micro;
+		print "$release -- $rc_date -- $release_date\n";
+		$insert->execute($release, $major, $minor, $micro, $rc_date, $release_date);
+	}
+}
+
+$update = $dbh_ref->prepare(q{update rd_period set days = extract(epoch from rel_date - rc_date)/86400});
+$update->execute;
+
+$query1->finish;
+$query2->finish;
+$insert->finish;
+$update->finish;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-10-26 scripts/release_times/rtr_period.pl

@@ -1,0 +1,59 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my($query1, $query2);
+
+$query1 = $dbh_ref->prepare(q{
+	select	release, major, minor, micro, (
+			select	max(date) as release_date
+			from	git_refs_tags
+			where	rc != 0 and major=m.major and minor=m.minor and micro=m.micro
+			group	by major, minor, micro order by release_date
+		) as rc_end_date
+	from merge_period m
+});
+
+my $insert = $dbh_ref->prepare(q{insert into rtr_period values (?,?,?,?,?,?)});
+
+$query1->execute or die(pg_last_error());
+
+while ( my($release, $major, $minor, $micro, $rc_end_date) = $query1->fetchrow_array) {
+
+	$query2 = $dbh_ref->prepare(q{select max(date) from git_refs_tags where major=? and minor=? and micro=? group by major, minor, micro});
+	$query2->execute($major, $minor, $micro) or die(pg_last_error());
+	my $release_date = $query2->fetchrow_array;
+	
+	if(defined $release_date){
+		my $release = 'linuxv'.$major.'.'.$minor.'.'.$micro;
+		print "$release -- $rc_end_date -- $release_date\n";
+		$insert->execute($release, $major, $minor, $micro, $rc_end_date, $release_date);
+	}
+}
+
+$update = $dbh_ref->prepare(q{update rtr_period set days = extract(epoch from rel_date - rc_end_date)/86400});
+$update->execute;
+
+$query1->finish;
+$query2->finish;
+$insert->finish;
+$update->finish;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-10-30 paper1/paper1.tex
Ownership calculated for releases. Paper updated. Reference files renamed.

@@
 \end{abstract}
-\category{K.6.3}{Software Management}{Software Development; Software Resource Management, Resource Reallocation}
+\category{K.6.3}{Software Management}{Software Development, Software Resource Management, Resource Reallocation}
 \terms{Experiment, Human Factors, Resource Management, Reallocation}
-\keywords{Resource Reallocation, Software Releases} % NOT required for Proceedings
+\keywords{Resource Reallocation, Code Ownership, Defect Density, Software Releases} % NOT required for Proceedings
 \section{Introduction}
@@
 The commit log data that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release.
-This information will help us to identify the criteria of the resources, their roles, file ownership and nativeness (∆ƞ) in the domain.
-This knowledge of nativeness (∆ƞ) will guide us understanding the method of reallocation.
+This information will help us to identify the criteria of the resources, their roles, file ownership and nativeness in the domain.
+This knowledge of nativeness will guide us understanding the method of reallocation.
 Very few research works have been performed regarding the re-allocation of resources.
@@
 What changes in nativeness (∆ƞ) occurs after the reallocation.
-Section 6 will give us the result to show how change in ∆ƞ puts impact on the outcome of a software.
+Section 6 will give us the result to show how change in nativeness puts impact on the outcome of a software.
 Finally section 7 will give us an idea of our future work followed by the conclusion in section 8.
@@
 We are going to present the steps involved in this process and then we will follow up with an application of our methodology in a case study.
-Our methodology can be summarized as: Extracting Data for revisions and releases (Section 4.1); Partitioning the version numbers (Section 4.2); Get time-span between each release (Section 4.3); Calculate developer areas (Section 4.4); Finding code area owners (Section 4.5).
-Finding merging time and development time within a release period that we found in section 4.1 (Section 4.6).
+In order to address our research questions, we obtain key measures of project evolution from archival data had been preserved throughout the history of the Linux Kernel development project.
+All information on the OSS project is recorded in electronic form.
+Many other OSS projects archive similar data, so the techniques used here can be replicated on any such project.
+We used the data elements extracted from the archival source to construct a number of measures on the commit log records to understand the behavior of the development resources (mainly developers).
+Our methodology can be summarized as: Extracting Data for revisions and releases (Section 4.1); Partitioning the version numbers (Section 4.2); Get time-span between each release (Section 4.3); Calculate developer areas (Section 4.4); Finding code ownership (Section 4.5).
+Calculating Jaccard Distance for different development areas.
 
@@
 By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can get determine which commit belongs to which version and release, and also what type of release that is as well.
-Figure 1 shows the picture of the data how it looks like.
-\begin{figure}
-\centering
-\psfig{file=versions.png, height=1in, width=3in,}
-\caption{Releases extracted from Version}
-\end{figure}
 
@@
 
-Note that the very first row has no information for the ``Start Date'' because we don't have any data prior to release ``linuxv2.6.12''.
+Note that the very first row has no information for the ``Start Date'' because we don't have any data prior to stable release ``linuxv2.6.12''.
 From the extraction we found complete records for releases ``linuxv2.6.13'' to ``linuxv2.6.39'' then ``linuxv3.0'' to ``linuxv3.11''.
 We have last couple of release candidates and the release date for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
-So we are having 340 releases including major, minor, micro and rc; 40 complete releases from ``linuxv2.6.12'' to ``linuxv3.11''.
+So we are having 340 releases including major, minor, micro and rc; 40 stable releases from ``linuxv2.6.12'' to ``linuxv3.11''.
 We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers.
+Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once. So we found them in our released wise datasets.
 
@@
 
-\subsection{Finding Code-Area Owners}
-... ... ...
+These information above will help us to answer our first research-question.
+
+\subsection{Finding Code Ownership}
+So many developers are working from different development communities.
+We tried to investigate the "code ownership" \cite{15_mockus} evolved in Linux Kernel development.
+Here code ownership is going to be represented as percentage value.
+Considering the data that we have for complete releases (``linuxv2.6.12'' to ``linuxv3.11'') we filtered the code files and we found 75138 distinct files that have been worked on.
+We investigate the total number of commits, total number of churn for each and every file also how many developers contributed for these commits and changes.
+This information yet does not tell about the ownership.
+We need to find out ownership for every developers in different development areas in an RP.
+We already have the collection of developers working in different areas MP, RDP, RTR within an RP and stored them with corresponding file they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
+We now update those information with the ownership information.
+For calculating ownership Equation 1 is applied.
+\begin{equation}\omega=\frac{n}{N}*100\end{equation}
+Where $\omega$ is the ownership and n is the number of total changes made by an atuthor of a file, N is the total number of changes made for a particular file.
+To determine a developer be a owner of a file we considering that if the developer makes changes more than 80\% of the total change that the file has got, then that developer can be treated as a owner of the codes of that file similarly as C.
+Gutwin did \cite{16_gutwin} for finding out the main developers' group for a project.
+We already mentioned that 14569 individual files didn't have any change (addition or deletion) but was being committed at least once.
+So we found them in our release wise datasets that's why in addition to Gutwin here considering commits also to determine ownership but only for files without any add or remove lines information.
+If a file has no addition or deletion information (we are calling it churn) in it's commit log but has beet committed by some one at least once then that or those authors may have the ownership for that file.
+So the equation 1 becomes like:
+\begin{equation} \omega = \left\{ \begin{array}{l l} n/N & \quad \text{if $N > 0$}\\ c/C & \quad \text{if $N = 0$} \end{array} * 100 \right.\end{equation}
+Where c is the number of commits made by the author and C is the total number of commits made for the particular file.
+We calculate code ownership for all different parts MP, RDP, RTR and also for an entire release period RP. Table 6 represents a part of the data where ownerships is calculated.
+
+\begin{table}[ht]
+\caption{Code Ownership in RP}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Author 				& Linuxv		& Path				& $\omega$ (\%) \\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+Thomas Gleixner		& 2.6.24		& .../numa\_64.h	& 0.0000\\
+Jeff Kirsher			& 3.1		& .../ethtool.c		& 0.0000\\
+Sathya Perla			& 2.6.29		& .../hwlib.h		& 100.00\\
+Roel Kluin			& 2.6.24		& .../innovator.h 	& 100.00\\
+David S. Miller		& 2.6.24		& .../visasm.h 		& 100.00\\
+Stephen Hemminger	& 2.6.24		& .../qla3xxx.c	 	& 12.083\\
+Randy Dunlap			& 2.6.24		& ...\_core.c 		& 100.00\\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+The example given above is calculated for the developers worked for different files in different releases.
+Ownership is calculated for all the developers in release periods.
+In the same way we have calculated what is the ownership value for a developer to a particular file in the merge period (MP) in a release, development period (RDP) in a release and RTR period ind a release.
 
@@
 If I explain it more then I can say, developers are working in many different files in a release and may work in a same file again for the next release or releases.
+
+\section{Preliminary Results}
+In this section we present results from several quantitative analysis of the archival data from the Linux Kernel development project.
+The measures we derive from these data are well-suited to address our research questions.
 

### 2013-10-30 scripts/jaccard/dev_area_rel.pl

@@ -57,7 +57,6 @@ my($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
 
 while ( my($date, $release) = $get_release_dates->fetchrow_array) {
 	print "$release -- $prev_date --  $date\n";
-
 	$dev_area->execute($release, $prev_date, $date) or die; 
 
 	$prev_date = $date;

### 2013-10-30 scripts/ownership/file_info.pl

@@ -1,0 +1,83 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $update_file_info;
+
+my $get_release_dates = $dbh_ref->prepare(q{
+	select	committer_dt, path as release
+	from	git_refs_tags r, git_commit c
+	where	c.commit = r.commit
+		and r.rc = 0
+	order by committer_dt
+});
+
+my $insert_file_info = $dbh_ref->prepare(q{
+	insert into file_info (path, release, authors, commits, churn)
+	select 
+		distinct new_path,
+		?,
+		0 as authors,
+		count(*) as commits,
+		sum(add+remove) as churn
+	from
+		git_revision r, git_commit c
+	where 
+		c.commit = r.commit
+		and c.committer_dt > ?
+		and c.committer_dt <= ?
+	group by
+		r.new_path
+});
+
+$update_file_info = $dbh_ref->prepare(q{
+	update file_info set authors = num_authors, first_change = first_ch, last_change = last_ch
+	from (
+		select 	new_path, count(distinct(author)) as num_authors,
+			min(committer_dt) as first_ch,
+			max(committer_dt) as last_ch
+		from 	git_commit c, git_revision r 
+		where 	c.commit = r.commit
+			and c.committer_dt > ?
+			and c.committer_dt <= ?
+		group by new_path
+	) as r
+	where r.new_path = file_info.path and file_info.release = ?;
+});
+
+$get_release_dates->execute or die;
+my($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
+
+while(my($date, $release) = $get_release_dates->fetchrow_array){
+
+	$insert_file_info->execute($release, $prev_date, $date) or die; 
+	
+	$update_file_info->execute($prev_date, $date, $release) or die;
+
+	$prev_date = $date;
+	$prev_release = $release;
+}
+
+$get_release_dates->finish;
+$insert_file_info->finish;
+$update_file_info->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see ownership.sql

### 2013-10-30 scripts/ownership/ownership_rel.pl

@@ -17,24 +17,45 @@ my %config =  Config::General::ParseConfig($config_path);
 
 my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
 
+my $get_dev_area_rel_info = $dbh_ref->prepare(q{
+	select  author, path, release from dev_area_rel
+});
 my $get_file_info = $dbh_ref->prepare(q{
-	select	path, churn from file_info
+		select  churn, commits from file_info where release = ? and path = ?
+	});
+my $update_ownership_ch = $dbh_ref->prepare(q{
+	update dev_area_rel set ownership = ((churn/?)*100)
+	where author = ? and path = ? and release = ?
+});
+my $update_ownership_cm = $dbh_ref->prepare(q{
+	update dev_area_rel set ownership = ((commits/?)*100)
+	where author = ? and path = ? and release = ?
 });
 
-my $update_ownership = $dbh_ref->prepare(q{
-	update dev_area_rel set ownership = ((churn/?)*100) where author = author and path=?
-});
+$get_dev_area_rel_info->execute or die;
+my $ch0 = 0;
+while (my($author, $path, $release) = $get_dev_area_rel_info->fetchrow_array) {
 
-$get_file_info->execute() or die;
+	$get_file_info->execute($release, $path) or die;
+	
+	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
 
-while ( my($path, $churn) = $get_file_info->fetchrow_array) {
-	$update_ownership->execute($churn, $path) or die; 
+	if($file_total_churn == 0){
+		print "$ch0. [$path] File total churn is 0\n";
+		$update_ownership_cm->execute($file_total_commits, $author, $path, $release) or die;
+		$ch0++;
+	}else{
+		$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
+	}
 }
 
+$get_dev_area_rel_info->finish;
 $get_file_info->finish;
-$update_ownership->finish;
+
+$update_ownership_ch->finish;
+$update_ownership_cm->finish;
 $dbh_ref->disconnect;
 
 __END__
 
-see ownership.sql
+see file_info.sql

### 2013-11-01 paper1/paper1.tex
updating paper, calculating ownerships in different developers' areas

@@
 We observe a reallocation of the resources among the software development teams in a large project to identify that an improper reallocation or inappropriate reorganization causes a disruptive event take place in a software development process.
-We attempt to identify a project’s different release times and calculate the difference between two consecutive releases to discover which are the new areas have been worked between two consecutive releases.
+We attempt to identify a project's different release times and calculate the difference between two consecutive releases to discover which are the new areas have been worked between two consecutive releases.
 The commit log data that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release.

### 2013-11-01 scripts/ownership/ownership_dev.pl

@@ -1,0 +1,61 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_dev_area_dev_info = $dbh_ref->prepare(q{
+	select  author, path, release from dev_area_dev
+});
+my $get_file_info = $dbh_ref->prepare(q{
+		select  churn, commits from file_info where release = ? and path = ?
+	});
+my $update_ownership_ch = $dbh_ref->prepare(q{
+	update dev_area_dev set ownership = ((churn/?)*100)
+	where author = ? and path = ? and release = ?
+});
+my $update_ownership_cm = $dbh_ref->prepare(q{
+	update dev_area_dev set ownership = ((commits/?)*100)
+	where author = ? and path = ? and release = ?
+});
+
+$get_dev_area_dev_info->execute or die;
+my $ch0 = 0;
+while (my($author, $path, $release) = $get_dev_area_dev_info->fetchrow_array) {
+
+	$get_file_info->execute($release, $path) or die;
+	
+	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
+
+	if($file_total_churn == 0){
+		print "$ch0. [$path] File total churn is 0\n";
+		$update_ownership_cm->execute($file_total_commits, $author, $path, $release) or die;
+		$ch0++;
+	}else{
+		$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
+	}
+}
+
+$get_dev_area_dev_info->finish;
+$get_file_info->finish;
+
+$update_ownership_ch->finish;
+$update_ownership_cm->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see file_info.sql

### 2013-11-01 scripts/ownership/ownership_merge.pl

@@ -1,0 +1,61 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_dev_area_merge_info = $dbh_ref->prepare(q{
+	select  author, path, release from dev_area_merge
+});
+my $get_file_info = $dbh_ref->prepare(q{
+		select  churn, commits from file_info where release = ? and path = ?
+	});
+my $update_ownership_ch = $dbh_ref->prepare(q{
+	update dev_area_merge set ownership = ((churn/?)*100)
+	where author = ? and path = ? and release = ?
+});
+my $update_ownership_cm = $dbh_ref->prepare(q{
+	update dev_area_merge set ownership = ((commits/?)*100)
+	where author = ? and path = ? and release = ?
+});
+
+$get_dev_area_merge_info->execute or die;
+my $ch0 = 0;
+while (my($author, $path, $release) = $get_dev_area_merge_info->fetchrow_array) {
+
+	$get_file_info->execute($release, $path) or die;
+	
+	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
+
+	if($file_total_churn == 0){
+		print "$ch0. [$path] File total churn is 0\n";
+		$update_ownership_cm->execute($file_total_commits, $author, $path, $release) or die;
+		$ch0++;
+	}else{
+		$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
+	}
+}
+
+$get_dev_area_merge_info->finish;
+$get_file_info->finish;
+
+$update_ownership_ch->finish;
+$update_ownership_cm->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see file_info.sql

### 2013-11-01 scripts/ownership/ownership_rtr.pl

@@ -1,0 +1,61 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_dev_area_rtr_info = $dbh_ref->prepare(q{
+	select  author, path, release from dev_area_rtr
+});
+my $get_file_info = $dbh_ref->prepare(q{
+		select  churn, commits from file_info where release = ? and path = ?
+	});
+my $update_ownership_ch = $dbh_ref->prepare(q{
+	update dev_area_rtr set ownership = ((churn/?)*100)
+	where author = ? and path = ? and release = ?
+});
+my $update_ownership_cm = $dbh_ref->prepare(q{
+	update dev_area_rtr set ownership = ((commits/?)*100)
+	where author = ? and path = ? and release = ?
+});
+
+$get_dev_area_rtr_info->execute or die;
+my $ch0 = 0;
+while (my($author, $path, $release) = $get_dev_area_rtr_info->fetchrow_array) {
+
+	$get_file_info->execute($release, $path) or die;
+	
+	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
+
+	if($file_total_churn == 0){
+		print "$ch0. [$path] File total churn is 0\n";
+		$update_ownership_cm->execute($file_total_commits, $author, $path, $release) or die;
+		$ch0++;
+	}else{
+		$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
+	}
+}
+
+$get_dev_area_rtr_info->finish;
+$get_file_info->finish;
+
+$update_ownership_ch->finish;
+$update_ownership_cm->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see file_info.sql

### 2013-11-01 scripts/release_times/merge_period.pl

@@ -11,33 +11,31 @@ my $config_path = shift @ARGV;
 if (!defined $config_path) {
 	$config_path = 'config';
 }
-die "Config file \'$config_path\' does not exist"
-	unless (-e $config_path);
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
 
 my %config =  Config::General::ParseConfig($config_path);
 
 my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
 
-my $query1 = $dbh_ref->prepare(q{select r.major, r.minor, r.micro, r.rc, r.date from git_refs_tags r, git_commit c where r.commit=c.commit order by c.committer_dt });
+my $query1 = $dbh_ref->prepare(q{select substring(r.path, '(linuxv[0-9]\.*[0-9]\.*[0-9]*\.?)') as release, r.major, r.minor, r.micro, r.rc, r.date from git_refs_tags r, git_commit c where r.commit=c.commit order by c.committer_dt });
 
 my $insert = $dbh_ref->prepare(q{insert into merge_period values (?,?,?,?,?,?)});
 
 $query1->execute or die;
 
 my $prev_date;
-while ( my($major, $minor, $micro, $rc, $date) = $query1->fetchrow_array) {
+while ( my($release, $major, $minor, $micro, $rc, $date) = $query1->fetchrow_array) {
 	if(not defined $prev_date){
 		 $prev_date = $date;
 	}
 	if (defined $rc and $rc == 1) {
-		my $release = 'linuxv'.$major.'.'.$minor.'.'.$micro;
 		print "$release -- $prev_date -- $date\n";
 		$insert->execute($release, $major, $minor, $micro, $prev_date, $date);
 	}
 	$prev_date = $date;
 }
 
-$update = $dbh_ref->prepare(q{update merge_period set days = extract(epoch from rc_date - previous)/86400});
+my $update = $dbh_ref->prepare(q{update merge_period set days = extract(epoch from rc_date - previous)/86400});
 $update->execute;
 
 $query1->finish;

### 2013-11-01 scripts/release_times/rd_period.pl

@@ -32,13 +32,12 @@ while ( my($release, $major, $minor, $micro, $rc_date) = $query1->fetchrow_array
 	my $release_date = $query2->fetchrow_array;
 	
 	if(defined $release_date){
-		my $release = 'linuxv'.$major.'.'.$minor.'.'.$micro;
 		print "$release -- $rc_date -- $release_date\n";
 		$insert->execute($release, $major, $minor, $micro, $rc_date, $release_date);
 	}
 }
 
-$update = $dbh_ref->prepare(q{update rd_period set days = extract(epoch from rel_date - rc_date)/86400});
+my $update = $dbh_ref->prepare(q{update rd_period set days = extract(epoch from rel_date - rc_date)/86400});
 $update->execute;
 
 $query1->finish;

### 2013-11-01 scripts/release_times/rel_period.pl

@@ -48,9 +48,9 @@ my $end_date = '';
 my ($query,$query_handler) = '';
 my $type = '';
 
-$get_release_dates->bind_columns(undef, \$release, \$major, \$minor, \$micro, \$rc, \$release_date);
+#$get_release_dates->bind_columns(undef, \$release, \$major, \$minor, \$micro, \$rc, \$release_date);
 
-while ( $get_release_dates->fetchrow_array ){
+while ( my($release, $major, $minor, $micro, $rc, $release_date) = $get_release_dates->fetchrow_array ){
 	print "$release :: $major - $minor - ".($micro ? $micro : "")." - ".($rc ? $rc : "")." - $release_date\n";
 	if(!$rc){
 		if($micro){
@@ -68,7 +68,8 @@ while ( $get_release_dates->fetchrow_array ){
 	$end_date = $release_date;
 	$start_date = $prev_release_date ? $prev_release_date : $release_date;
 
-	$query = "insert into git_rel_period(release, type, start_date, end_date) values('".$release."','".$type."','".$start_date."','".$end_date."')";
+	$query = "insert into rel_period(release, type, start_date, end_date) values('".$release."','".$type."','".$start_date."','".$end_date."')";
+
 	$query_handler = $dbh_ref->prepare($query);
 	$query_handler->execute() or die('Could not insert into git_rel_period');
 	

### 2013-11-01 scripts/release_times/rtr_period.pl

@@ -23,7 +23,7 @@ $query1 = $dbh_ref->prepare(q{
 	select	release, major, minor, micro, (
 			select	max(date) as release_date
 			from	git_refs_tags
-			where	rc != 0 and major=m.major and minor=m.minor and micro=m.micro
+			where	rc != 0 and major = m.major and minor = m.minor and micro = m.micro
 			group	by major, minor, micro order by release_date
 		) as rc_end_date
 	from merge_period m
@@ -40,13 +40,12 @@ while ( my($release, $major, $minor, $micro, $rc_end_date) = $query1->fetchrow_a
 	my $release_date = $query2->fetchrow_array;
 	
 	if(defined $release_date){
-		my $release = 'linuxv'.$major.'.'.$minor.'.'.$micro;
 		print "$release -- $rc_end_date -- $release_date\n";
 		$insert->execute($release, $major, $minor, $micro, $rc_end_date, $release_date);
 	}
 }
 
-$update = $dbh_ref->prepare(q{update rtr_period set days = extract(epoch from rel_date - rc_end_date)/86400});
+my $update = $dbh_ref->prepare(q{update rtr_period set days = extract(epoch from rel_date - rc_end_date)/86400});
 $update->execute;
 
 $query1->finish;

### 2013-11-04 paper1/paper1.tex
updated paper, worked on jaccard distance calculation for between releases and also between different segments within a release period

@@
 
-\subsection{Jaccard Distance}
-Once we found different releases and the release periods as well we calculate the developers' are to see what changes developers are doing in releases.
-We also want to know what is the difference being created by making changes between two consecuitive releases.
-If I explain it more then I can say, developers are working in many different files in a release and may work in a same file again for the next release or releases.
-
 \section{Preliminary Results}
 In this section we present results from several quantitative analysis of the archival data from the Linux Kernel development project.
-The measures we derive from these data are well-suited to address our research questions.
+The measures we derive from these data are well-suited to answer our research questions.
+Once we found different releases and the release periods as well as we calculate the work areas and code ownerships for developers we also want to know what is the difference being created by making changes between two consecutive releases.
+We want to see what is the difference among the releases also among the different sections MP, RDP, RTR in a release period.
+To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{17_jaccard} which is represented by the following equation.
+\begin{equation} J(A, B) =\frac{|A \cap B|}{|A \cup B|} \end{equation}
+So the Jaccard Distance can be obtained by subtracting the Jaccard coefficient from 1.
+\begin{equation} d_j(A, B) = 1 - J(A, B) = \frac{|A \cup B|-|A \cap B|}{|A \cup B|} \end{equation}
+Here A and B are two sets.
+For calculating Jaccard Distance between two releases we are considering the files that have been worked for in a particular release as the set A and files worked for in another release is set B.
+We found that Jaccard distance between two consecutive releases are not too high.
+For example jaccard bwteen release ``linuxv2.6.13'' and ``linuxv2.6.14'' is 0.925446 and bwteen ``linuxv2.6.14'' and ``linuxv2.6.15'' is 0.9191968.
+The higest Jaccard distance we have measured is 0.940 which is between 2.6.20 and 2.6.21 on the other hand the lowest distance is 0.906 between 2.6.30 and 2.6.31.
+Table 7 shows some Jaccard distances for release pairs and in Table 8 we see the Jaccard distance within the same releases between different perilds MP, RDP and RTR.
+
+\begin{table}[ht]
+\caption{Jaccard Distance between Releases}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c}				% centered columns (3 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+From 				& To		& Jaccard Distance	\\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+linuxv2.6.13			& linuxv2.6.14		& 0.925446	\\
+linuxv2.6.14			& linuxv2.6.15		& 0.919196	\\
+linuxv2.6.15			& linuxv2.6.16		& 0.917945	\\
+linuxv2.6.16			& linuxv2.6.17		& 0.916900 	\\
+linuxv2.6.17			& linuxv2.6.18		& 0.929941 	\\
+linuxv2.6.18			& linuxv2.6.19		& 0.937535	\\
+linuxv2.6.19			& linuxv2.6.20		& 0.935265 	\\
+linuxv2.6.20			& linuxv2.6.21		& 0.940366 	\\
+linuxv2.6.21			& linuxv2.6.22		& 0.920760 	\\
+linuxv2.6.22			& linuxv2.6.23		& 0.921652 	\\
+linuxv2.6.23			& linuxv2.6.24		& 0.929194 	\\
+linuxv2.6.24			& linuxv2.6.25		& 0.910464 	\\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+
+\begin{table}[ht]
+\caption{Jaccard Distance between Releases}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Release 				& J(MP, RDP)		& J(RDP, RTR)	& J(MP, RTR)	\\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+linuxv2.6.13			& 0.952060		& 0.921850		& 0.996786 \\
+linuxv2.6.14			& 0.958213		& 0.839313		& 0.988072 \\
+linuxv2.6.15			& 0.947005		& 0.936153		& 0.996408 \\
+linuxv2.6.16			& 0.949774		& 0.919361 		& 0.991275 \\
+linuxv2.6.17			& 0.938539		& 0.835925 		& 0.971014 \\
+linuxv2.6.18			& 0.946127		& 0.865967		& 0.990750 \\
+linuxv2.6.19			& 0.960241		& 0.845649 		& 0.993054 \\
+linuxv2.6.20			& 0.967823		& 0.804856 		& 0.995071 \\
+linuxv2.6.21			& 0.941798		& 0.835575 		& 0.989031 \\
+linuxv2.6.22			& 0.947115		& 0.928818 		& 0.997208 \\
+linuxv2.6.23			& 0.939658		& 0.909090 		& 0.995797 \\
+linuxv2.6.24			& 0.946806		& 0.871875 		& 0.989284 \\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+
+In table 8 last three columns representing the Jaccard distance between merge period and release development period, between release development and rush to release period, between merge period and rush to release period respectively.
 

### 2013-11-04 scripts/jaccard/dev_area_dev.pl

@@ -56,4 +56,4 @@ $dbh_ref->disconnect;
 
 __END__
 
-see dev_jac_releases.sql
+see dev_area.sql

### 2013-11-04 scripts/jaccard/dev_area_rel.pl

@@ -68,4 +68,4 @@ $dbh_ref->disconnect;
 
 __END__
 
-see dev_jac_releases.sql
+see dev_area.sql

### 2013-11-04 scripts/jaccard/dev_area_rtr.pl

@@ -53,4 +53,4 @@ $dbh_ref->disconnect;
 
 __END__
 
-see dev_jac_releases.sql
+see dev_area.sql

### 2013-11-04 scripts/jaccard/dev_jac.pl

@@ -1,87 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_release_dates = $dbh_ref->prepare(q{
-	select committer_dt, path as release 
-	from git_refs_tags r, git_commit c
-	where c.commit = r.commit
-	order by committer_dt
-});
-
-my $dev_union = $dbh_ref->prepare(q{
-	select count(*) 
-	from (
-		select author, path 
-		from dev_area_rel
-		where release = ? 
-		union
-		select author, path 
-		from dev_area_rel 
-		where release = ?
-	) as r
-});
-my $dev_intersection = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path
-		from dev_area_rel
-		where release = ?
-		INTERSECT
-		select author, path 
-		from dev_area_rel
-		where release = ?
-	) as r
-});
-
-$get_release_dates->execute() or die;
-
-#throw away the first because nothing is before it
-my($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
-
-($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
-
-while ( my($date, $release) = $get_release_dates->fetchrow_array) {
-
-	$dev_union->execute($prev_release, $release) or die;
-	my $union = $dev_union->fetchrow_array;
-	
-	$dev_intersection->execute($prev_release, $release) or die;
-	my $intersection = $dev_intersection->fetchrow_array;
-	
-	my $jac = $intersection/$union;
-	my $jac_dist = ($union - $intersection) / $union;
-	print " $prev_release ~ $release => $jac_dist\n";
-	
-	my $query_insert = $dbh_ref->prepare(q{
-		insert into rel_jac_dist values(?,?,?)
-	});
-	$query_insert->execute($prev_release, $release, $jac_dist) or die("Could not insert into rel_jac_dist");
-
-	$prev_date = $date;
-	$prev_release = $release;
-}
-
-$dev_intersection->finish;
[…]

### 2013-11-04 scripts/jaccard/jac_dist.pl

@@ -1,0 +1,182 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my ($prev_release, $release);
+my $jac_dist;
+
+my $get_releases = $dbh_ref->prepare(q{
+	select distinct p,date from (select substring(path, '(linuxv[0-9]*\.[0-9]?\.?[0-9]*)') as p, date from git_refs_tags) a order by a.date
+});
+
+my $query_insert = $dbh_ref->prepare(q{
+	insert into jac_dist(release) values(?)
+});
+
+# Inserting releases first
+$get_releases->execute() or die;
+($prev_release) = $get_releases->fetchrow_array;
+while ( ($release) = $get_releases->fetchrow_array) {
+	if(not $prev_release eq $release){
+		#$query_insert->execute($release) or die;
+	}
+	$prev_release = $release;
+}
+
+#************* Calculate Jaccard Distance Between Merge Period and Development Period *******
+#****************************** For ALl Releases ********************************************
+my $md_union = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path 
+		from dev_area_merge
+		where release = ? 
+		UNION
+		select author, path 
+		from dev_area_dev 
+		where release = ?
+	) as r
+});
+my $md_intersection = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path
+		from dev_area_merge
+		where release = ?
+		INTERSECT
+		select author, path 
+		from dev_area_dev
+		where release = ?
+	) as r
+});
+my $dr_union = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path 
+		from dev_area_dev
+		where release = ? 
+		UNION
+		select author, path 
+		from dev_area_rtr 
+		where release = ?
+	) as r
+});
+my $dr_intersection = $dbh_ref->prepare(q{
[…]

### 2013-11-04 scripts/jaccard/jac_dist_rel.pl

@@ -1,0 +1,91 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select distinct p,date from (select substring(path, '(linuxv[0-9]*\.[0-9]?\.?[0-9]*)') as p, date from git_refs_tags) a order by a.date
+});
+
+my $dev_union = $dbh_ref->prepare(q{
+	select count(*) 
+	from (
+		select author, path 
+		from dev_area_rel
+		where release = ? 
+		UNION
+		select author, path 
+		from dev_area_rel 
+		where release = ?
+	) as r
+});
+my $dev_intersection = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path
+		from dev_area_rel
+		where release = ?
+		INTERSECT
+		select author, path 
+		from dev_area_rel
+		where release = ?
+	) as r
+});
+
+my $query_insert = $dbh_ref->prepare(q{
+	insert into jac_dist_rel values(?,?,?)
+});
+
+my($jac_dist);
+
+$get_releases->execute() or die;
+
+#throw away the first because nothing is before it
+my($prev_release) = $get_releases->fetchrow_array;
+
+while ( my($release) = $get_releases->fetchrow_array) {
+	if(not $prev_release eq $release){
+	
+		$dev_union->execute($prev_release, $release) or die;
+		my $union = $dev_union->fetchrow_array;
+
+		$dev_intersection->execute($prev_release, $release) or die;
+		my $intersection = $dev_intersection->fetchrow_array;
+
+		print "$union - $intersection / $union\n";
+
+		if($union > 0){
+			$jac_dist = ($union - $intersection) / $union;
+		}else{
+			$jac_dist = 0;
+		}
+
+		print " $prev_release ~ $release => $jac_dist\n";
+
+		$query_insert->execute($prev_release, $release, $jac_dist) or die("Could not insert into jac_dist_rel");
+	}
[…]

### 2013-11-14 paper1/paper1.tex

@@
 Software projects are notorious for going over budget and schedule.
-Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{1_brooks}.
+Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{brooks_mythical}.
 This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor.
@@
 In this paper we study how RTR effects project organization and introduces technical debt.
+We want to propose a method to observe, analyze and summarize the results of revisions found near release.
+We intend to infer behavior of the developers related to the process around release time.
 The key research questions that we expect to answer with our methodology are as follows:
@@
 
-We observe a reallocation of the resources among the software development teams in a large project to identify that an improper reallocation or inappropriate reorganization causes a disruptive event take place in a software development process.
-We attempt to identify a project's different release times and calculate the difference between two consecutive releases to discover which are the new areas have been worked between two consecutive releases.
-The commit log data that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release.
-This information will help us to identify the criteria of the resources, their roles, file ownership and nativeness in the domain.
-This knowledge of nativeness will guide us understanding the method of reallocation.
-Very few research works have been performed regarding the re-allocation of resources.
-Robert van Engelen worked for similar kind of a research to understand the resource allocation dynamics across the software projects \cite{2_datta}.
-He mainly tried to reallocate development resources amongst projects for increasing the satisfactory level of consumer or customer while we are focusing on the impact on code-base like the complexity of script files.
-Robert proposed a project-entropy metric in his work to understand if there is any limit for a particular reallocation does not lead to user satisfaction.
-Here entropy is to represent disorder and chaos to understand degradation of software and its inherent complexity.
-In his work resources may not just be the developers but also can be any other resources necessary for a software project development.
+We observe a the developers working areas to understand the allocation of the resources within an open source software development project to identify that an improper reallocation or inappropriate reorganization causes a disruptive event take place in a software development process.
+We attempt to identify a project's different release times and calculate the difference between different development periods within a releases to identify which new areas are being worked on and what is the behavior of the developers between normal development period and the period when RTR is prompted before a releases.
+The historical data from git that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release as well as different periods in a stable release period.
+This information will help us to identify the criteria of the resources, their roles and behaviors, code ownership and defect density of the domains they are working in.
+
 We have organized this paper as follows.
-In Section 2, we describe some background and motivations followed by some summaries of related works in section 3.
-Section 4 will describe about the ownership of files and ownership of a set of files or a directories.
-We will try to understand how native a code-base is to a developer or a development team.
-In Section 5, some analysis to determine reallocation has been performed in a release or where reallocation needs to be performed will be presented.
-What changes in nativeness (∆ƞ) occurs after the reallocation.
-Section 6 will give us the result to show how change in nativeness puts impact on the outcome of a software.
-Finally section 7 will give us an idea of our future work followed by the conclusion in section 8.
+In Section 2, we describe some background and motivations followed by some summaries of related works in Section 3.
+Section 4 will describe methodology of our work and the data we are using for this research.
+In section 5 we will dicuss the results of the findings.
+Section 6 is going to cover the threats to validity.
+Finally section 7 will conclude the paper.
 
 \section{Background}
-Sometimes project members with interdependent tasks usually may not communicate effectively; coordination breakdowns occur, which results in integration failures \cite{3_kwan}.
-There may have lower developers productivity \cite{4_cataldo, 5_damian} which may cause inefficient run in the rush moments in a release period.
+There may have lower developers productivity \cite{cataldo_identification, damian_awareness} which may cause inefficient run in the rush moments in a release period.
 There is a substantial and important body of literature on risk in software engineering.
-Boehm identified the most important risks encountered by software project managers and described successful risk management practices \cite{6_boehm, 7_keil, 8_boehm}.
+Boehm identified the most important risks encountered by software project managers and described successful risk management practices \cite{boehm_software_risk, keil_framework, boehm_agile}.
 Some of the risks identified are related to disruptive events, such as the introduction of a new technology, but most are macro risks associated with running a project, such as developing the wrong functionality.
 General risk mitigation strategies can be difficult to apply to specific disruptive events.
-There may be various kinds of disruptive events for example, as a release approaches; developers take shortcuts that introduce technical debt.
+There may be various kinds of disruptive events for example, as a release approaches; developers take shortcuts that introduces technical debt.
 If it is not repaired, the long term quality of the system will suffer.
 Another example can be placed, if a lead developer who owns an important part of the code-base leaves and if steps to train other developers were not taken, it will become a dead area of the system and will be difficult to modify and maintain.
-Also often management reorganizes the developers on a company’s projects, with the result that developers move to code-bases for which they have less experience.
-The reorganization introduces new perspectives and expertise that can lead to innovation; however, it can also result in a drop in productivity and the unnecessary re-writing of large portions of the system that the new developers do not understand.
+Also often management reorganizes the developers on a company's projects during the rush period around the release time, with the result that developers move to code-bases for which they have less experience.
+The reorganization introduces new perspectives and expertise that can lead to faster release; however, it can also result in a drop in productivity and the unnecessary re-writing of large portions of the system that the new developers do not understand.
 In this paper, we plan to take the measures on this last example among them mentioned above.
-We want to study that proper re-organization or efficient re-allocation of resources based on meaningful criteria can bring better outcome of a software development project by identifying quantify outcomes (Example: number of defects found).
 
 \section{Related Works}
-Many people have worked with pretty relevant ideas but I didn't find many very similar to our motivation.
-Hindle worked on release pattern discovery via partitioning \cite{9_hindle}.
+Hindle worked on release pattern discovery via partitioning \cite{hindle_release_pattern} to propose an approach to characterize a project's behavior around the time of major and minor releases while we are trying to study the behavior of the development resources around the time of release.
 In this research they proposed a method of observing, analyzing and summarizing the results of metrics of revisions found near releases.
 They have characterized a project's behavior around the time of major and minor releases.
-This is done by partitioning the observed activities like the art-effect check-ins around the dates of major and minor releases, then look for reasonable patterns.
+This is done by partitioning the observed activities like the artiffect check-ins around the dates of major and minor releases, then look for reasonable patterns.
 Hindle divided the revisions in each release in 4 different classes, Source Code, Testing, Building, and Documentations.
-Actually this paper worked in a reverse way than Cook did \cite{10_cook}.
-Cook inserted sensors and monitors into the development process but Hindle and Michael analyzed the data to understand what happened in the past.
-Another research work we would like to mention was done by  Damian where they have worked on the role of domain knowledge and cross functional communication among the OOS development teams \cite{11_damian}.
-Posnett did some dual ecological measures of focus in software development \cite{12_posnett}.
+On the other hand Cook did an interesting job, he inserted sensors and monitors into the development process but Hindle analyzed the data to understand what happened in the past \cite{cook_automating}.
+Basically Hindle worked in a reverse way than Cook did.
+Another research work we would like to mention was done by  Damian where they have worked on the role of domain knowledge and cross functional communication among the OOS development teams \cite{damian_domain}.
+Posnett did some dual ecological measures of focus in software development \cite{posnett_ecological}.
 Posnett's measure was for the more general view that unifies developer focus and artifact ownership.
-Posnett analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from ehology to produce a novel and iii) conceptually unified view of measuring focus and ownership.
+He analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from ehology to produce a novel and iii) conceptually unified view of measuring focus and ownership.
 Another study was done by F.
-Rahman about the authorship of the code-bases in OSS development \cite{13_rahman}.
+Rahman about the authorship of the code-bases in OSS development \cite{rahman_ownership}.
 
@@
 We have collected the development history data of Linux kernel.
-Actually it is a database containing the all the commit log records by the Linux kernel developers since 2005.
+It is a data source containing the the historical data of Linux kernel development since 2005.
 We are going to present the steps involved in this process and then we will follow up with an application of our methodology in a case study.
-In order to address our research questions, we obtain key measures of project evolution from archival data had been preserved throughout the history of the Linux Kernel development project.
-All information on the OSS project is recorded in electronic form.
+In order to address our research questions, we obtain key measures of project evolution from the archival data collected from the distributed version contron (DVC) system of Git where all information of the OSS project ``Linux Kernel Development'' is recorded in electronic form.
 Many other OSS projects archive similar data, so the techniques used here can be replicated on any such project.
-We used the data elements extracted from the archival source to construct a number of measures on the commit log records to understand the behavior of the development resources (mainly developers).
+We used the data elements extracted from the archival source to construct a number of measures on the commit log records to understand the behavior of the developers.
+
 Our methodology can be summarized as: Extracting Data for revisions and releases (Section 4.1); Partitioning the version numbers (Section 4.2); Get time-span between each release (Section 4.3); Calculate developer areas (Section 4.4); Finding code ownership (Section 4.5).
@@
 
-\subsection{Extracting Data}
+\subsection{Data Extraction}
 We went for the VCS of a target project and either mirror the repository or download every revision and commit log history data.
@@
 We have used PSQL database to create tables in, to store our extracted data.
-These extracted will be analyzed by us later on.
+These extracted data will be analyzed by us later on.
 Per each revision the information extracted includes the commit id, tree id, author of the revision, date of revision, the name of the revised file, parent and child info for the revision and the detail log information.
-Once extraction is complete we are ready to partition the version numbers (Section 4.2) and duration  of each release (Section 4.3).
+Once extraction is completed we are ready to partition the version numbers (Section 4.2) and duration  of each release (Section 4.3).
+
+\subsubsection{Explanation}
+A Linux kernel development release version having maximum length of information does look like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
+If a release versioning looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release  in the seriese of the 6th major release of kernel version 2.
+``linuxv2.6.13\textbf{-rc1}'' says that after the 12th stable minor release had published, development for the next release has been started and rc1 is the first candidate on the way to the next release.
+It also ensures that next release is going to be another minor release which is ``linuxv2.6.13''.
+We have last couple of release candidates and the release date for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
+So we are having 340 releases including major, minor, micro and rc; 40 stable releases from ``linuxv2.6.12'' to ``linuxv3.11''.
+We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers.
+Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once. So we found them in our released wise datasets.
 
 \subsection{Partitioning Release Numbers}
-We stored the git commit log extracted data into a table named git commit and git revision where all the basic and log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
-By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can get determine which commit belongs to which version and release, and also what type of release that is as well.
+We stored the extracted git commit log data into the tables git\_commit and git\_revision where all the basic and log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
+By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can get determine which commit belongs to which version and release, and also what type of release that is.
 
-\begin{lstlisting}
-Find out the release candidates:
-update git_refs_tags set rc = cast(
-  substring(
-    path from
-      position( '-rc' in path )
-        + 3 for 2 
-  ) as integer
-) where path ~ E'-rc';
-\end{lstlisting}
-Find out major release version number:
-\begin{lstlisting}
-update git_refs_tags set major = cast(
-  substring(
-    path, 'v([0-9]+)\.?'
-      ) as integer
-);
-\end{lstlisting}
-Find out minor release version number:
-\begin{lstlisting}
-update git_refs_tags set minor = cast(
-  substring(
-    path, 'v[0-9]+\.([0-9]+)\.?'
-      ) as integer
-);
-\end{lstlisting}
-Find out micro release version number:
-\begin{lstlisting}
-update git_refs_tags set micro = cast(
-  substring(
-    path, 'v[0-9]+\.[0-9]+\.([0-9]+)\-?'
-      ) as integer
-);
-\end{lstlisting}
+We are getting the release dates with every single commit record.
+So we can understand which commit belongs to which version of release, is this a major release or minor or micro.
+Another information we have captured that is \textbf{rc} which means that the particular commit was a release candidate.
 
-We are getting the release dates also with every commit record.
-So we can understand which commit belongs to which version of release, is this a major release or minor or micro.
-Another information we have captured that is \textbf{rc} which means that the particular commit was for a release candidate.
-
-\subsubsection{Explanation}
-A Linux kernel development release version having maximum length of information looks like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
-If a release versioning looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release  under  the 6th major release of kernel version 2.
-``linuxv2.6.13\textbf{-rc1}'' says that after the 13th minor release been released development for the next release has been started and rc1 is the first candidate on the way to the next release.
-It doesn't ensure that next release is also going to be another minor release.
-
-\subsection{Get Time-Span Between Release}
+\subsection{Time-Span of Releases}
 Another information that we require is what are the durations of the releases of Linux kernel development.
-To achieve that we joined the table in figure 1 and the table ``git\_commit''.
-The following psql did the job pretty easily for us:
-\begin{lstlisting}
-select
-grt.path as release, grt.major, grt.minor,
-grt.micro, grt.rc, gc.committer_dt
-from
-git_refs_tags grt, git_commit gc
-where
-gc.commit = grt.commit
-order by
-gc.committer_dt
-\end{lstlisting}
-This query gives us all the dates of commit for each and every release, so we can easily find out the duration between two consecutive releases (all including release candidates RC).
-This information is more important to us because we need to see what is the actual development period and what is the merging or other fixing period within a release time-span and also we need to understand how developers are working, what is the impact of their changes made in the code-base during a particular release period.
+To achieve that we joined the table in figure 1 and the table ``git\_commit'' which gives us all the dates of commit for each and every release, so we can easily find out the duration between two consecutive releases (all including release candidates RC).
+This information is more important to us because we need to see what is the general development period and what is the merge which we can treat as RTR period within a release period of time.
+We also need to understand how developers are working, what is the impact of their changes made in the code-base during a particular release period later on.
 Table 1 shows a small portion of this information.
-Preior to calculate the areas of the developers in secion 4.4 we require this information.
+Preior to calculate the developers' areas in secion 4.4 we require this information.
 
@@
 linuxv2.6.13-rc3 & rc       & 2005-07-05 & 2005-07-13 \\
-linuxv2.6.13-rc4 & rc       & 2005-07-13 & 2005-07-28 \\
-linuxv2.6.13-rc5 & rc       & 2005-07-28 & 2005-08-02 \\
-linuxv2.6.13-rc6 & rc       & 2005-08-02 & 2005-08-07 \\
-linuxv2.6.13-rc7 & rc       & 2005-08-07 & 2005-08-23 \\
-linuxv2.6.13        & micro & 2005-08-23 & 2005-08-28 \\
-linuxv2.6.14-rc1 & rc       & 2005-08-28 & 2005-09-12 \\
-linuxv2.6.14-rc2 & rc       & 2005-09-12 & 2005-09-19 \\
-linuxv2.6.14-rc3 & rc       & 2005-09-19 & 2005-09-30 \\
-linuxv2.6.14-rc4 & rc       & 2005-09-30 & 2005-10-10 \\
-linuxv2.6.14-rc5 & rc       & 2005-10-10 & 2005-10-20 \\
+...			     & ...	   & ... 		     & ...\\
+...			     & ...	   & ... 		     & ... \\
+...			     & ...	   & ... 		     & ... \\
+linuxv3.11            & minor & 2013-08-25 & 2013-09-02 \\
+linuxv3.12-rc1     & rc       & 2013-09-02 & 2013-09-16 \\
+linuxv3.12-rc2     & rc       & 2013-09-16 & 2013-09-23 \\
+linuxv3.12-rc3     & rc       & 2013-09-23 & 2013-09-29 \\
 [1ex]							% adds vertical space
@@
 Note that the very first row has no information for the ``Start Date'' because we don't have any data prior to stable release ``linuxv2.6.12''.
-From the extraction we found complete records for releases ``linuxv2.6.13'' to ``linuxv2.6.39'' then ``linuxv3.0'' to ``linuxv3.11''.
-We have last couple of release candidates and the release date for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
-So we are having 340 releases including major, minor, micro and rc; 40 stable releases from ``linuxv2.6.12'' to ``linuxv3.11''.
-We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers.
-Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once. So we found them in our released wise datasets.
+From the extraction we found complete records for releases ``linuxv2.6.13'' to ``linuxv2.6.39'' then it is ``linuxv3.0'' to ``linuxv3.11''.
+Our farther works will be proceeded based on these 40 releases only.
+As we don't have the complete release information for 3.12 or later and also for 2.6.12 or earlier ones, we are going to not consider them in our farther calculation.
 
@@
 Developers are working throughout the release time.
-Developers' Are (DA) means the files developers work in.
-It doesn't refer the to file itself but it is important to understand which files are being touched by which developers.
+Here ``Developers' Area'' (DA) means the files developers work in within a release time.
+It doesn't refer to the file itself but it is important to understand which files are being touched by which developers.
 We see that authors are committing files almost everyday throughout a release.
 We have the commit log data in our hand and we know what is the duration for each and every releases (i.e.\ start and end dates).
-Now it is possible to find out which commits were made for which files by a developer within a given time range of a release.
+Now it is possible to find out which commits were made for which files by which developer within a certain time range of a release.
 
@@
 
-A relatively straightforward discipline of Linux Kernel Development team is followed with regard to the merging of patches for each release \cite{14_kernel}.
+A relatively straightforward discipline of Linux Kernel Development team is followed with regard to the merging of patches for each release \cite{linux_kernel}.
 At the beginning of each development cycle, the "merge window" is said to be opened.
@@
 So many developers are working from different development communities.
-We tried to investigate the "code ownership" \cite{15_mockus} evolved in Linux Kernel development.
+We tried to investigate the "code ownership" \cite{mockus_case_study} evolved in Linux Kernel development.
 Here code ownership is going to be represented as percentage value.
@@
 To determine a developer be a owner of a file we considering that if the developer makes changes more than 80\% of the total change that the file has got, then that developer can be treated as a owner of the codes of that file similarly as C.
-Gutwin did \cite{16_gutwin} for finding out the main developers' group for a project.
+Gutwin did \cite{gutwin_awareness} for finding out the main developers' group for a project.
 We already mentioned that 14569 individual files didn't have any change (addition or deletion) but was being committed at least once.
@@
 We want to see what is the difference among the releases also among the different sections MP, RDP, RTR in a release period.
-To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{17_jaccard} which is represented by the following equation.
+To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by the following equation.
 \begin{equation} J(A, B) =\frac{|A \cap B|}{|A \cup B|} \end{equation}

### 2013-11-14 paper1/paper1.tex
minor edits to research questions

@@
 \begin{enumerate}
+
+\item What is the release process used by the project?
 \item Do developers work on different areas of the system around the time of release?
 \item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?
-\item Do the areas of code that are modified around the time of release have higher defect densities than code that is modified during normal development?
 \end{enumerate}
+
+During the merge window, developers are free to provide any change that is ready for release.
+During the release candinate period, we would expect to see fixs on the files that were changed during the previous merge window.
+We measure this by comparing the Jac of merge window with the subsequent rc period, compared with the merge window and subsequent merge window.
 

### 2013-11-19 paper1/paper1.tex
Script for traversing git DAG is ok now. Updated paper.

@@
 \usepackage{booktabs}
+\usepackage{graphicx}
 \begin{document}
@@
 We intend to infer behavior of the developers related to the process around release time.
-The key research questions that we expect to answer with our methodology are as follows:
-\begin{enumerate}
-
-\item What is the release process used by the project?
-\item Do developers work on different areas of the system around the time of release?
-\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?
-\end{enumerate}
+The key research questions that we expect to answer with our methodology are described in section 1.1.
 
@@
 
-We observe a the developers working areas to understand the allocation of the resources within an open source software development project to identify that an improper reallocation or inappropriate reorganization causes a disruptive event take place in a software development process.
+We observe the developers' working areas to understand the allocation of the resources within an open source software development project to identify that an improper reallocation or inappropriate reorganization causes a disruptive event take place in a software development process.
 We attempt to identify a project's different release times and calculate the difference between different development periods within a releases to identify which new areas are being worked on and what is the behavior of the developers between normal development period and the period when RTR is prompted before a releases.
@@
 Finally section 7 will conclude the paper.
+
+\subsection{Research Questions}
+We have set our research questions focusing the key properties of software development process, allocation of developers throughout the process, especially for open source software development.
+First couple of research questions are to understand the basic structure and strategies of the development and release and merging process practiced by Linux.
+Rest of the questions are to understand the distribution of developers working areas and the behavior of developers in different segments of a release period.
+
+\renewcommand{\labelenumi}{Q\theenumi:}
+\begin{enumerate}
+\item What is the release process used by the project? \newline
+We are going to give a qualitative description of Linux Kernel development in brief to give anser to this question.
+\item How many developers are allocated troughout different segments of a release period? \newline
+Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different periods within a stable release period.
+\item Do developers work on different areas of the system around the time of release? \newline
+We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the merge period or merge window\cite{linux_kernel}.
+We are expecting this would be the RTR are in a release time where technical debt may be introduced.
+\item How do developers own code around t he system?
+Many developers are working on many files. We will find out which files has been churned mostly by which developer so that we can understand how developers are distributed among the system.
+\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)? \newline
+To answer this question we will look into the frequency of file churns made into files.
+Difference or distance of the files between normal development period and the RTR period or merge period of a release.
+\end{enumerate}
 
@@
 Per each revision the information extracted includes the commit id, tree id, author of the revision, date of revision, the name of the revised file, parent and child info for the revision and the detail log information.
-Once extraction is completed we are ready to partition the version numbers (Section 4.2) and duration  of each release (Section 4.3).
+Once extraction is completed we are ready to partition the version numbers (Section 4.3) and duration  of each release (Section 4.4).
 
@@
 We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers.
-Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once. So we found them in our released wise datasets.
+Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once.
+So we found them in our released wise datasets.
+
+\subsection{Finding Release Commits}
+As out first step we had to sort out all the commits together those are belonging to any of the releases that we have.
+We have all 400441 commits in our hand but though we can't plot them into a single time domain to say that these commits are for release 2.6.12 and these are for 2.6.13 and these are for 2.6.14 and so on because commits go on parallelly in git if there are multiple branches.
+If there are multiple branches, surely there are multiple merges and the commits prior to a crisscross merge are all ancestors of the heads of all subsequent branches \cite{bird_git}.
+Figure 1 shows how a git DAG looks like having so many crisscross merges in a busy branching snap-shot of the git DAG of Linux Kernel development.
+\begin{figure}
+\begin{center}
+\includegraphics[height=3.5in,width=2.5in]{gitdag.png}
+\caption{\small \sl Branching in git DAG for linux kernel development.}
+\end{center}
+\end{figure}
+So it is possible to make a commit months ago from today while several releases may have already been made in the mean time but that commit can belong to any future release.
+Commits that are being made to a branch may get merged with other branch or the head branch during the release period.
+This is why we had to track all the way down the trees for each of the 340 releases in the git DAG to find out which commit contributes to which release.
+We could do this using Git DAG Traversing (GDT) algorithm as shown in Algorithm 1.
+After applying GDT we collected 381152 out of 400441 commits those are well organized in the git DAG for Linux Kernel development.
+As we mentioned earlier that we have last couple of release candidates and the release date for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' and we are choping out them because we don't have complete data for version 2.6.12-rc as well as 3.12-rc releases, 19289 commits belonging to those releases.
+So finally we have 381152 commits for 340 releases in our hand to progress our work on.
+
+\begin{algorithm}
+\caption{Traverse Git DAG to find Commits within Releases}
+\begin{algorithmic}[1]
+\REQUIRE
+\STATE commit id for all releases
+\ENSURE
+\FOR{all commits}
+\STATE start from new commit, release R
+\STATE store commit in ``git\_commit\_release''
+\IF{has parent commit}
+	\FOR{each parent commit}
+		\IF{if parent commit has a release tag}
+			\STATE repeat step 1
+		\ELSIF{parent commit already stored}
+			\STATE compare release versions
+			\IF{release version not smaller than R}
+				\STATE update existing\_release $\gets$ R
+			\ENDIF
+		\ELSE
+			\STATE store parent commit in ``git\_commit\_release''
+			\STATE commit id $\gets$ parent commit id
+			\STATE repeat step 3
+		\ENDIF
+	\ENDFOR
+\ELSIF{no parent commit}
+	\STATE repeat step 1
+\ENDIF
+\ENDFOR
+\end{algorithmic}
+\end{algorithm}
 
@@
 We are getting the release dates with every single commit record.
-So we can understand which commit belongs to which version of release, is this a major release or minor or micro.
+So we can understand which commit belongs to which version of release; is this a major release or minor or micro.
 Another information we have captured that is \textbf{rc} which means that the particular commit was a release candidate.
@@
 We insert these information into another table so that we can use the data for our further analysis.
-
-The following pseudo code shows us the way of achieving the desired result in this section:
-
-\begin{algorithm}
-\caption{Calculate Developers Area}
-\begin{algorithmic}
-\REQUIRE $ $\\
-$commit\_date \geq  release\_start\_date$\\
-$commit\_date < release\_end\_date$
-\ENSURE
-\STATE $get all releases$
-
-\WHILE{$prev\_release\_date \leftarrow release\_start\_date\ and\ release \leftarrow release\_version$}
-\IF{$release$}
-	\IF{$commit\_date \geq  release\_start\_date$ and $commit\_date < release\_end\_date$}
-		\STATE $select author, path, commits, churn$
-		\STATE $insert data into table dev\_area\_rel$
-	\ENDIF
-\ENDIF
-\ENDWHILE
-\end{algorithmic}
-\end{algorithm}
-
 A relatively straightforward discipline of Linux Kernel Development team is followed with regard to the merging of patches for each release \cite{linux_kernel}.

### 2013-11-19 scripts/git_dagging/dag.pl

@@ -1,5 +1,4 @@
-#!/usr/bin/perl -w
-
+#!/usr/bin/perl
 use warnings;
 use strict;
 
@@ -15,47 +14,152 @@ die "Config file \'$config_path\' does not exist" unless (-e $config_path);
 
 my %config =  Config::General::ParseConfig($config_path);
 
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 0});
 
 my $get_revisions = $dbh_ref->prepare(q{
-	select	commit, path as release
-	from	git_refs_tags
-});
-my $get_parent = $dbh_ref->prepare(q{
-	select	parent
-	from	git_dag
-	where	child = ?
+	select	commit, path as release from git_refs_tags order by major, minor, micro, rc
 });
 
 $get_revisions->execute or die;
-
 while ( my($commit, $release) = $get_revisions->fetchrow_array) {
-	print "$commit\n";
-	_lookupParent($commit);
+	#if($release eq 'linuxv2.6.18'){
+	print "Starting from: $commit\n\n";
+	my $r = _isExistsInCommitRelease($commit);
+	if($r eq ''){
+		_storeCommit($commit, $release);
+		_lookupAndStoreParent($commit, $release);
+	}else{
+		print "Commit already exists: $commit\n";
+	}
+	#}
 }
 
-sub _lookupParent($commit)
-{
+sub _lookupAndStoreParent{
+	my ($commit, $release) = @_;
+	
+	my $get_parent = $dbh_ref->prepare(q{
+		select parent from git_dag where child = ?
+	});
 	$get_parent->execute($commit) or die;
-	if(my($parent) = $get_parent->fetchrow_array){
-		if(_lookupInCommitRelease($parent)){
-			# update release number for this commit id
+	
+	my ($num_parent) = $get_parent->rows;
+
+	print "$num_parent Parent(s) found\n";
+	
+	if($num_parent > 0){
+	    while ( my($parent) = $get_parent->fetchrow_array ){
+		if(_hasReleaseTag($parent)==1){
+		    print "stopping: there is a release tag at $parent\n";
+		    $dbh_ref->commit;
+		    return 1;
 		}else{
-			# store
+		    print "storing commit $parent\n";
[…]

### 2013-11-21 paper1/paper1.tex
working on paper. scripts updated for jaccard, developers' areas

@@
 \item What is the release process used by the project? \newline
-We are going to give a qualitative description of Linux Kernel development in brief to give anser to this question.
-\item How many developers are allocated troughout different segments of a release period? \newline
+We will be giving a qualitative description of Linux Kernel development in brief to give anser to this question.
+\item How many developers are allocated troughout different segments of a release period? What significant difference can be observed between the segments of an entire release period? \newline
 Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different periods within a stable release period.
+We will calculate Jaccard Distance to differentiate the behavior of developers during RTR and normal development period.
 \item Do developers work on different areas of the system around the time of release? \newline
@@
 It also ensures that next release is going to be another minor release which is ``linuxv2.6.13''.
-We have last couple of release candidates and the release date for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
-So we are having 340 releases including major, minor, micro and rc; 40 stable releases from ``linuxv2.6.12'' to ``linuxv3.11''.
+We have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
+So we are having 340 releases including major, minor, micro and rc; 39 stable releases from ``linuxv2.6.11'' to ``linuxv3.11'' having complete data with us.
 We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers.
@@
 
-\subsection{Finding Release Commits}
-As out first step we had to sort out all the commits together those are belonging to any of the releases that we have.
-We have all 400441 commits in our hand but though we can't plot them into a single time domain to say that these commits are for release 2.6.12 and these are for 2.6.13 and these are for 2.6.14 and so on because commits go on parallelly in git if there are multiple branches.
+ \subsection{Partitioning Release Numbers}
+We stored the extracted git commit log data into the tables git\_commit and git\_revision where all the basic and detail log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
+By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can determine which commit belongs to which version and release, and also what type of release that is.
+
+Commits those are made for pushing a release have release tags associated to them by which we can understand which commit belongs to which version of release; is this a major release or minor or a micro stable release.
+Another information we have captured that is \textbf{rc} which indicates that the particular commit was a release candidate.
+These information and splitting off release numbers will help us accumulating commits for different releases.
+
+\subsection{Finding Commits for Releases}
+We have to sort out and accumulate all the commits together those are belonging to any of the releases that we have.
+We have all 400441 commits in our hand but though we can't plot them into a single time domain to assign different set of commits to different release periods because development goes in parallel on different branches in git so commits also go in parallel.
 If there are multiple branches, surely there are multiple merges and the commits prior to a crisscross merge are all ancestors of the heads of all subsequent branches \cite{bird_git}.
@@
 After applying GDT we collected 381152 out of 400441 commits those are well organized in the git DAG for Linux Kernel development.
-As we mentioned earlier that we have last couple of release candidates and the release date for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' and we are choping out them because we don't have complete data for version 2.6.12-rc as well as 3.12-rc releases, 19289 commits belonging to those releases.
-So finally we have 381152 commits for 340 releases in our hand to progress our work on.
+As we mentioned earlier that we have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12''.
+We are choping out them because we don't have complete release commit data for version 2.6.12-rc as well as 3.12-rc releases.
+Out of 400441 commits 19289 are belonging to those releases.
+So finally we have 381152 commits for 340 releases in our database to progress our work on.
 
 \begin{algorithm}
-\caption{Traverse Git DAG to find Commits within Releases}
+\caption{GDT: to find Commits within Releases}
 \begin{algorithmic}[1]
@@
 
- \subsection{Partitioning Release Numbers}
-We stored the extracted git commit log data into the tables git\_commit and git\_revision where all the basic and log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
-By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can get determine which commit belongs to which version and release, and also what type of release that is.
-
-We are getting the release dates with every single commit record.
-So we can understand which commit belongs to which version of release; is this a major release or minor or micro.
-Another information we have captured that is \textbf{rc} which means that the particular commit was a release candidate.
-
 \subsection{Time-Span of Releases}
 Another information that we require is what are the durations of the releases of Linux kernel development.
-To achieve that we joined the table in figure 1 and the table ``git\_commit'' which gives us all the dates of commit for each and every release, so we can easily find out the duration between two consecutive releases (all including release candidates RC).
-This information is more important to us because we need to see what is the general development period and what is the merge which we can treat as RTR period within a release period of time.
+To achieve that we joined the table ``git\_refs\_tags'' where all the releases are stored including the splitted release numbers and the table ``git\_commit'' to give us all the dates of commits for each and every releases, so that we can easily find out the duration between two consecutive releases (including release candidates RC).
+This information will significantly help us because we need to see what is the general development period and what are the merge periods which can be treated as RTR period within a release period.
 We also need to understand how developers are working, what is the impact of their changes made in the code-base during a particular release period later on.
@@
 linuxv3.11            & minor & 2013-08-25 & 2013-09-02 \\
-linuxv3.12-rc1     & rc       & 2013-09-02 & 2013-09-16 \\
-linuxv3.12-rc2     & rc       & 2013-09-16 & 2013-09-23 \\
-linuxv3.12-rc3     & rc       & 2013-09-23 & 2013-09-29 \\
 [1ex]							% adds vertical space
@@
 
-Note that the very first row has no information for the ``Start Date'' because we don't have any data prior to stable release ``linuxv2.6.12''.
+Note that the very first row has no information for the ``Start Date'' because we don't have the  complete information prior to stable release ``linuxv2.6.12'' and we have chopped them out.
+This will not affect our methodology and measurements.
 From the extraction we found complete records for releases ``linuxv2.6.13'' to ``linuxv2.6.39'' then it is ``linuxv3.0'' to ``linuxv3.11''.
-Our farther works will be proceeded based on these 40 releases only.
-As we don't have the complete release information for 3.12 or later and also for 2.6.12 or earlier ones, we are going to not consider them in our farther calculation.
+Our farther works will be proceeded based on these 39 releases only.
+As we don't have the complete release information for 3.12 or later as well as for 2.6.12 and earlier ones.
 
@@
 
-\subsubsection{DA in a Release Period}
-We select all the release information from the table where we stored the releases with their corresponding time-span.
-After that we select author name and other relevant information from the joining of ``git\_revision'' and ``git\_commits'' tables for every release.
-We insert these information into another table so that we can use the data for our further analysis.
 A relatively straightforward discipline of Linux Kernel Development team is followed with regard to the merging of patches for each release \cite{linux_kernel}.
@@
 Strategically linux starts a new kernel release with the merging and fixing to get their development branch ready to start development for the next release.
-So there are two main segments in a release period, one is merge window or merge period (MP) and another is development window what we are going to call Release Development Period (RDP).
-
-Similarly we have calculated DA in both MP and RDP as described in the following subsections.
+So there are two main segments in a release period, one is merge window or merge period (MP) and another is development window what we are going to call Release Development Period (RDP)
 
@@
 For example if the date of release for ``linuxv2.6.12''  is 2005-06-17 and date of pushing the first RC for the next release ``linuxv2.6.13-rc1'' is 2005-06-29 then this time period of of 12 days is being called the merge window \cite{14_kernel} or MP.
-Table 2 shows some merging periods of different releases.
+We are considering this segment as a Rush To Release i.e.\ RTR as we mentioned earlier because thousands of commits are made during this time and developers remain in a rush to pack up merging all the branches those are to go with this release.
+Table 2 shows merging periods of some releases.
 
@@
 
-We understand DA or Developers' Area is the files in the code-base, developers are working from the dataset that we have in our hand.
-We have the commit logs and every record says about who committed the file when did he/she worked on the file.
-If we run an SQL query then we can easily find out for every author and for every particular file how many times it's been committed by an author and what changes (here, addition + deletion = churn) he/she has been made.
-So we are calculating the DA and storing the information into a table.
+We have the commits contributed to releases and every record explains us who committed the file when did this get churned.
+If we run an SQL query then we can easily find out for every author and for every particular file how many times it's been committed by an author and what churns (addition + deletion = churn) developer has made.
+We are calculate DA and store the information into a table.
 A part of that table is shown in table 3.
@@
 
-\subsubsection{DA in a RD Period and RTR}
-As like MP we can extract the RDP from the.
-RDP here in Linux Kernel development process is being considered as from the release date of RC1 (i.e.\ first release candidate opening the gate for the development of the next release) to the next release (major, minor or micro) date.
-For example if the date of release for ``linuxv2.6.13-rc1'' after releasing ``linuxv2.6.12''  is 2005-06-29 and date of publishing the next release ``linuxv2.6.13'' is 2005-08-28 then this time period of of 60 days is being called the RDP.
+\subsubsection{DA in RD Period}
+As like MP we can extract the RDP from the releases.
+RDP here in Linux Kernel development process is being considered as from the date of RC1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the next release (major, minor or micro) date.
+For example if the date of release for ``linuxv2.6.13-rc1'' after releasing ``linuxv2.6.12'' is 2005-06-29 and date of publishing the next release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the RDP.
 Table 4 is showing some development periods of different releases.
@@
 
-So along these RDs of each release period developers get involved in the development for the next release.
-As we mentioned earlier RTR may happen as the release approaches.
-Keeping this in our aim list we noticed an important slot in these RDs of releases.
+Along these RDs of each release period developers get involved in the development for the next release.
 We see in between two consecutive releases there is a merging period of time, after that development starts by pushing RCs and once RC releases stops and it takes some days of time for the preperation to publish the release.
-We are calling this last part as RTR Period because we asume RTR may happen in this period of time before release.
-Table 5 represents some releases with their corresponding RTR (i.e.\ from end date to rc and date of release).
+This is the end of the code development for this particular release.
+Usually bug fixes and small enhancement works take place here.
+We observed there are very few commits in this small period.
 
-\begin{table}[ht]
-\caption{RTR Periods}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Release 			& RC End Date	& Release Date	& Days \\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-linuxv2.6.13		& 2005-06-29	& 2005-08-28	& 5 \\
-linuxv2.6.14		& 2005-09-12	& 2005-10-27	& 8 \\
-linuxv2.6.15		& 2005-11-11	& 2006-01-02	& 9 \\
-linuxv2.6.16		& 2006-01-17	& 2006-03-20	& 8 \\
-linuxv2.6.17		& 2006-04-02	& 2006-06-17	& 12 \\
-linuxv2.6.18		& 2006-07-06	& 2006-09-19	& 7 \\
-linuxv2.6.19		& 2006-10-04	& 2006-11-29	& 14 \\
-linuxv2.6.20  		& 2006-12-13	& 2007-02-04	& 10 \\
-linuxv2.6.21		& 2007-02-20	& 2007-04-25	& 7 \\
-linuxv2.6.22		& 2007-05-12	& 2007-07-08	& 8 \\
-linuxv2.6.23		& 2007-07-22	& 2007-10-09	& 9 \\
-linuxv2.6.24		& 2007-10-23	& 2008-01-24	& 5 \\
-linuxv2.6.25		& 2008-02-10	& 2008-04-16	& 8 \\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-
-These information above will help us to answer our first research-question.
+These information above will greatly help us to answer our first couple of research questions.
 
@@
 
-\section{Preliminary Results}
+\section{Results}
 In this section we present results from several quantitative analysis of the archival data from the Linux Kernel development project.
 The measures we derive from these data are well-suited to answer our research questions.
-Once we found different releases and the release periods as well as we calculate the work areas and code ownerships for developers we also want to know what is the difference being created by making changes between two consecutive releases.
-We want to see what is the difference among the releases also among the different sections MP, RDP, RTR in a release period.
-To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by the following equation.
+
+\textit{What is the release process used by the project?}
+
+In the early 1990's the Linux kernel development was not so busy affair \cite{linux_kernel}.
+There were very small number of users and developers involved at that time.
+Developers use a loosely time-based release process.
+Linux publishes it's major kernel release in every two or three months.
+If we look at figure 2 the Release Duration Line represents how the stable releases are going on since 2005.
+From the figure we can see the average duration of each stable release is 62.47 although ``linuxv2.6.24'' was significantly hight as exception, it took 92.8 days.
+
+Linux Kernel development uses Rolling Release Development Model.
+Usually every micro release (ex.\ linuxv2.6.x) is a major kernel release with new features, internal API changes, and more.
+A minor release (ex.\ linuxv3.11) can have around  10 thousand changesets with several hundred thousands of churned lines of  codes (LOC).
+At the beginning of each stable release the merge window i.e.\ merge period gets opened and all the accepted and stable codes from the community are merged having around 1000 of churns everyday.
+Merge period approximately for 14 days as shown in the figure 2.
+The bottom line is representing the merge windows of every releases.
+We don't have the merge period data for the very first one that's why it's starting from 0.
+
+After getting all the major works merged development period for the next release is announced to be opened.
+If the next release is going to be linuxv2.6.14 then the release pushed at the end of the merge window will be called linuxv2.6.14-rc1.
+\textbf{-rc1} release indecates that the time to stabilize the next kernel has begun.
+These candidate releases continu to be pushed for once a week.
+If there is any bug fix or any high-priority change only then that goes to the main line during this period.
+With the continuous rc releases when the new kernel seems to be stable then the it goes for the stable release.
+Again after the core features are pushed to the main line then merge window gets opened and accepts all other feature developments, patchsets from other branches.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{linxrelmergfreq.png}
+\caption{\small \sl Durations of Linux Kernel development release}
+\end{center}
+\end{figure}
+
+As a summary, the description above helps to address some of the questions about how Linux Kernel development is organized.
+Answer to this first research question provides essential background for understanding our quantitative results.
+We will look into more detail of the development process, distribution of developers among the release segments as well as will try to find answers for our other research questions in the next sections.
+
+\subsection{Difference between release segments}
+\textit{How many developers are allocated troughout different segments of a release period? What significant differ-ence can be observed between the segments of an entire release period?}
+
+In order to see how many developers contribute to the new featcher developments and how many contribute in merging and fixing, review and accepting codes from the community during the merge period, we observed the developers' are in MP and developers' area in RDP.
+Out of all 381152 commits belonging to any of the 340 releases 292834 commits were made during the time of merge period which is 76.82\% (more than 2/3) of the total commits.
+
+We found that there was not a great number of people contributing during the time of merge periods.
+The number was pretty stedy for every releases while during the development periods we see increasing number of contributions of developers .
+Figure 3 illustrates this behaviour clearly.
+
+(TODO: Add figure for developers and churns in MP and RDP)
+
+Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ MP and RDP).
+To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by equation 3.
 \begin{equation} J(A, B) =\frac{|A \cap B|}{|A \cup B|} \end{equation}
-So the Jaccard Distance can be obtained by subtracting the Jaccard coefficient from 1.
+The Jaccard Distance can be obtained by subtracting the Jaccard Coefficient from 1.
 \begin{equation} d_j(A, B) = 1 - J(A, B) = \frac{|A \cup B|-|A \cap B|}{|A \cup B|} \end{equation}
@@
 The higest Jaccard distance we have measured is 0.940 which is between 2.6.20 and 2.6.21 on the other hand the lowest distance is 0.906 between 2.6.30 and 2.6.31.
-Table 7 shows some Jaccard distances for release pairs and in Table 8 we see the Jaccard distance within the same releases between different perilds MP, RDP and RTR.
+Table 7 shows some Jaccard distances for release pairs.
 
@@
 linuxv2.6.20			& linuxv2.6.21		& 0.940366 	\\
-linuxv2.6.21			& linuxv2.6.22		& 0.920760 	\\
-linuxv2.6.22			& linuxv2.6.23		& 0.921652 	\\
-linuxv2.6.23			& linuxv2.6.24		& 0.929194 	\\
-linuxv2.6.24			& linuxv2.6.25		& 0.910464 	\\
+...					& ...					& ... 	\\
+...					& ...					& ... 	\\
+linuxv2.6.30			& linuxv2.6.31		& 0.906517 	\\
+...					& ...					& ... 	\\
 [1ex]							% adds vertical space
@@
 
-\begin{table}[ht]
-\caption{Jaccard Distance between Releases}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Release 				& J(MP, RDP)		& J(RDP, RTR)	& J(MP, RTR)	\\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-linuxv2.6.13			& 0.952060		& 0.921850		& 0.996786 \\
-linuxv2.6.14			& 0.958213		& 0.839313		& 0.988072 \\
-linuxv2.6.15			& 0.947005		& 0.936153		& 0.996408 \\
-linuxv2.6.16			& 0.949774		& 0.919361 		& 0.991275 \\
-linuxv2.6.17			& 0.938539		& 0.835925 		& 0.971014 \\
-linuxv2.6.18			& 0.946127		& 0.865967		& 0.990750 \\
-linuxv2.6.19			& 0.960241		& 0.845649 		& 0.993054 \\
-linuxv2.6.20			& 0.967823		& 0.804856 		& 0.995071 \\
-linuxv2.6.21			& 0.941798		& 0.835575 		& 0.989031 \\
-linuxv2.6.22			& 0.947115		& 0.928818 		& 0.997208 \\
-linuxv2.6.23			& 0.939658		& 0.909090 		& 0.995797 \\
-linuxv2.6.24			& 0.946806		& 0.871875 		& 0.989284 \\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
+We can see in figure 4 that the Jaccard distances between MP and RDP for each release.
+The average distance is 0.959 but the average distance after 2.6.35 has gone up than the average up to this point.
+So we can say that developers work in very different areas after the merge period is over and all core developments, feature developments, merging other branches regarding the previous release is done.
+For linux kernel development in recent releases this difference has been increased then earlier times.
 
-In table 8 last three columns representing the Jaccard distance between merge period and release development period, between release development and rush to release period, between merge period and rush to release period respectively.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{jaccardmprdp.png}
+\caption{\small \sl Jaccard Distance between the MP and RDP}
+\end{center}
+\end{figure}
 

### 2013-11-21 scripts/jaccard/jac_dist.pl

@@ -18,28 +18,13 @@ my %config =  Config::General::ParseConfig($config_path);
 my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
 
 my ($prev_release, $release);
-my $jac_dist;
-
-my $get_releases = $dbh_ref->prepare(q{
-	select distinct p,date from (select substring(path, '(linuxv[0-9]*\.[0-9]?\.?[0-9]*)') as p, date from git_refs_tags) a order by a.date
-});
 
 my $query_insert = $dbh_ref->prepare(q{
 	insert into jac_dist(release) values(?)
 });
 
-# Inserting releases first
-$get_releases->execute() or die;
-($prev_release) = $get_releases->fetchrow_array;
-while ( ($release) = $get_releases->fetchrow_array) {
-	if(not $prev_release eq $release){
-		#$query_insert->execute($release) or die;
-	}
-	$prev_release = $release;
-}
-
-#************* Calculate Jaccard Distance Between Merge Period and Development Period *******
-#****************************** For ALl Releases ********************************************
+#************* Calculate Jaccard Distance Between Merge Period and Development Period *******#
+#****************************** For ALl Releases ********************************************#
 my $md_union = $dbh_ref->prepare(q{
 	select count(*)
 	from (
@@ -64,69 +49,24 @@ my $md_intersection = $dbh_ref->prepare(q{
 		where release = ?
 	) as r
 });
-my $dr_union = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path 
-		from dev_area_dev
-		where release = ? 
-		UNION
-		select author, path 
-		from dev_area_rtr 
-		where release = ?
-	) as r
-});
-my $dr_intersection = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path
-		from dev_area_dev
-		where release = ?
-		INTERSECT
-		select author, path 
-		from dev_area_rtr
-		where release = ?
-	) as r
-});
-my $mr_union = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path 
-		from dev_area_merge
-		where release = ? 
-		UNION
-		select author, path 
-		from dev_area_rtr 
[…]

### 2013-11-22 paper1/paper1.tex
worked on scripts for repotrs, updated paper for writing results

@@
 \begin{center}
-\includegraphics[height=3.5in,width=2.5in]{gitdag.png}
+\includegraphics[height=2.5in,width=2.5in]{gitdag.png}
 \caption{\small \sl Branching in git DAG for linux kernel development.}
@@
 % table heading
-Release 			& RD Start Date	& Release Date \\ [0.5ex]
+Release 			& RDP Start Date	& Release Date \\ [0.5ex]
 \hline 							% single horizontal line
@@
 
-Along these RDs of each release period developers get involved in the development for the next release.
+Along these RDPs of each release period developers get involved in the development for the next release.
 We see in between two consecutive releases there is a merging period of time, after that development starts by pushing RCs and once RC releases stops and it takes some days of time for the preperation to publish the release.
-This is the end of the code development for this particular release.
+This is the end of the core development for this particular release.
 Usually bug fixes and small enhancement works take place here.
@@
 Here code ownership is going to be represented as percentage value.
-Considering the data that we have for complete releases (``linuxv2.6.12'' to ``linuxv3.11'') we filtered the code files and we found 75138 distinct files that have been worked on.
+From the data that we have for complete releases (``linuxv2.6.13'' to ``linuxv3.11'') we found 75138 distinct files that have been churned or commited by any developers.
 We investigate the total number of commits, total number of churn for each and every file also how many developers contributed for these commits and changes.
-This information yet does not tell about the ownership.
-We need to find out ownership for every developers in different development areas in an RP.
-We already have the collection of developers working in different areas MP, RDP, RTR within an RP and stored them with corresponding file they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
+This information yet does not tell about the ownership, we need to find out ownership for every developers in different development areas in a Release Cycle.
+We already have the collection of developers working in MP and RDP within an RP and stored them with corresponding files they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
 We now update those information with the ownership information.
-For calculating ownership Equation 1 is applied.
+Equation 1 is the base for calculating ownership.
 \begin{equation}\omega=\frac{n}{N}*100\end{equation}
@@
 So we found them in our release wise datasets that's why in addition to Gutwin here considering commits also to determine ownership but only for files without any add or remove lines information.
-If a file has no addition or deletion information (we are calling it churn) in it's commit log but has beet committed by some one at least once then that or those authors may have the ownership for that file.
-So the equation 1 becomes like:
+If a file has no addition or deletion information (i.e.\ never been churned) in it's commit log but has beet committed by some one at least once then that or those authors may have the ownership for that file.
+So made little change in equation 1 which becomes like:
 \begin{equation} \omega = \left\{ \begin{array}{l l} n/N & \quad \text{if $N > 0$}\\ c/C & \quad \text{if $N = 0$} \end{array} * 100 \right.\end{equation}
 Where c is the number of commits made by the author and C is the total number of commits made for the particular file.
-We calculate code ownership for all different parts MP, RDP, RTR and also for an entire release period RP. Table 6 represents a part of the data where ownerships is calculated.
+We calculate code ownership for both MP and RDP.
+We also canculate general ownership for all the developers for all the files they have worked ever.
+Table 6 represents a part of the data which shows the ownerships of the developers in each release cycle.
 
@@
 With the continuous rc releases when the new kernel seems to be stable then the it goes for the stable release.
-Again after the core features are pushed to the main line then merge window gets opened and accepts all other feature developments, patchsets from other branches.
+Again after the core features are pushed to the main line, merge window gets opened and accepts all other feature developments, patchsets from other branches.
 
@@
 \includegraphics[height=1.7in,width=3.4in]{linxrelmergfreq.png}
-\caption{\small \sl Durations of Linux Kernel development release}
+\caption{\small \sl Durations of Merge Window and Release Cycle}
 \end{center}
@@
 
-In order to see how many developers contribute to the new featcher developments and how many contribute in merging and fixing, review and accepting codes from the community during the merge period, we observed the developers' are in MP and developers' area in RDP.
-Out of all 381152 commits belonging to any of the 340 releases 292834 commits were made during the time of merge period which is 76.82\% (more than 2/3) of the total commits.
+In order to see how many developers contribute to the new featcher developments and how many contribute in merging and fixing, review and accepting codes from the community during the merge period, we observed the developers' area in MP and developers' area in RDP.
+Out of all 381152 commits belonging to any of the 340 releases 292834 commits were made during the time of merge period which is 76.82\% (more than 2/3) of the total.
+These commits were made by 14621 individual developers where 4884 of them contributed in both merge period (around the time of RTR) and the release development period.
+As we have found that in total 8057 developers worked in the period of MP so we can say half of the developers those work during RTR are dedicated to this special period and half of the total are shared (work in both MP and RDP).
 
@@
 The number was pretty stedy for every releases while during the development periods we see increasing number of contributions of developers .
-Figure 3 illustrates this behaviour clearly.
+In figure 3 we see the boxplot showing that around 600 developers contributes during the merge period while in release revelopment period around 1000 developers work and this contribution is in increasing order as shown in figure 4.
 
-(TODO: Add figure for developers and churns in MP and RDP)
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{devMP_RDP_box.png}
+\caption{\small \sl Developers working in MP \& RDP}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{devRDP.png}
+\caption{\small \sl Increasing contribution in RDP}
+\end{center}
+\end{figure}
 
@@
 Here A and B are two sets.
-For calculating Jaccard Distance between two releases we are considering the files that have been worked for in a particular release as the set A and files worked for in another release is set B.
-We found that Jaccard distance between two consecutive releases are not too high.
-For example jaccard bwteen release ``linuxv2.6.13'' and ``linuxv2.6.14'' is 0.925446 and bwteen ``linuxv2.6.14'' and ``linuxv2.6.15'' is 0.9191968.
-The higest Jaccard distance we have measured is 0.940 which is between 2.6.20 and 2.6.21 on the other hand the lowest distance is 0.906 between 2.6.30 and 2.6.31.
-Table 7 shows some Jaccard distances for release pairs.
-
-\begin{table}[ht]
-\caption{Jaccard Distance between Releases}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c}				% centered columns (3 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-From 				& To		& Jaccard Distance	\\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-linuxv2.6.13			& linuxv2.6.14		& 0.925446	\\
-linuxv2.6.14			& linuxv2.6.15		& 0.919196	\\
-linuxv2.6.15			& linuxv2.6.16		& 0.917945	\\
-linuxv2.6.16			& linuxv2.6.17		& 0.916900 	\\
-linuxv2.6.17			& linuxv2.6.18		& 0.929941 	\\
-linuxv2.6.18			& linuxv2.6.19		& 0.937535	\\
-linuxv2.6.19			& linuxv2.6.20		& 0.935265 	\\
-linuxv2.6.20			& linuxv2.6.21		& 0.940366 	\\
-...					& ...					& ... 	\\
-...					& ...					& ... 	\\
-linuxv2.6.30			& linuxv2.6.31		& 0.906517 	\\
-...					& ...					& ... 	\\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-
-We can see in figure 4 that the Jaccard distances between MP and RDP for each release.
-The average distance is 0.959 but the average distance after 2.6.35 has gone up than the average up to this point.
-So we can say that developers work in very different areas after the merge period is over and all core developments, feature developments, merging other branches regarding the previous release is done.
-For linux kernel development in recent releases this difference has been increased then earlier times.
+For calculating Jaccard Distance between two releases we are considering the files that have been worked for, in a particular release.
+If set A is the set of files worked in MP and files worked for in another release is set B then In figure 5 the Jaccard distances between MP and RDP for each release can be represented.
+The average distance is 0.959 but the average distance after release ``linuxv2.6.39'' has gone up than the average up to this point.
+So we can say that developers work in very different areas once the merge window is closed and all core developments, feature developments, merging other branches regarding the previous release are done.
+Regarding the increase in the Jaccard Distance for the minor releases (since linuxv3.0) we can say that in minor releases developers work in more versatile areas than micro releases.
 
@@
 \end{figure}
+
+\subsection{Developers' contributions around the time of release}
+\textit{Do developers work on different areas of the system around the time of release?}\newline
+\textit{How do developers own code around t he system?}
+
+Developers work for the software continuously.
+Some are working for the core development some are working for the fixing and minor enhancements and some for feature developments, planning to merge new feature with any future release but we would like to understand what amount of changes they make during the time of regular development period and what amount the changes they make during the time of RTR.
+We also want to know about the code ownership of the developers around the time of release and general code ownership i.e.\ which files a developer has worked making more than 80% chruns in his lifetime.
+
+We examine contribution in writing code and making churns. Figure 6 plots the representation of code churns and ownerships per developer.
+
+(TODO: line chart representing churned files line, owned files line. x-axis : developers, y-axis : files churned)
 

### 2013-11-22 scripts/dev_area/dev_area_dev.pl

@@ -1,0 +1,60 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_rc_dates = $dbh_ref->prepare(q{
+	select	release, rc_date, rel_date
+	from	rd_period
+});
+
+my $dev_area = $dbh_ref->prepare(q{
+	insert into dev_area_dev
+        select 
+		author,
+		?,
+		r.new_path,
+		count(*) as commits,
+		sum(add+remove) as churn,
+		0 as ownership
+	from 
+		git_commit_release cr, git_revision r, git_commit c
+                                    
+	where 
+		c.commit = r.commit
+		and r.commit = cr.commit
+		and c.committer_dt > ?
+		and c.committer_dt <= ?
+	group by
+		author, r.new_path
+});
+#This will insert the information about the changes that developers are making in a period of merging in a release.
+
+$get_rc_dates->execute() or die;
+
+while ( my($release, $rc_date, $rel_date) = $get_rc_dates->fetchrow_array) {
+	print "$release -- $rc_date --  $rel_date\n";
+
+	$dev_area->execute($release, $rc_date, $rel_date) or die; 
+}
+
+$get_rc_dates->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see dev_area.sql

### 2013-11-22 scripts/dev_area/dev_area_merge.pl

@@ -1,0 +1,57 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_merge_dates = $dbh_ref->prepare(q{
+	select	release, previous, rc_date
+	from	merge_period order by major, minor, micro
+});
+
+my $dev_area = $dbh_ref->prepare(q{
+	insert into dev_area_merge
+        select
+		author,
+		?,
+		r.new_path,
+		count(*) as commits,
+		sum(add+remove) as churn,
+		0 as ownership
+	from
+		git_commit_release cr, git_revision r, git_commit c
+	where 
+		c.commit = r.commit
+		and r.commit = cr.commit
+		and c.committer_dt > ?
+		and c.committer_dt <= ?
+	group by
+		author, r.new_path
+});
+#This will insert the information about the changes that developers are making in a period of merging in a release.
+
+$get_merge_dates->execute() or die;
+
+while ( my($release, $prev_date, $rc_date) = $get_merge_dates->fetchrow_array) {
+	print "$release -- $prev_date --  $rc_date\n";
+
+	$dev_area->execute($release, $prev_date, $rc_date) or die;
+}
+
+$get_merge_dates->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-11-22 scripts/jaccard/dev_area_rel.pl

@@ -40,10 +40,11 @@ my $dev_area = $dbh_ref->prepare(q{
 		sum(add+remove) as churn,
 		0
 	from 
-		git_revision r, git_commit c
+		git_commit_release cr, git_revision r, git_commit c
                                     
 	where 
-		c.commit = r.commit 
+		c.commit = r.commit
+		and r.commit = cr.commit
 		and c.committer_dt > ? 
 		and c.committer_dt <= ?
 	group by

### 2013-11-22 scripts/jaccard/developer_file_ownership.pl

@@ -1,0 +1,47 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+#This file calculates the area of developers for the life time. How many commits are made
+#by an author for a particular file, how many churns are made and what is the percentage of his/her 
+#ownership to that file.
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $dev_area = $dbh_ref->prepare(q{
+	insert into developer_file_ownership
+        select 
+		author,
+		r.new_path,
+		count(*) as commits,
+		sum(add+remove) as churn,
+		0
+	from 
+		git_commit_release cr, git_revision r, git_commit c
+                                    
+	where 
+		c.commit = r.commit
+		and r.commit = cr.commit
+	group by
+		author, r.new_path
+});
+$dev_area->execute() or die;
+$dev_area->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+see dev_area.sql

### 2013-11-22 scripts/ownership/developer_file_ownership.pl

@@ -1,0 +1,82 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_auth_info = $dbh_ref->prepare(q{
+	select distinct author,path from developer_file_ownership;
+});
+
+my $get_file_info = $dbh_ref->prepare(q{
+	select
+		sum(add+remove) as churn,
+		count(*) as commits
+	from
+		git_commit_release cr, git_revision r, git_commit c
+	where 
+		c.commit = r.commit and r.commit=cr.commit
+		and path = ?
+	group by new_path;
+});
+
+my $update_ownership_ch = $dbh_ref->prepare(q{
+	update developer_file_ownership set ownership = ((churn/?)*100)
+	where author = ? and path = ?
+});
+my $update_ownership_cm = $dbh_ref->prepare(q{
+	update developer_file_ownership set ownership = ((commits/?)*100)
+	where author = ? and path = ?
+});
+
+#my @files;
+
+#push @files, $get_file_info->fetchall_arrayref;
+
+#foreach my $row (@files) {
+#    foreach my $element (@$row) {
+#        print "@$_\n" for $element;
+#    }
+#}
+
+$get_auth_info->execute() or die;
+
+my $ch0 = 0;
+while (my($author,$path) = $get_auth_info->fetchrow_array){
+	$get_file_info->execute($path) or die;
+
+	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
+	print "$author => $path\n";
+	if($file_total_churn == 0){
+		print "$ch0. [$path] File total churn is 0\n";
+		$update_ownership_cm->execute($file_total_commits, $author, $path) or die;
+		$ch0++;
+	}else{
+		$update_ownership_ch->execute($file_total_churn, $author, $path) or die;
+	}
+}
+
+$get_auth_info->finish;
+$get_file_info->finish;
+$update_ownership_ch->finish;
+$update_ownership_cm->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+
+
+

### 2013-11-22 scripts/release_times/stable_releases.pl

@@ -1,0 +1,54 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_release_days = $dbh_ref->prepare(q{
+	select
+		major, minor, micro,
+		min(committer_dt),
+		max(committer_dt),
+		extract(epoch from max(committer_dt) - min(committer_dt))/86400 num_days
+	from
+		git_refs_tags r, git_commit c
+	where
+		c.commit = r.commit
+	group by major, minor, micro
+	order by major, minor, micro
+});
+my $insert_query = $dbh_ref->prepare(q{
+	insert into stable_releases values(?,?,?,?);
+});
+
+$get_release_days->execute() or die;
+
+
+while ( my($major, $minor, $micro, $start_date, $end_date, $days) = $get_release_days->fetchrow_array ){
+	my $release = 'linuxv'.$major.'.'.$minor;
+	if($micro){
+		$release .= '.'.$micro;
+	}
+	
+	$insert_query->execute($release, $start_date, $end_date, $days) or die('Could not insert into git_rel_period');
+}
+
+$get_release_days->finish;
+$insert_query->finish;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-11-22 paper1/paper1.tex
updating paper and new scripts for reports

@@
 Linux publishes it's major kernel release in every two or three months.
-If we look at figure 2 the Release Duration Line represents how the stable releases are going on since 2005.
+If we look at figure 2 the upper Line represents how the stable releases are going on since 2005.
 From the figure we can see the average duration of each stable release is 62.47 although ``linuxv2.6.24'' was significantly hight as exception, it took 92.8 days.
+The bottom line which is much steady than the upper one is representing the durations of merge period in each stable release.
+If we put the releases in a time domain we can see a picture shown in figure 3 where we see that the stable releases are all going on maintaining almost a similar frequency and similar pattern.
+The highest picks are the merge periods then the smaller picks between the highest ones are representing the rc releases.
+For more clear view we have plotted only 100 releases of all 340 releases.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{relTimeDomain100.png}
+\caption{\small \sl Time Domain for Releases}
+\end{center}
+\end{figure}
+
 As a summary, the description above helps to address some of the questions about how Linux Kernel development is organized.
@@
 The number was pretty stedy for every releases while during the development periods we see increasing number of contributions of developers .
-In figure 3 we see the boxplot showing that around 600 developers contributes during the merge period while in release revelopment period around 1000 developers work and this contribution is in increasing order as shown in figure 4.
+In figure 4 we see the boxplot showing that around 600 developers contributes during the merge period while in release revelopment period around 1000 developers work and this contribution is in increasing order as shown in figure 5.
 
@@
 For calculating Jaccard Distance between two releases we are considering the files that have been worked for, in a particular release.
-If set A is the set of files worked in MP and files worked for in another release is set B then In figure 5 the Jaccard distances between MP and RDP for each release can be represented.
+If set A is the set of files worked in MP and files worked for in another release is set B then In figure 6 the Jaccard distances between MP and RDP for each release can be represented.
 The average distance is 0.959 but the average distance after release ``linuxv2.6.39'' has gone up than the average up to this point.
@@
 \textit{Do developers work on different areas of the system around the time of release?}\newline
-\textit{How do developers own code around t he system?}
+\textit{How do developers own code around the system?}
 
+We are supposed to find the answers for the two research questions together in this section.
 Developers work for the software continuously.
-Some are working for the core development some are working for the fixing and minor enhancements and some for feature developments, planning to merge new feature with any future release but we would like to understand what amount of changes they make during the time of regular development period and what amount the changes they make during the time of RTR.
+Some are working for the core development some people are for the fixing and minor enhancements and some for feature developments, planning to merge new features with any up coming release but we would like to understand what number of files they change during the time of regular development period and how many during the time of RTR.
+How many of them they really own and how many files they work that they do not own.
 We also want to know about the code ownership of the developers around the time of release and general code ownership i.e.\ which files a developer has worked making more than 80% chruns in his lifetime.
 
-We examine contribution in writing code and making churns. Figure 6 plots the representation of code churns and ownerships per developer.
+Since the release of ``linuxv2.6.13'' till ``linuxv3.11'' 2889 developers out of 14621 worked for the files they owned.
+They have worked for other files also.
+So the percentage of working with owned files is 19.82% through out the life time (here 2.6.13 to 3.11).
+
+We examine the contribution in writing code and making churns by the developers. Figure 7 plots the cumulative representation of code churns and ownerships per developer.
 

### 2013-11-22 scripts/dev_area/dev_area_merge_owned.pl

@@ -1,0 +1,46 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $select_dev_area = $dbh_ref->prepare(q{
+        select 
+		author,
+		release,
+		path,
+		ownership
+	from 
+		dev_area_merge                                   
+});
+my $update = $dbh_ref->prepare(q{
+	update dev_area_merge set owned = 1 where author=? and release=? and path=?
+});
+$select_dev_area->execute() or die;
+
+while ( my($author, $release, $path, $ownership) = $select_dev_area->fetchrow_array) {
+	if($ownership > 80){
+		print "$author - $release -- $ownership\n";
+		$update->execute($author, $release, $path) or die;
+	}
+}
+
+$select_dev_area->finish;
+$update->finish;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-11-22 scripts/jaccard/developer_file_ownership.pl

@@ -1,47 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-#This file calculates the area of developers for the life time. How many commits are made
-#by an author for a particular file, how many churns are made and what is the percentage of his/her 
-#ownership to that file.
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $dev_area = $dbh_ref->prepare(q{
-	insert into developer_file_ownership
-        select 
-		author,
-		r.new_path,
-		count(*) as commits,
-		sum(add+remove) as churn,
-		0
-	from 
-		git_commit_release cr, git_revision r, git_commit c
-                                    
-	where 
-		c.commit = r.commit
-		and r.commit = cr.commit
-	group by
-		author, r.new_path
-});
-$dev_area->execute() or die;
-$dev_area->finish;
-$dbh_ref->disconnect;
-
-__END__
-
-see dev_area.sql

### 2013-11-22 scripts/ownership/developer_file_ownership.pl

@@ -28,7 +28,8 @@ my $get_file_info = $dbh_ref->prepare(q{
 	from
 		git_commit_release cr, git_revision r, git_commit c
 	where 
-		c.commit = r.commit and r.commit=cr.commit
+		c.commit = r.commit
+		and r.commit=cr.commit
 		and path = ?
 	group by new_path;
 });

### 2013-11-22 scripts/ownership/developer_file_ownership_owned.pl

@@ -1,0 +1,46 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_auth_info = $dbh_ref->prepare(q{
+	select distinct author,path,ownership from developer_file_ownership;
+});
+
+my $update_ownership = $dbh_ref->prepare(q{
+	update developer_file_ownership set owned = 1 where author = ? and path = ?
+});
+
+$get_auth_info->execute() or die;
+
+while (my($author,$path,$ownership) = $get_auth_info->fetchrow_array){
+	
+	if($ownership > 80){
+		print "$author => $path : $ownership\n";
+		$update_ownership->execute($author, $path) or die;
+	}
+}
+
+$get_auth_info->finish;
+$update_ownership->finish;
+$dbh_ref->disconnect;
+
+__END__
+
+
+
+

### 2013-11-27 paper1/paper1.tex
working on result writing and calculating. pictures are added

@@
 We are expecting this would be the RTR are in a release time where technical debt may be introduced.
-\item How do developers own code around t he system?
+\item Do developers mostly work on their own codes around the system?
 Many developers are working on many files. We will find out which files has been churned mostly by which developer so that we can understand how developers are distributed among the system.
@@
 \begin{center}
-\includegraphics[height=1.7in,width=3.4in]{devMP_RDP_box.png}
+\includegraphics[height=1.7in,width=3.4in]{devMPRDPBox.png}
 \caption{\small \sl Developers working in MP \& RDP}
@@
 \textit{Do developers work on different areas of the system around the time of release?}\newline
-\textit{How do developers own code around the system?}
+\textit{Do developers mostly work on their own codes around the system?}
 
@@
 How many of them they really own and how many files they work that they do not own.
-We also want to know about the code ownership of the developers around the time of release and general code ownership i.e.\ which files a developer has worked making more than 80% chruns in his lifetime.
+We also want to know about the code ownership of the developers around the time of release and general code ownership i.e.\ which files a developer has worked making more than 80\% chruns in lifetime.
 
 Since the release of ``linuxv2.6.13'' till ``linuxv3.11'' 2889 developers out of 14621 worked for the files they owned.
-They have worked for other files also.
-So the percentage of working with owned files is 19.82% through out the life time (here 2.6.13 to 3.11).
+Although they have worked for other files that they do not own.
+So the percentage of working with owned files is 19.82\% through out the life time (release 2.6.13 to 3.11).
+We examine the contribution in writing code and making churns by the developers to understand the behaviour and to see if the impact of this 19.82\% on the graph.
+Figure 7 plots the cumulative representation of churnes files and percentage of owned files per developer for a particular release ``linuxv2.6.13''.
+If I say in details, in the increase of every 10 developers it is observed that developers work increasingly more unknown files than the files they own or they are very familier to.
+We see the similar picture for other releases too.
+So we can say that in Linux Kernel development developers work in more unfamilier files than the most familier (i.e.\ more than 80\%) ones.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{cumulativeChurnOwnershipPercent.png}
+\caption{\small \sl Cumulative Number of Churns vs Percentage of Owned Files in release 2.3.13}
+\end{center}
+\end{figure}
 
-We examine the contribution in writing code and making churns by the developers. Figure 7 plots the cumulative representation of code churns and ownerships per developer.
+To understand the distribution of the developers around the system we also found that during these release periods 8057 developers have experience of working in the merge meriod and 14621 developers worked in the release development period as we already mentioned earlier but we noted that 4884 developers work in both the parts.
+So almost half of the developers that work in merge period also work in the release development period.
+Figure 8 shows the Venn diagram.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{devDistMPRDP.png}
+\caption{\small \sl Developers' Distribution in Merge Period and Development Period}
+\end{center}
+\end{figure}
 
-(TODO: line chart representing churned files line, owned files line. x-axis : developers, y-axis : files churned)
+If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in general ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a very significant difference as shown in figure 9.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{ownedFilesMPRDPBox.png}
+\caption{\small \sl Percentage of working in owned files during Merge Period and the that of life time}
+\end{center}
+\end{figure}
+We still interested to see the correlation of $\omega$\textit{P} with $\Omega$\textit{P} to get more idea about the role of merge period over the role in general for any other time in release development.
+Figure 10 plots the graphical representation of the correlation.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{owPercentMPRDPCorr.png}
+\caption{\small \sl X axis: \% of working in owned files during Merge Period, Y axis: \%of working in owned files during Release Development Period}
+\end{center}
+\end{figure}
+As we find the residual standard error is 33.69 on 8055 degrees of freedom  and the multiple R-squared value is 0.04803, Adjusted R-squared value is 0.04791.
+We found the F-statistic 406.4 and the p-value is < 2.2e-16.
+
+If we add other independent variables ``churn frequency in merge period (\c{c}\textit{F})'', ``churn frequency in general (\c{C}\textit{F})'' and ``average ownership for the life time ($\omega$\textit{Avg})'' then the correlation looks like as shown in figure 11.
+
+So, finally we can say that in merge periods developers work on more native codes while during the regular release development period the percentage of working with native code is very less in number.
 

### 2013-11-27 scripts/reports/cumul.pl

@@ -1,0 +1,46 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $rel_churn_ownper = $dbh_ref->prepare(q{
+	select author, count(path) as files, sum(churn) as tch, round(cast(sum(owned) as numeric)/cast(count(path) as numeric),2)*100 as wp 
+	from dev_area_merge 
+	where release='linuxv2.6.13' 
+	group by author order by author;
+});
+my $insert = $dbh_ref->prepare(q{insert into dev_churn_ownp_cumul values(?,?,?,?)});
+
+$rel_churn_ownper->execute() or die;
+
+my $i=0;
+my ($totalFiles,$totalChurn,$totalOwnPercent) = 0;
+while(my($author,$files,$tch,$wp) = $rel_churn_ownper->fetchrow_array){
+	$i++;
+	$totalChurn = $totalChurn + $tch;
+	$totalFiles = $totalFiles + $files;
+	$totalOwnPercent = $totalOwnPercent + $wp;
+	if($i%10==0){
+		$insert->execute($i,$totalFiles/10,$totalOwnPercent/10,$totalChurn/10);
+	}
+}
+
+$rel_churn_ownper->finish;
+$insert->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-11-27 scripts/reports/cumulative_dev_churn_file_ownp.r

@@ -1,0 +1,8 @@
+relDCOP <- read.csv("~/Documents/git/rupak/scripts/reports/cumulative_dev_churn_file_ownp.rpt")
+
+xrange <- range(relDCOP$devs)
+
+plot(relDCOP$devs, relDCOP$churns, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of developers", ylab="")
+lines(relDCOP$devs, relDCOP$ownp, type="l", lwd=1.5, lty=2, col="blue")
+
+legend(xrange[1],150000,c("churns","ownership"), col=c("red","blue"),lty=c("solid","dashed"))

### 2013-11-28 paper1/paper1.tex
updated paper for result on rq3,4,5(partial), written new scripts

@@
 We are expecting this would be the RTR are in a release time where technical debt may be introduced.
-\item Do developers mostly work on their own codes around the system?
+\item Do developers work in others' code in a high proportion during the rush period?
 Many developers are working on many files. We will find out which files has been churned mostly by which developer so that we can understand how developers are distributed among the system.
@@
 
-\subsubsection{DA in RD Period}
+\subsubsection{DA in Release Development Period}
 As like MP we can extract the RDP from the releases.
@@
 \textit{Do developers work on different areas of the system around the time of release?}\newline
-\textit{Do developers mostly work on their own codes around the system?}
+\textit{Do developers work in others' code in a high proportion during the rush period?}
 
@@
 
-If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in general ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a very significant difference as shown in figure 9.
+If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in general ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a significant difference as shown in figure 9.
 \begin{figure}
@@
 \end{figure}
-We still interested to see the correlation of $\omega$\textit{P} with $\Omega$\textit{P} to get more idea about the role of merge period over the role in general for any other time in release development.
-Figure 10 plots the graphical representation of the correlation.
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3in]{owPercentMPRDPCorr.png}
-\caption{\small \sl X axis: \% of working in owned files during Merge Period, Y axis: \%of working in owned files during Release Development Period}
-\end{center}
-\end{figure}
-As we find the residual standard error is 33.69 on 8055 degrees of freedom  and the multiple R-squared value is 0.04803, Adjusted R-squared value is 0.04791.
-We found the F-statistic 406.4 and the p-value is < 2.2e-16.
 
-If we add other independent variables ``churn frequency in merge period (\c{c}\textit{F})'', ``churn frequency in general (\c{C}\textit{F})'' and ``average ownership for the life time ($\omega$\textit{Avg})'' then the correlation looks like as shown in figure 11.
+Now, to predict if developers work in others' code in a high proportion during the rush period we would like to observe the correlation of the \% of working in owned files in merge period with other independent variables ``churn percentage in merge period (\c{c}\textit{P})'', ``churn percentage in general (\c{C}\textit{P})'', ``average ownership ($\omega$\textit{Avg})'' and \% of wirking in owned files in general ($\Omega$\textit{P}).
+Table 6 shows the Spearman rank correlation among the \% of working with owned files and other variables.
+We can see there is no statistically significant positive relationship between the measures and the \% of working in owned files
 
-So, finally we can say that in merge periods developers work on more native codes while during the regular release development period the percentage of working with native code is very less in number.
+All three correlations Kendall, Pearson and Spearman calculates that the percentage of working with owned files doesn't to any other variables strongly as we predicted seeing figure 7 having a very poor percentage of contribution (19.82\%) on owned files during the merge period of time.
+But we can see a significant strong relation between the \% of churn in general and \% of churn in merge period which is 0.7199 according to Kendall, 0.7028 according to Pearson and 0.8446 according to Spearman.
+Also the correlation between the \% of churn in general and the average ownership is strong according to Spearman model which is 0.7982.
+We are giving the priority to Spearman model because Spearman correlation is a more robust correlation technique \cite{nagappan_defect}.
+If we consider the following models with our variables:
+\renewcommand{\labelenumi}{M\theenumi:}
+\begin{enumerate}
+\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}}
+\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}}
+\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}, \c{c}\textit{P}}
+\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}, \c{c}\textit{P}, \c{C}\textit{P}}
+\end{enumerate}
+then we see the linear regression model for the \% of working with owned code measure using all the predictors has an R-squared value 0.1132 with residual standard error is 32.52 on 8053 degrees of freedom, Adjusted R-squared value is 0.1139.
+F-statistic is 342.8 and the p-value is < 2.2e-16.
+R-square is a measure of variance in the dependent variable that is accounted for by the model built using the predictors \cite{nagappan_defect}.
+R-square is a measure of the fit for the given data set.
+It cannot be interpreted as the quality of the dataset to make future predictions.
+
+\begin{table}[ht]
+\caption{Cross Correlations}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c c c}			% centered columns (6 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Measures  & $\omega$\textit{P} & $\Omega$\textit{P} & $\omega$\textit{Avg} & \c{c}\textit{P} & \c{C}\textit{P} \\ [0.5ex]
+\hline 							% single horizontal line
+% inserting body of the table
+$\omega$\textit{P}		& 1.0000	& 0.2897	& 0.4496	& 0.3325	& 0.2826 \\
+$\Omega$\textit{P}	& --			& 1.0000	& 0.7110	& 0.3979	& 0.5075 \\
+$\omega$\textit{Avg}	& --			& --			& 1.0000 	& 0.6754 	& \textbf{0.7982} \\
+\c{c}\textit{P}			& -- 			& -- 		 	& --			& 1.0000	& \textbf{0.8446} \\
+\c{C}\textit{P}			& -- 			& -- 			& -- 			& -			& 1.0000 \\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+
+So, finally we can say that in merge periods developers work in more native codes while during the regular release development period the percentage of working with native code is very low in number although this percentage of working in owned code during merge period does not significantly relate to other co-factors.
+
+\subsection{Developers' focus on code-base around the time of release}
+\textit{Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?}
+Answer to the following questions are going to be looked for to answer this research question:
+\renewcommand{\labelenumi}{q\theenumi:}
+\begin{enumerate}
+\item{How many times a file has been committed during merge period?}
+\item{How many authors made those commits?}
+\item{How many churns were made to the files during each commit?}
+\item{What is the time interval for the commits for a file?}
+\item{How many files each developer deals with during merge period?}
+\item{How many files each developer deals with during release development period?}
+\item{What is the jaccard distance J(mp1, rdp1), J(rdp1, rdp0) and J(rdp0, mp1)?}
+\end{enumerate}
+We found the relation J(mp1, rdp1) > J(rdp1, rdp0) < J(rdp0, mp1) for the minor releases is significant but among the micro stable releases this relation is not significant at all.
 
@@
 
-\section{Acknowledgments}
-... ... ...
 \bibliographystyle{abbrv}

### 2013-11-30 paper1/paper1.tex
updating scripts and revising papers. a big mistake was found correcting all the  scripts and texts

@@
 Regardless of the causes, the rush to release stresses developers and often requires developers to work on unusual, high priority or critical areas of the system.
-In this paper we study how RTR effects project organization and introduces technical debt.
-We want to propose a method to observe, analyze and summarize the results of revisions found near release.
+In this paper we study how RTR may effect project organization and introduce technical debt.
+We want to propose a method to observe, analyze and summarize the results of revisions found around releases.
 We intend to infer behavior of the developers related to the process around release time.
@@
 During the release candinate period, we would expect to see fixs on the files that were changed during the previous merge window.
-We measure this by comparing the Jac of merge window with the subsequent rc period, compared with the merge window and subsequent merge window.
+We measure this by comparing the Jaccard distance of merge window with the subsequent rc period, compared with the merge window and subsequent merge window.
 
-We observe the developers' working areas to understand the allocation of the resources within an open source software development project to identify that an improper reallocation or inappropriate reorganization causes a disruptive event take place in a software development process.
-We attempt to identify a project's different release times and calculate the difference between different development periods within a releases to identify which new areas are being worked on and what is the behavior of the developers between normal development period and the period when RTR is prompted before a releases.
+We observe the developers' working areas to understand the allocation of the resources within an open source software development project to understand the reallocation or distribution takes place in a software development process which may cause disruptive events.
+We attempt to identify the project's different release times and calculate the difference between different development periods within a releases cycle to identify which new areas are being worked on and what is the behavior of the developers between normal development period and the period when RTR is prompted.
 The historical data from git that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release as well as different periods in a stable release period.
-This information will help us to identify the criteria of the resources, their roles and behaviors, code ownership and defect density of the domains they are working in.
+This information will help us to identify the criteria of the resources, their roles and behaviors, code ownerships of the domains they are working in.
 
 We have organized this paper as follows.
-In Section 2, we describe some background and motivations followed by some summaries of related works in Section 3.
-Section 4 will describe methodology of our work and the data we are using for this research.
+In Section 2, we describe some background and motivations followed by the summaries of related works in Section 3.
+Section 4 will describe methodology of our work and explanation of the data we are working with for this research.
 In section 5 we will dicuss the results of the findings.
-Section 6 is going to cover the threats to validity.
-Finally section 7 will conclude the paper.
+Finally section 6 will conclude the paper.
 
@@
 We have set our research questions focusing the key properties of software development process, allocation of developers throughout the process, especially for open source software development.
-First couple of research questions are to understand the basic structure and strategies of the development and release and merging process practiced by Linux.
-Rest of the questions are to understand the distribution of developers working areas and the behavior of developers in different segments of a release period.
+First couple of research questions are to understand the basic structure and strategies of the development and release and merging process practiced by Linux Kernel development team.
+Rest of the questions are to understand the distribution of developers' working areas and the behavior of developers in different segments of a release period.
 
@@
 
-Our methodology can be summarized as: Extracting Data for revisions and releases (Section 4.1); Partitioning the version numbers (Section 4.2); Get time-span between each release (Section 4.3); Calculate developer areas (Section 4.4); Finding code ownership (Section 4.5).
-Calculating Jaccard Distance for different development areas.
+Our methodology can be summarized as: Extracting Data for revisions and releases (Section 4.1); Partitioning the release version numbers (Section 4.2); Finding the commits associated to a version of Kernel (Section 4.3); Get time-span between each release (Section 4.4); Calculate developer areas (Section 4.5); Finding code ownership (Section 4.6).
 
@@
 Developers are working throughout the release time.
-Here ``Developers' Area'' (DA) means the files developers work in within a release time.
+Here ``Developers' Area'' means the files developers work in within a release cycle.
 It doesn't refer to the file itself but it is important to understand which files are being touched by which developers.
-We see that authors are committing files almost everyday throughout a release.
-We have the commit log data in our hand and we know what is the duration for each and every releases (i.e.\ start and end dates).
+We see that authors are committing files almost everyday throughout a release but this does not make sure that these commits are going to the next release because commits are being made in different branches and all branches are not supposed to get merged to the next release.
+We have the commit log data in our hand and we know what is the duration for each and every release (i.e.\ start and end dates).
 Now it is possible to find out which commits were made for which files by which developer within a certain time range of a release.
@@
 The bulk of changes for a new development cycle (and all of the major changes) will be merged during this time, at a rate approaching 1,000 changes ("patches," or "changesets") per day.
-Strategically linux starts a new kernel release with the merging and fixing to get their development branch ready to start development for the next release.
-So there are two main segments in a release period, one is merge window or merge period (MP) and another is development window what we are going to call Release Development Period (RDP)
+Strategically linux starts a new kernel release with the merging to get their development branch ready to start development for the next release.
+So there are two main segments in a release period, one is merge window or merge period (MP) where all the developments works get merged together from different branches.
+So we can say this is the main development period of a release.
+A merge period remains opened exactly for two weeks \cite{linux_kernel}, many developers are working in many other branches to develop new features once they are ready to push it to the main kernel then they wait for the upcoming merge window and once it's merge period they all contribute their works for the next release during this Merge Period.
+Some developers who are mainly responsible to merge new developments verify and accept the new changes and merge them into the main kernel.
+Another perod in a release cycle is the period of candidate releases which gets opened once the merge window is closed where mainly the bug fixing of minor enhancement works are to be worked on and pushes by small candidate releases.
+Once all the fixing and enhancements are done for all the codes that had been merged into the main kernel, the release is published.
+We are calling this period of development as the release period (RP) because no new feature development works do not get accepted during this time, it is just the period prior to publishing a new release.
 
-\subsubsection{DA in a Merge Period}
-Merge Perid can be determined from the previous release (any of major, minor or micro releases) date to the first RC date.
-For example if the date of release for ``linuxv2.6.12''  is 2005-06-17 and date of pushing the first RC for the next release ``linuxv2.6.13-rc1'' is 2005-06-29 then this time period of of 12 days is being called the merge window \cite{14_kernel} or MP.
-We are considering this segment as a Rush To Release i.e.\ RTR as we mentioned earlier because thousands of commits are made during this time and developers remain in a rush to pack up merging all the branches those are to go with this release.
-Table 2 shows merging periods of some releases.
+\subsubsection{Developers' Area in a Merge Period}
+Merge Perid can be determined from the previous release date (of any of major, minor or micro releases) to the date of rc-1 (i.e.\ date of the first candidate release).
+For example if the date of release for ``linuxv2.6.12''  is 2005-06-17 and date of pushing the rc-1 for the next release ``linuxv2.6.13'' is 2005-06-29 then this time period of of 12 days is going to be being called the merge window.
+We are considering this segment as a Rush To Release or RTR because thousands of commits gets pushed in the main branch during this time and developers remain in a rush to pack up merging all the branches those are to go with this release.
+Table 2 shows merge periods of some releases.
 
@@
 % table heading
-Release 			& Start Date		& RC Date \\ [0.5ex]
+Release 			& Start Date		& End Date \\ [0.5ex]
 \hline 							% single horizontal line
@@
 We have the commits contributed to releases and every record explains us who committed the file when did this get churned.
-If we run an SQL query then we can easily find out for every author and for every particular file how many times it's been committed by an author and what churns (addition + deletion = churn) developer has made.
-We are calculate DA and store the information into a table.
+If we run an SQL query then we can easily find out for every author and for every particular file how many times a it has been committed by an author and how many churns (addition + deletion = churn) developer has made.
+We calculate developers' working areas and store the information into a table.
 A part of that table is shown in table 3.
@@
 \begin{table}[ht]
-\caption{DA in Merge Period}  % title of Table
+\caption{Developers' Areas in Merge Period}  % title of Table
 \centering 						% used for centering table
@@
 
-In this table we see in a merging period inside a release period D.
+In this table we see in a merge period within a release cycle D.
 S.
-Miller has made change in pci.h file only once wich the churn number 8.
-In the similar way we calculate DA in RDP and RTR period as well.
+Miller has made change in pci.h file only once where he has made 8 churns.
+In the similar approach we calculate developers' areas in release period and also for merge period.
 
-\subsubsection{DA in Release Development Period}
-As like MP we can extract the RDP from the releases.
-RDP here in Linux Kernel development process is being considered as from the date of RC1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the next release (major, minor or micro) date.
-For example if the date of release for ``linuxv2.6.13-rc1'' after releasing ``linuxv2.6.12'' is 2005-06-29 and date of publishing the next release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the RDP.
+\subsubsection{Developers' Areas in Release Period}
+As like merge period we can extract developers working in code files during release period.
+Release Period here in Linux Kernel development process is being considered as since the date of rc-1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the date of the next stable release.
+For example if the date of rc-1 for ``linuxv2.6.13'' after releasing ``linuxv2.6.12'' is 2005-06-29 and the date of publishing the release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the Release Period.
 Table 4 is showing some development periods of different releases.
@@
 \begin{table}[ht]
-\caption{Release Development Periods}  % title of Table
+\caption{Release Periods}  % title of Table
 \centering 						% used for centering table
@@
 % table heading
-Release 			& RDP Start Date	& Release Date \\ [0.5ex]
+Release 			& Start Date		& End Date \\ [0.5ex]
 \hline 							% single horizontal line
@@
 
-Along these RDPs of each release period developers get involved in the development for the next release.
-We see in between two consecutive releases there is a merging period of time, after that development starts by pushing RCs and once RC releases stops and it takes some days of time for the preperation to publish the release.
-This is the end of the core development for this particular release.
-Usually bug fixes and small enhancement works take place here.
-We observed there are very few commits in this small period.
-
-These information above will greatly help us to answer our first couple of research questions.
+These information above will greatly help us to answer our first couple of research questions and to progress our further works.
 
 \subsection{Finding Code Ownership}
-So many developers are working from different development communities.
+So many developers are working from different development communities throught different development branches.
 We tried to investigate the "code ownership" \cite{mockus_case_study} evolved in Linux Kernel development.
-Here code ownership is going to be represented as percentage value.
-From the data that we have for complete releases (``linuxv2.6.13'' to ``linuxv3.11'') we found 75138 distinct files that have been churned or commited by any developers.
-We investigate the total number of commits, total number of churn for each and every file also how many developers contributed for these commits and changes.
-This information yet does not tell about the ownership, we need to find out ownership for every developers in different development areas in a Release Cycle.
-We already have the collection of developers working in MP and RDP within an RP and stored them with corresponding files they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
+Here code ownership is going to be represented as a percentage of making churns or commits by a developer with respect to the total churns or commits made to a particular file.
+From the data that we have for complete releases (``linuxv2.6.13'' to ``linuxv3.11'') we found 75138 distinct files that have been churned or commited by developers.
+We investigate the total number of commits, total number of churns for each and every file, we also investigate how many developers contributed for these commits and changes.
+This information yet does not tell about the ownership, we need to find out ownership for each developer in different development areas in a release cycle.
+We already have the collection of developers working in merge period and release period within a release cycle and stored them with corresponding files they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
 We now update those information with the ownership information.
@@
 Where $\omega$ is the ownership and n is the number of total changes made by an atuthor of a file, N is the total number of changes made for a particular file.
-To determine a developer be a owner of a file we considering that if the developer makes changes more than 80\% of the total change that the file has got, then that developer can be treated as a owner of the codes of that file similarly as C.
+To determine a developer be a owner of a file we are considering that if the developer makes changes more than 80\% of the total churn that has been made by all contributors so far for that file, then that developer can be called as a owner of that file, similarly as C.
 Gutwin did \cite{gutwin_awareness} for finding out the main developers' group for a project.
 We already mentioned that 14569 individual files didn't have any change (addition or deletion) but was being committed at least once.
-So we found them in our release wise datasets that's why in addition to Gutwin here considering commits also to determine ownership but only for files without any add or remove lines information.
-If a file has no addition or deletion information (i.e.\ never been churned) in it's commit log but has beet committed by some one at least once then that or those authors may have the ownership for that file.
-So made little change in equation 1 which becomes like:
+So we found them in our release wise datasets that's why in addition to Gutwin here we are involving commits to determine ownerships but only for those files that do not have churn information.
+If a file has no addition or deletion information in it's commit log but has been committed by some one at least once then that or those authors may have the ownership for that file.
+So, we have made a little change in equation 1 which becomes like:
 \begin{equation} \omega = \left\{ \begin{array}{l l} n/N & \quad \text{if $N > 0$}\\ c/C & \quad \text{if $N = 0$} \end{array} * 100 \right.\end{equation}
 Where c is the number of commits made by the author and C is the total number of commits made for the particular file.
-We calculate code ownership for both MP and RDP.
+We calculate code ownership for both Merge Period and Release Period.
 We also canculate general ownership for all the developers for all the files they have worked ever.
@@
 \end{table}
-The example given above is calculated for the developers worked for different files in different releases.
-Ownership is calculated for all the developers in release periods.
-In the same way we have calculated what is the ownership value for a developer to a particular file in the merge period (MP) in a release, development period (RDP) in a release and RTR period ind a release.
+The example given above is calculated for finding ownerships of developers worked for different files in different releases.
+Ownership is calculated for all the developers in release periods as well as in merge period.
+In addition we have calculated which file is owned by which developer and also the percentage of working with owned files during merge meriod and release period seperately.
+These extractions will help us drawing the results from our findings to answer our 3rd and 4th research questions.
 
@@
 
-In order to see how many developers contribute to the new featcher developments and how many contribute in merging and fixing, review and accepting codes from the community during the merge period, we observed the developers' area in MP and developers' area in RDP.
-Out of all 381152 commits belonging to any of the 340 releases 292834 commits were made during the time of merge period which is 76.82\% (more than 2/3) of the total.
-These commits were made by 14621 individual developers where 4884 of them contributed in both merge period (around the time of RTR) and the release development period.
-As we have found that in total 8057 developers worked in the period of MP so we can say half of the developers those work during RTR are dedicated to this special period and half of the total are shared (work in both MP and RDP).
+In order to see how many developers contribute to the new featcher developments and how many contribute in merging and fixing, review and accepting codes from the community during the merge period, we observed the developers' area in Merge Period and developers' area in Release Period.
+Out of all 381152 commits belonging to all 340 releases 292926 commits were made during the time of merge period which is 76.85\% (more than 2/3) of the total.
+These commits were made by 14621 individual developers.
+We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for thse releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later.
+11209 developers work in merge period and 7625 developers work around the release period.
+We found that 4908 developers contribute in both merge period and the release period that means near about half (43.78\%) of the developers work during the merge period are shared that means they work in both merge and release periods.
 
-We found that there was not a great number of people contributing during the time of merge periods.
-The number was pretty stedy for every releases while during the development periods we see increasing number of contributions of developers .
-In figure 4 we see the boxplot showing that around 600 developers contributes during the merge period while in release revelopment period around 1000 developers work and this contribution is in increasing order as shown in figure 5.
+In figure 4 we see the boxplot showing that a very large number of developers contribute during the merge period which is in a sense the main development period because all the development branches get merged together during this time, all the new features come into the main branch of the kernel.
+In release period significantly small number of developers work and this number looks pretty steady for all the releases only a couple of high number appeared in two releases as we see in figure 4.
+The number of contributions during the main development period over releases looks going up in an increasing manner as shown in figure 5.
+On the other hand the bottom line for the release developers is pretty steady for all the releases.
 
@@
 \begin{center}
-\includegraphics[height=1.7in,width=3.4in]{devMPRDPBox.png}
-\caption{\small \sl Developers working in MP \& RDP}
+\includegraphics[height=1.7in,width=3.4in]{devsMPRPbox.png}
+\caption{\small \sl Developers working in MP \& RP}
 \end{center}
@@
 \begin{center}
-\includegraphics[height=1.7in,width=3.4in]{devRDP.png}
+\includegraphics[height=1.7in,width=3.4in]{devsMPRP.png}
 \caption{\small \sl Increasing contribution in RDP}
@@
 
-Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ MP and RDP).
+Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ Merge Period MP and Release Period RP).
 To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by equation 3.
@@
 For calculating Jaccard Distance between two releases we are considering the files that have been worked for, in a particular release.
-If set A is the set of files worked in MP and files worked for in another release is set B then In figure 6 the Jaccard distances between MP and RDP for each release can be represented.
-The average distance is 0.959 but the average distance after release ``linuxv2.6.39'' has gone up than the average up to this point.
-So we can say that developers work in very different areas once the merge window is closed and all core developments, feature developments, merging other branches regarding the previous release are done.
-Regarding the increase in the Jaccard Distance for the minor releases (since linuxv3.0) we can say that in minor releases developers work in more versatile areas than micro releases.
+If set A is the set of files worked in MP and files worked for in another release is set B then In figure 6 the Jaccard distances between MP and RP for each release can be represented.
+The average jaccard distance between merge period and release period for all the release cycles is 0.85 and we see the jaccard distance is also going upward by releases except the only exception at release 2.6.34.
 
@@
 \begin{center}
-\includegraphics[height=1.7in,width=3.4in]{jaccardmprdp.png}
-\caption{\small \sl Jaccard Distance between the MP and RDP}
+\includegraphics[height=1.7in,width=3.4in]{jdMPRP.png}
+\caption{\small \sl Jaccard Distance between the Merge Period and Release Period}
 \end{center}
@@
 
-If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in general ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a significant difference as shown in figure 9.
+If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in release period ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a significant difference as shown in figure 9.
 \begin{figure}

### 2013-11-30 images/devsMP.r

@@ -1,0 +1,3 @@
+devsMPRP <- read.table("~/Documents/git/rupak/scripts/reports/devsMPRP.rpt",header=T,sep="|")
+plot(devsMPRP$release, devsMPRP$devs_mp)
+lines(devsMPRP$release, devsMPRP$devs_mp, type='h')

### 2013-11-30 images/devsMPRP.r

@@ -1,0 +1,5 @@
+plot(devsMPRP$devs_mp,type="b",lwd=2,xaxt="n",ylim=c(0,20000),col="black",xlab="release",ylab="developers",main="developers during merge period and release periods for releases")
+axis(1,at=1:length(devsMPRP$release),labels=devsMPRP$release)
+lines(devsMPRP$devs_rp,col="red",type="b",lwd=2)
+
+legend("topright",legend=c("Devs in MP","Devs in RP"),lty=1,lwd=2,pch=21,col=c("black","red"),ncol=2,bty="n",cex=0.8,text.col=c("black","red"),inset=0.01)

### 2013-11-30 images/devsMPRPbox.r

@@ -1,0 +1,2 @@
+devsMPRP <- read.table("~/Documents/git/rupak/scripts/reports/devs_mp_rp.csv",header=T,sep=",")
+boxplot(devsMPRP$devs_mp, devsMPRP$devs_rp, names=c("Developers in MP","Developers in RP"))

### 2013-11-30 images/jdMPRP.r

@@ -1,0 +1,2 @@
+jdMPRDP <- read.table("~/Documents/git/rupak/scripts/reports/rq2/jdMPRP.rpt",sep="|",header=T)
+plot(jacMPRP$jd_merge_rel, type="b",lwd=2,cex=0.8, xlab="releases", ylab="dj(mp,rp)")

### 2013-11-30 scripts/dev_area/dev_area_dev_owned.pl

@@ -1,0 +1,47 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $select_dev_area = $dbh_ref->prepare(q{
+        select 
+		author,
+		release,
+		path,
+		ownership
+	from 
+		dev_area_dev                                   
+});
+my $update = $dbh_ref->prepare(q{
+	update dev_area_dev set owned = 1 where author=? and release=? and path=?
+});
+$select_dev_area->execute() or die;
+
+while ( my($author, $release, $path, $ownership) = $select_dev_area->fetchrow_array) {
+	print "$author, $release, $path, $ownership\n";
+	if($ownership > 80){
+		print "$author - $release -- $ownership\n";
+		$update->execute($author, $release, $path) or die;
+	}
+}
+
+$select_dev_area->finish;
+$update->finish;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-11-30 scripts/jaccard/jac_dist.pl

@@ -19,20 +19,16 @@ my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoComm
 
 my ($prev_release, $release);
 
-my $query_insert = $dbh_ref->prepare(q{
-	insert into jac_dist(release) values(?)
-});
-
 #************* Calculate Jaccard Distance Between Merge Period and Development Period *******#
 #****************************** For ALl Releases ********************************************#
 my $md_union = $dbh_ref->prepare(q{
 	select count(*)
 	from (
-		select author, path 
+		select path 
 		from dev_area_merge
 		where release = ? 
 		UNION
-		select author, path 
+		select path 
 		from dev_area_dev 
 		where release = ?
 	) as r
@@ -40,27 +36,22 @@ my $md_union = $dbh_ref->prepare(q{
 my $md_intersection = $dbh_ref->prepare(q{
 	select count(*)
 	from (
-		select author, path
+		select path
 		from dev_area_merge
 		where release = ?
 		INTERSECT
-		select author, path 
+		select path 
 		from dev_area_dev
 		where release = ?
 	) as r
 });
 
 my $query_update = $dbh_ref->prepare(q{
-	update jac_dist set jd_merge_dev=? where release=?
+	update jac_dist set jd_merge_rel=? where release=?
 });
 
 my $get_releases = $dbh_ref->prepare(q{
-	select 	distinct p, date
-	from 	(
-			select 	substring(path, '(linuxv[0-9]*\.[0-9]?\.?[0-9]*)') as p, date
-			from 	git_refs_tags
-		) a
-	order by a.date
+	select 	release from stable_releases
 });
 
 $get_releases->execute or die;
@@ -78,8 +69,7 @@ while ( ($release) = $get_releases->fetchrow_array) {
 		if($mdu > 0){
 			$jac_dist_md = ($mdu - $mdi) / $mdu;
 			print "$release - $jac_dist_md\n";
-			$query_update->execute($jac_dist_md, $release)
-				or die("Could not update jac_dist");
+			$query_update->execute($jac_dist_md, $release) or die("Could not update jac_dist");
 		}else{
 			print "Union is <= 0\n";
 		}
@@ -90,7 +80,6 @@ while ( ($release) = $get_releases->fetchrow_array) {
 $md_union->finish;
 $md_intersection->finish;
 $query_update->finish;
-$query_insert->finish;
 $get_releases->finish;
 
 $dbh_ref->disconnect;

### 2013-11-30 scripts/reports/old scripts/peter.r

@@ -1,0 +1,41 @@
+plot(crSpman)
+ls
+ls()
+names(table)
+plot(table)
+plot(log1p(table$chp_mp), log1p(chp_gen))
+plot(log1p(table$chp_mp), log1p(table$chp_gen))
+plot(table$chp_mp, table$chp_gen)
+plot(log1p(table$chp_mp), log1p(table$chp_gen))
+qqnorm(table$chp_mp)
+qqnorm(log1p(table$chp_mp))
+summary(table$chp_mp)
+quantile(table$chp_mp, .9)
+quantile(table$chp_mp, .99\)
+quantile(table$chp_mp, .99)
+t <- table[table$chp_mp <= 1.32, ]
+summary(t)
+qqnorm(chp_mp)
+qqnorm(t$chp_mp)
+qqnorm(log1p(t$chp_mp)
+qqnorm(log1p(t$chp_mp))
+rjac <- read.table('~/Documents/git/rupak/scripts/reports/jd_anal.rpt', sep = '|', header = T)
+summary(rjac)
+lag <- read.table('~/Documents/git/rupak/scripts/reports/lag.rpt', sep = '|', header = T)
+summary(lag)
+summary(lag$lag[lag$stage == 'mp'])
+lag$lag[lag$stage == 'mp']
+lag$lag[lag$stage == 'mp', ]
+lag[lag$stage == 'mp', ]
+summary(lag$lag[lag$stage eq 'mp'])
+rm(lag)
+rplag <- read.table('~/Documents/git/rupak/scripts/reports/rp_lag.rpt', sep = '|', header = T)
+mplag <- read.table('~/Documents/git/rupak/scripts/reports/mp_lag.rpt', sep = '|', header = T)
+summary(rplag)
+summary(mplag)
+wilcox.test(mplag$lag, rplag$lag)
+qqnorm(rplag$lag)
+qqnorm(mplag$lag)
+boxplot(rplag$lag+1, mplag$lag+1, log = 'y')
+length(rplag$lag)
+length(mplag$lag)

### 2013-11-30 scripts/reports/rq6/jd_mprdpmp.pl

@@ -1,0 +1,144 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 0});
+
+my ($prev_release, $release);
+
+#************* Calculate Jaccard Distance Between Merge Period and Development Period *******#
+#****************************** For ALl Releases ********************************************#
+my $md_union = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path 
+		from dev_area_merge
+		where release = ? 
+		UNION
+		select author, path 
+		from dev_area_dev 
+		where release = ?
+	) as r
+});
+my $md_intersection = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path
+		from dev_area_merge
+		where release = ?
+		INTERSECT
+		select author, path 
+		from dev_area_dev
+		where release = ?
+	) as r
+});
+
+my $dd_union = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path 
+		from dev_area_dev
+		where release = ? 
+		UNION
+		select author, path 
+		from dev_area_dev 
+		where release = ?
+	) as r
+});
+my $dd_intersection = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select author, path
+		from dev_area_dev
+		where release = ?
+		INTERSECT
+		select author, path 
+		from dev_area_dev
+		where release = ?
+	) as r
+});
+
+
+my $query_update = $dbh_ref->prepare(q{
+	update release_jd_analysis set j_mp1_rdp1=?, j_rdp1_rdp2=?, j_rdp1_mp2=? where release=?
+});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select release from release_jd_analysis;
+});
+
+$get_releases->execute or die;
+($prev_release) = $get_releases->fetchrow_array;
+while (($release) = $get_releases->fetchrow_array) {
[…]

### 2013-12-01 paper1/paper1.tex
major literary correction made the paper, new research question added. rq done 1-5.

@@
 Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different periods within a stable release period.
-We will calculate Jaccard Distance to differentiate the behavior of developers during RTR and normal development period.
+We will calculate Jaccard Distance to differentiate the behavior of developers during release period and development period.
 \item Do developers work on different areas of the system around the time of release? \newline
-We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the merge period or merge window\cite{linux_kernel}.
-We are expecting this would be the RTR are in a release time where technical debt may be introduced.
+We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the release period or rc period.
+We are expecting this would be the RTR in a release cycle which may introduce technical debts.
 \item Do developers work in others' code in a high proportion during the rush period?
-Many developers are working on many files. We will find out which files has been churned mostly by which developer so that we can understand how developers are distributed among the system.
+Developers work on various files during release period.
+We will try to find out what is the percentage of dealing with files that developers own or they are most familier to.
+This will give us a sense of the nature of work during release time.
+\item How long a commit take to get pushed into the main kernel? Does it differ in different periods of release?
+In distributed development environment developers work in different branches they commit their codes to the branches they are associated to.
+Developers in that case do not directly push their changes to the main branch.
+We would like to see how much time it takes for a commit to the local branch to get pushed to the main branch.
+We also should understand how long it takes for regular development commits and how long it takes for the commits made around the release period.
 \item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)? \newline
-To answer this question we will look into the frequency of file churns made into files.
-Difference or distance of the files between normal development period and the RTR period or merge period of a release.
+To answer this question we will look into the frequency of file churns made into files. Difference or distance of the files between normal development period and the release period of a release.
 \end{enumerate}
@@
 To achieve that we joined the table ``git\_refs\_tags'' where all the releases are stored including the splitted release numbers and the table ``git\_commit'' to give us all the dates of commits for each and every releases, so that we can easily find out the duration between two consecutive releases (including release candidates RC).
-This information will significantly help us because we need to see what is the general development period and what are the merge periods which can be treated as RTR period within a release period.
+This information will significantly help us because we need to see what is the development period and what are the release periods within a release cycle.
 We also need to understand how developers are working, what is the impact of their changes made in the code-base during a particular release period later on.
@@
 For example if the date of release for ``linuxv2.6.12''  is 2005-06-17 and date of pushing the rc-1 for the next release ``linuxv2.6.13'' is 2005-06-29 then this time period of of 12 days is going to be being called the merge window.
-We are considering this segment as a Rush To Release or RTR because thousands of commits gets pushed in the main branch during this time and developers remain in a rush to pack up merging all the branches those are to go with this release.
+Thousands of commits get pushed in the main branch during this period.
 Table 2 shows merge periods of some releases.
@@
 As like merge period we can extract developers working in code files during release period.
-Release Period here in Linux Kernel development process is being considered as since the date of rc-1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the date of the next stable release.
-For example if the date of rc-1 for ``linuxv2.6.13'' after releasing ``linuxv2.6.12'' is 2005-06-29 and the date of publishing the release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the Release Period.
+Release Period here in Linux Kernel development process is being considered as since the date of rc1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the date of the next stable release.
+For example if the date of rc1 for ``linuxv2.6.13'' after releasing ``linuxv2.6.12'' is 2005-06-29 and the date of publishing the release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the Release Period.
 Table 4 is showing some development periods of different releases.
@@
 We tried to investigate the "code ownership" \cite{mockus_case_study} evolved in Linux Kernel development.
-Here code ownership is going to be represented as a percentage of making churns or commits by a developer with respect to the total churns or commits made to a particular file.
-From the data that we have for complete releases (``linuxv2.6.13'' to ``linuxv3.11'') we found 75138 distinct files that have been churned or commited by developers.
-We investigate the total number of commits, total number of churns for each and every file, we also investigate how many developers contributed for these commits and changes.
+Here code ownership is going to be represented as a percentage of making churns by a developer with respect to the total churns made to a particular file.
+From the data that we have for complete releases (``linuxv2.6.13'' to ``linuxv3.11'') we found 70210 distinct files that have been churned by developers.
+We removed those files where no developer made any churn at all during these 39 releases.
+We investigate the total number of churns for each and every file, we also investigate how many developers contributed for these commits and changes.
 This information yet does not tell about the ownership, we need to find out ownership for each developer in different development areas in a release cycle.
@@
 Gutwin did \cite{gutwin_awareness} for finding out the main developers' group for a project.
-We already mentioned that 14569 individual files didn't have any change (addition or deletion) but was being committed at least once.
-So we found them in our release wise datasets that's why in addition to Gutwin here we are involving commits to determine ownerships but only for those files that do not have churn information.
-If a file has no addition or deletion information in it's commit log but has been committed by some one at least once then that or those authors may have the ownership for that file.
-So, we have made a little change in equation 1 which becomes like:
-\begin{equation} \omega = \left\{ \begin{array}{l l} n/N & \quad \text{if $N > 0$}\\ c/C & \quad \text{if $N = 0$} \end{array} * 100 \right.\end{equation}
-Where c is the number of commits made by the author and C is the total number of commits made for the particular file.
 We calculate code ownership for both Merge Period and Release Period.
@@
 The highest picks are the merge periods then the smaller picks between the highest ones are representing the rc releases.
-For more clear view we have plotted only 100 releases of all 340 releases.
+For more clear view we have plotted only 100 releases of all 340 releases including rc candidates.
 
@@
 11209 developers work in merge period and 7625 developers work around the release period.
-We found that 4908 developers contribute in both merge period and the release period that means near about half (43.78\%) of the developers work during the merge period are shared that means they work in both merge and release periods.
 
@@
 Developers work for the software continuously.
-Some are working for the core development some people are for the fixing and minor enhancements and some for feature developments, planning to merge new features with any up coming release but we would like to understand what number of files they change during the time of regular development period and how many during the time of RTR.
+Some are working for the core development some people are for the fixing and minor enhancements and some for feature developments, planning to merge new features with any up coming release but we would like to understand what number of files they change during the time of development and merging period and how many during the release period.
 How many of them they really own and how many files they work that they do not own.
-We also want to know about the code ownership of the developers around the time of release and general code ownership i.e.\ which files a developer has worked making more than 80\% chruns in lifetime.
+We also want to know about the code ownership of the developers around the time of release as well as around the time of main development works that get merged during merge meriod.
 
-Since the release of ``linuxv2.6.13'' till ``linuxv3.11'' 2889 developers out of 14621 worked for the files they owned.
-Although they have worked for other files that they do not own.
-So the percentage of working with owned files is 19.82\% through out the life time (release 2.6.13 to 3.11).
-We examine the contribution in writing code and making churns by the developers to understand the behaviour and to see if the impact of this 19.82\% on the graph.
-Figure 7 plots the cumulative representation of churnes files and percentage of owned files per developer for a particular release ``linuxv2.6.13''.
-If I say in details, in the increase of every 10 developers it is observed that developers work increasingly more unknown files than the files they own or they are very familier to.
-We see the similar picture for other releases too.
-So we can say that in Linux Kernel development developers work in more unfamilier files than the most familier (i.e.\ more than 80\%) ones.
+In order to understand the distribution of the developers around the system we also found that during these release periods 11209 developers have experience of working in the merge meriod and 7625 developers worked in the release period as we already mentioned earlier but we noted that 4908 developers contribute in both merge period and the release period that means near about half (43.78\%) of the developers work during the merge period are shared that means they work for core developments and also bug fixing or minor enhancement works.
+Figure 7 representing the venn diagram.
 \begin{figure}
 \begin{center}
-\includegraphics[height=1.7in,width=3.4in]{cumulativeChurnOwnershipPercent.png}
-\caption{\small \sl Cumulative Number of Churns vs Percentage of Owned Files in release 2.3.13}
-\end{center}
-\end{figure}
-
-To understand the distribution of the developers around the system we also found that during these release periods 8057 developers have experience of working in the merge meriod and 14621 developers worked in the release development period as we already mentioned earlier but we noted that 4884 developers work in both the parts.
-So almost half of the developers that work in merge period also work in the release development period.
-Figure 8 shows the Venn diagram.
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3in]{devDistMPRDP.png}
+\includegraphics[height=1.3in,width=2.3in]{devDistMPRPvenn.png}
 \caption{\small \sl Developers' Distribution in Merge Period and Development Period}
@@
 
-If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in release period ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a significant difference as shown in figure 9.
+From release ``linuxv2.6.13'' to ``linuxv3.11'' We examine the contribution in writing code by the developers to understand the behaviour during the two vital segments in a release cycle.
+Figure 8 plots the cumulative representation of the percentage of working with owned files ($\omega$\textit{MP}) during the merge period and the percentage of working with owned files ($\omega$\textit{RP}) during release period of ``linuxv2.6.13''.
+From the figure It can be observed that with the increase of every 10 files that developers working in, $\omega$\textit{RP} is going down apart from the line of $\omega$\textit{MP}.
+Up to a certain number may be around 2200 files developers mostly work with owned files.
+We see the similar picture for other releases too.
 \begin{figure}
 \begin{center}
-\includegraphics[height=1.7in,width=3in]{ownedFilesMPRDPBox.png}
-\caption{\small \sl Percentage of working in owned files during Merge Period and the that of life time}
+\includegraphics[height=1.7in,width=3.4in]{cumulFileOwnP.png}
+\caption{\small \sl Cumulative percentage of working with owned files in MP and RP of release 2.3.13}
 \end{center}
@@
 
-Now, to predict if developers work in others' code in a high proportion during the rush period we would like to observe the correlation of the \% of working in owned files in merge period with other independent variables ``churn percentage in merge period (\c{c}\textit{P})'', ``churn percentage in general (\c{C}\textit{P})'', ``average ownership ($\omega$\textit{Avg})'' and \% of wirking in owned files in general ($\Omega$\textit{P}).
-Table 6 shows the Spearman rank correlation among the \% of working with owned files and other variables.
-We can see there is no statistically significant positive relationship between the measures and the \% of working in owned files
+If we simply compare the percentage of working in owned files during merge period ($\omega$\textit{MP}) and the percentage of working in owned files during release period ($\omega$\textit{RP}) for each developer then we see a significant difference of the mean lines as shown in figure 9.
+In release period developers work with less number of files that they own.
 
-All three correlations Kendall, Pearson and Spearman calculates that the percentage of working with owned files doesn't to any other variables strongly as we predicted seeing figure 7 having a very poor percentage of contribution (19.82\%) on owned files during the merge period of time.
-But we can see a significant strong relation between the \% of churn in general and \% of churn in merge period which is 0.7199 according to Kendall, 0.7028 according to Pearson and 0.8446 according to Spearman.
-Also the correlation between the \% of churn in general and the average ownership is strong according to Spearman model which is 0.7982.
-We are giving the priority to Spearman model because Spearman correlation is a more robust correlation technique \cite{nagappan_defect}.
-If we consider the following models with our variables:
-\renewcommand{\labelenumi}{M\theenumi:}
-\begin{enumerate}
-\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}}
-\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}}
-\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}, \c{c}\textit{P}}
-\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}, \c{c}\textit{P}, \c{C}\textit{P}}
-\end{enumerate}
-then we see the linear regression model for the \% of working with owned code measure using all the predictors has an R-squared value 0.1132 with residual standard error is 32.52 on 8053 degrees of freedom, Adjusted R-squared value is 0.1139.
-F-statistic is 342.8 and the p-value is < 2.2e-16.
-R-square is a measure of variance in the dependent variable that is accounted for by the model built using the predictors \cite{nagappan_defect}.
-R-square is a measure of the fit for the given data set.
-It cannot be interpreted as the quality of the dataset to make future predictions.
+So we can say that in Linux Kernel development developers work in more unfamilier files during the release period.
+Before the release period main development works are accepted from different branches and they get merged together with main kernel, so, core feature developers finishes their duty for a particular feature development for a particular release within the time of merge period althoug some contributors still work during the release period where basically they work on fixing, testing and minor enhancement related work on the codes that have been merged and accepted from various developers from other branches.
+It is clear now that during the release period developers work mostly on others' works, the proportion of working with owned files is lower around the release than the proportion during normal development time.
+When they feel the confidence that everything is tested and can be pushed out for the release, they publish the stable release.
 
-\begin{table}[ht]
-\caption{Cross Correlations}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c c c}			% centered columns (6 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Measures  & $\omega$\textit{P} & $\Omega$\textit{P} & $\omega$\textit{Avg} & \c{c}\textit{P} & \c{C}\textit{P} \\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-$\omega$\textit{P}		& 1.0000	& 0.2897	& 0.4496	& 0.3325	& 0.2826 \\
-$\Omega$\textit{P}	& --			& 1.0000	& 0.7110	& 0.3979	& 0.5075 \\
-$\omega$\textit{Avg}	& --			& --			& 1.0000 	& 0.6754 	& \textbf{0.7982} \\
-\c{c}\textit{P}			& -- 			& -- 		 	& --			& 1.0000	& \textbf{0.8446} \\
-\c{C}\textit{P}			& -- 			& -- 			& -- 			& -			& 1.0000 \\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{ownpMPRPbox.png}
+\caption{\small \sl Percentage of working in owned files during Merge Period and Release Period}
+\end{center}
+\end{figure}
 
 So, finally we can say that in merge periods developers work in more native codes while during the regular release development period the percentage of working with native code is very low in number although this percentage of working in owned code during merge period does not significantly relate to other co-factors.
+
+\subsection{Time for commits to go live}
+\textit{How long a commit take to get pushed into the main kernel? Does it differ in different periods of release?}
+
+There are thousands of commits goes to the main kernel during the merge meriod.
+All they are to be considered as the normal development commits or regular development or core development commits for developing new features to the kernel.
+Merge period remains opened for two weeks only, the development works that are supposed to go for a particular release are not developed during this couple of weeks.
+These have been developed since many days ago on a different development branch by any developer.
+For a particular feature that is going to the current release there are hundreds of commits, obviously all these commits are not made during the merge period of the current release 90-100\% commits must have been made before the opening of the merge period of current release.
+As described in section 4.3, we have sorted up the releases according to the git DAG.
+This helps us to calculate how many days in past the first commit of this particular feature had been made which is going to be pushed into the current release.
+The duration a commit was made to the local branch to the date it is pushed into the main branch is being called here ``lag'' of commits.
+Figure 10 represents lag of the commits made for regular development and lag of the commits made during the release period.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{lagMPRPbox.png}
+\caption{\small \sl Time takes for development commits and commits around release periods to get released}
+\end{center}
+\end{figure}
+
+From figure 10 we can understand it easily that rather quick fixes are made during the release period.
+With the small sets of bug fixes, important wuick enhancements candidate releases are pushed and once the kernel seems to me more stable with all the new features that's been merged at the beginning of the release cycle, stable release is published.
+Comperatively lag for the feature development commits is quite high.
+Median for the lags for the commits during this time is 5.57 while median for the lags for the commits goes to the main kernel during merge period is 26.15 which is a significant different between these two periods of a release cycle.
 

### 2013-12-01 scripts/dev_area/dev_area_dev.pl

@@ -1,60 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_rc_dates = $dbh_ref->prepare(q{
-	select	release, rc_date, rel_date
-	from	rd_period
-});
-
-my $dev_area = $dbh_ref->prepare(q{
-	insert into dev_area_dev
-        select 
-		author,
-		?,
-		r.new_path,
-		count(*) as commits,
-		sum(add+remove) as churn,
-		0 as ownership
-	from 
-		git_commit_release cr, git_revision r, git_commit c
-                                    
-	where 
-		c.commit = r.commit
-		and r.commit = cr.commit
-		and c.committer_dt > ?
-		and c.committer_dt <= ?
-	group by
-		author, r.new_path
-});
-#This will insert the information about the changes that developers are making in a period of merging in a release.
-
-$get_rc_dates->execute() or die;
-
-while ( my($release, $rc_date, $rel_date) = $get_rc_dates->fetchrow_array) {
-	print "$release -- $rc_date --  $rel_date\n";
-
-	$dev_area->execute($release, $rc_date, $rel_date) or die; 
-}
-
-$get_rc_dates->finish;
-$dbh_ref->disconnect;
-
-__END__
-
-see dev_area.sql

### 2013-12-01 scripts/dev_area/dev_area_dev_owned.pl

@@ -17,29 +17,12 @@ my %config =  Config::General::ParseConfig($config_path);
 
 my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
 
-my $select_dev_area = $dbh_ref->prepare(q{
-        select 
-		author,
-		release,
-		path,
-		ownership
-	from 
-		dev_area_dev                                   
-});
 my $update = $dbh_ref->prepare(q{
-	update dev_area_dev set owned = 1 where author=? and release=? and path=?
+	 update dev_area_dev set owned = case when ownership>80 then 1 else 0 end
 });
-$select_dev_area->execute() or die;
 
-while ( my($author, $release, $path, $ownership) = $select_dev_area->fetchrow_array) {
-	print "$author, $release, $path, $ownership\n";
-	if($ownership > 80){
-		print "$author - $release -- $ownership\n";
-		$update->execute($author, $release, $path) or die;
-	}
-}
+$update->execute() or die;
 
-$select_dev_area->finish;
 $update->finish;
 $dbh_ref->disconnect;
 

### 2013-12-01 scripts/dev_area/dev_area_merge.pl

@@ -1,57 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_merge_dates = $dbh_ref->prepare(q{
-	select	release, previous, rc_date
-	from	merge_period order by major, minor, micro
-});
-
-my $dev_area = $dbh_ref->prepare(q{
-	insert into dev_area_merge
-        select
-		author,
-		?,
-		r.new_path,
-		count(*) as commits,
-		sum(add+remove) as churn,
-		0 as ownership
-	from
-		git_commit_release cr, git_revision r, git_commit c
-	where 
-		c.commit = r.commit
-		and r.commit = cr.commit
-		and c.committer_dt > ?
-		and c.committer_dt <= ?
-	group by
-		author, r.new_path
-});
-#This will insert the information about the changes that developers are making in a period of merging in a release.
-
-$get_merge_dates->execute() or die;
-
-while ( my($release, $prev_date, $rc_date) = $get_merge_dates->fetchrow_array) {
-	print "$release -- $prev_date --  $rc_date\n";
-
-	$dev_area->execute($release, $prev_date, $rc_date) or die;
-}
-
-$get_merge_dates->finish;
-$dbh_ref->disconnect;
-
-__END__

### 2013-12-01 scripts/dev_area/dev_area_merge_owned.pl

@@ -17,28 +17,12 @@ my %config =  Config::General::ParseConfig($config_path);
 
 my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
 
-my $select_dev_area = $dbh_ref->prepare(q{
-        select 
-		author,
-		release,
-		path,
-		ownership
-	from 
-		dev_area_merge                                   
-});
 my $update = $dbh_ref->prepare(q{
-	update dev_area_merge set owned = 1 where author=? and release=? and path=?
+	 update dev_area_merge set owned = case when ownership>80 then 1 else 0 end
 });
-$select_dev_area->execute() or die;
 
-while ( my($author, $release, $path, $ownership) = $select_dev_area->fetchrow_array) {
-	if($ownership > 80){
-		print "$author - $release -- $ownership\n";
-		$update->execute($author, $release, $path) or die;
-	}
-}
+$update->execute() or die;
 
-$select_dev_area->finish;
 $update->finish;
 $dbh_ref->disconnect;
 

### 2013-12-01 scripts/jaccard/dev_area_dev.pl

@@ -1,59 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_rc_dates = $dbh_ref->prepare(q{
-	select	release, rc_date, rel_date
-	from	rd_period
-});
-
-my $dev_area = $dbh_ref->prepare(q{
-	insert into dev_area_dev
-        select 
-		author,
-		?,
-		r.new_path,
-		count(*) as commits,
-		sum(add+remove) as churn,
-		0 as ownership
-	from 
-		git_revision r, git_commit c
-                                    
-	where 
-		c.commit = r.commit 
-		and c.committer_dt > ?
-		and c.committer_dt <= ?
-	group by
-		author, r.new_path
-});
-#This will insert the information about the changes that developers are making in a period of merging in a release.
-
-$get_rc_dates->execute() or die;
-
-while ( my($release, $rc_date, $rel_date) = $get_rc_dates->fetchrow_array) {
-	print "$release -- $rc_date --  $rel_date\n";
-
-	$dev_area->execute($release, $rc_date, $rel_date) or die; 
-}
-
-$get_rc_dates->finish;
-$dbh_ref->disconnect;
-
-__END__
-
-see dev_area.sql

### 2013-12-01 scripts/jaccard/dev_area_merge.pl

@@ -1,59 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_merge_dates = $dbh_ref->prepare(q{
-	select	release, previous, rc_date
-	from	merge_period order by major, minor, micro
-});
-
-my $dev_area = $dbh_ref->prepare(q{
-	insert into dev_area_merge
-        select 
-		author,
-		?,
-		r.new_path,
-		count(*) as commits,
-		sum(add+remove) as churn,
-		0 as ownership
-	from 
-		git_revision r, git_commit c
-                                    
-	where 
-		c.commit = r.commit 
-		and c.committer_dt > ?
-		and c.committer_dt <= ?
-	group by
-		author, r.new_path
-});
-#This will insert the information about the changes that developers are making in a period of merging in a release.
-
-$get_merge_dates->execute() or die;
-
-while ( my($release, $prev_date, $rc_date) = $get_merge_dates->fetchrow_array) {
-	print "$release -- $prev_date --  $rc_date\n";
-
-	$dev_area->execute($release, $prev_date, $rc_date) or die; 
-}
-
-$get_merge_dates->finish;
-$dbh_ref->disconnect;
-
-__END__
-
-see dev_area.sql

### 2013-12-01 scripts/jaccard/dev_area_rel.pl

@@ -1,72 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-#This file calculates the area of developers during release period. How many commits are made
-#by an author for a particular file, how many churns are made and what is the percentage of his/her 
-#ownership to that file.
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_release_dates = $dbh_ref->prepare(q{
-	select	committer_dt, path as release
-	from	git_refs_tags r, git_commit c
-	where	c.commit = r.commit
-		and r.rc = 0
-	order by committer_dt
-});
-#we are avoiding rc because we want the release dates. rc dates are not release dates.
-
-my $dev_area = $dbh_ref->prepare(q{
-	insert into dev_area_rel
-        select 
-		author,
-		?,
-		r.new_path,
-		count(*) as commits,
-		sum(add+remove) as churn,
-		0
-	from 
-		git_commit_release cr, git_revision r, git_commit c
-                                    
-	where 
-		c.commit = r.commit
-		and r.commit = cr.commit
-		and c.committer_dt > ? 
-		and c.committer_dt <= ?
-	group by
-		author, r.new_path
-});
-#This will insert the information about the changes that developers are making in a release period.
-
-$get_release_dates->execute() or die;
-
-my($prev_date, $prev_release) = $get_release_dates->fetchrow_array;
-
-while ( my($date, $release) = $get_release_dates->fetchrow_array) {
-	print "$release -- $prev_date --  $date\n";
-	$dev_area->execute($release, $prev_date, $date) or die; 
-
-	$prev_date = $date;
-	$prev_release = $release;
-}
-
-$get_release_dates->finish;
-$dbh_ref->disconnect;
-
-__END__
-
-see dev_area.sql

### 2013-12-01 scripts/jaccard/dev_area_rtr.pl

@@ -1,56 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_rc_dates = $dbh_ref->prepare(q{select release, rc_end_date, rel_date from rtr_period});
-
-my $dev_area = $dbh_ref->prepare(q{
-	insert into dev_area_rtr
-        select 
-		author,
-		?,
-		r.new_path,
-		count(*) as commits,
-		sum(add+remove) as churn,
-		0 as ownership
-	from 
-		git_revision r, git_commit c
-                                    
-	where 
-		c.commit = r.commit 
-		and c.committer_dt > ?
-		and c.committer_dt <= ?
-	group by
-		author, r.new_path
-});
-#This will insert the information about the changes that developers are making in a period of merging in a release.
-
-$get_rc_dates->execute() or die;
-
-while ( my($release, $rc_end_date, $rel_date) = $get_rc_dates->fetchrow_array) {
-	print "$release -- $rc_end_date --  $rel_date\n";
-
-	$dev_area->execute($release, $rc_end_date, $rel_date) or die; 
-}
-
-$get_rc_dates->finish;
-$dbh_ref->disconnect;
-
-__END__
-
-see dev_area.sql

### 2013-12-01 scripts/jaccard/jac_dist_old.pl

@@ -1,182 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my ($prev_release, $release);
-my $jac_dist;
-
-my $get_releases = $dbh_ref->prepare(q{
-	select distinct p,date from (select substring(path, '(linuxv[0-9]*\.[0-9]?\.?[0-9]*)') as p, date from git_refs_tags) a order by a.date
-});
-
-my $query_insert = $dbh_ref->prepare(q{
-	insert into jac_dist(release) values(?)
-});
-
-# Inserting releases first
-$get_releases->execute() or die;
-($prev_release) = $get_releases->fetchrow_array;
-while ( ($release) = $get_releases->fetchrow_array) {
-	if(not $prev_release eq $release){
-		#$query_insert->execute($release) or die;
-	}
-	$prev_release = $release;
-}
-
-#************* Calculate Jaccard Distance Between Merge Period and Development Period *******
-#****************************** For ALl Releases ********************************************
-my $md_union = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path 
-		from dev_area_merge
-		where release = ? 
-		UNION
-		select author, path 
-		from dev_area_dev 
-		where release = ?
-	) as r
-});
-my $md_intersection = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path
-		from dev_area_merge
-		where release = ?
-		INTERSECT
-		select author, path 
-		from dev_area_dev
-		where release = ?
-	) as r
-});
-my $dr_union = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path 
-		from dev_area_dev
-		where release = ? 
-		UNION
-		select author, path 
-		from dev_area_rtr 
-		where release = ?
-	) as r
-});
-my $dr_intersection = $dbh_ref->prepare(q{
[…]

### 2013-12-01 scripts/jaccard/jac_dist_rel.pl

@@ -1,91 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_releases = $dbh_ref->prepare(q{
-	select distinct p,date from (select substring(path, '(linuxv[0-9]*\.[0-9]?\.?[0-9]*)') as p, date from git_refs_tags) a order by a.date
-});
-
-my $dev_union = $dbh_ref->prepare(q{
-	select count(*) 
-	from (
-		select author, path 
-		from dev_area_rel
-		where release = ? 
-		UNION
-		select author, path 
-		from dev_area_rel 
-		where release = ?
-	) as r
-});
-my $dev_intersection = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select author, path
-		from dev_area_rel
-		where release = ?
-		INTERSECT
-		select author, path 
-		from dev_area_rel
-		where release = ?
-	) as r
-});
-
-my $query_insert = $dbh_ref->prepare(q{
-	insert into jac_dist_rel values(?,?,?)
-});
-
-my($jac_dist);
-
-$get_releases->execute() or die;
-
-#throw away the first because nothing is before it
-my($prev_release) = $get_releases->fetchrow_array;
-
-while ( my($release) = $get_releases->fetchrow_array) {
-	if(not $prev_release eq $release){
-	
-		$dev_union->execute($prev_release, $release) or die;
-		my $union = $dev_union->fetchrow_array;
-
-		$dev_intersection->execute($prev_release, $release) or die;
-		my $intersection = $dev_intersection->fetchrow_array;
-
-		print "$union - $intersection / $union\n";
-
-		if($union > 0){
-			$jac_dist = ($union - $intersection) / $union;
-		}else{
-			$jac_dist = 0;
-		}
-
-		print " $prev_release ~ $release => $jac_dist\n";
-
-		$query_insert->execute($prev_release, $release, $jac_dist) or die("Could not insert into jac_dist_rel");
-	}
[…]

### 2013-12-01 scripts/ownership/ownership_dev.pl

@@ -21,39 +21,27 @@ my $get_dev_area_dev_info = $dbh_ref->prepare(q{
 	select  author, path, release from dev_area_dev
 });
 my $get_file_info = $dbh_ref->prepare(q{
-		select  churn, commits from file_info where release = ? and path = ?
-	});
-my $update_ownership_ch = $dbh_ref->prepare(q{
-	update dev_area_dev set ownership = ((churn/?)*100)
-	where author = ? and path = ? and release = ?
+	select  churn from file_info where release = ? and path = ?
 });
-my $update_ownership_cm = $dbh_ref->prepare(q{
-	update dev_area_dev set ownership = ((commits/?)*100)
+my $update_ownership_ch = $dbh_ref->prepare(q{
+	update dev_area_dev set ownership = round(((churn/?)*100), 2)
 	where author = ? and path = ? and release = ?
 });
 
 $get_dev_area_dev_info->execute or die;
-my $ch0 = 0;
+
 while (my($author, $path, $release) = $get_dev_area_dev_info->fetchrow_array) {
 
 	$get_file_info->execute($release, $path) or die;
 	
-	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
-
-	if($file_total_churn == 0){
-		print "$ch0. [$path] File total churn is 0\n";
-		$update_ownership_cm->execute($file_total_commits, $author, $path, $release) or die;
-		$ch0++;
-	}else{
-		$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
-	}
+	my ($file_total_churn) = $get_file_info->fetchrow_array;
+	$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
 }
 
 $get_dev_area_dev_info->finish;
 $get_file_info->finish;
-
 $update_ownership_ch->finish;
-$update_ownership_cm->finish;
+
 $dbh_ref->disconnect;
 
 __END__

### 2013-12-01 scripts/ownership/ownership_merge.pl

@@ -24,36 +24,24 @@ my $get_file_info = $dbh_ref->prepare(q{
 		select  churn, commits from file_info where release = ? and path = ?
 	});
 my $update_ownership_ch = $dbh_ref->prepare(q{
-	update dev_area_merge set ownership = ((churn/?)*100)
-	where author = ? and path = ? and release = ?
-});
-my $update_ownership_cm = $dbh_ref->prepare(q{
-	update dev_area_merge set ownership = ((commits/?)*100)
+	update dev_area_merge set ownership = round(((churn/?)*100), 2)
 	where author = ? and path = ? and release = ?
 });
 
 $get_dev_area_merge_info->execute or die;
-my $ch0 = 0;
+
 while (my($author, $path, $release) = $get_dev_area_merge_info->fetchrow_array) {
 
 	$get_file_info->execute($release, $path) or die;
 	
 	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
-
-	if($file_total_churn == 0){
-		print "$ch0. [$path] File total churn is 0\n";
-		$update_ownership_cm->execute($file_total_commits, $author, $path, $release) or die;
-		$ch0++;
-	}else{
-		$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
-	}
+	$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
 }
 
 $get_dev_area_merge_info->finish;
 $get_file_info->finish;
-
 $update_ownership_ch->finish;
-$update_ownership_cm->finish;
+
 $dbh_ref->disconnect;
 
 __END__

### 2013-12-01 scripts/ownership/ownership_rtr.pl

@@ -1,61 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $get_dev_area_rtr_info = $dbh_ref->prepare(q{
-	select  author, path, release from dev_area_rtr
-});
-my $get_file_info = $dbh_ref->prepare(q{
-		select  churn, commits from file_info where release = ? and path = ?
-	});
-my $update_ownership_ch = $dbh_ref->prepare(q{
-	update dev_area_rtr set ownership = ((churn/?)*100)
-	where author = ? and path = ? and release = ?
-});
-my $update_ownership_cm = $dbh_ref->prepare(q{
-	update dev_area_rtr set ownership = ((commits/?)*100)
-	where author = ? and path = ? and release = ?
-});
-
-$get_dev_area_rtr_info->execute or die;
-my $ch0 = 0;
-while (my($author, $path, $release) = $get_dev_area_rtr_info->fetchrow_array) {
-
-	$get_file_info->execute($release, $path) or die;
-	
-	my ($file_total_churn, $file_total_commits) = $get_file_info->fetchrow_array;
-
-	if($file_total_churn == 0){
-		print "$ch0. [$path] File total churn is 0\n";
-		$update_ownership_cm->execute($file_total_commits, $author, $path, $release) or die;
-		$ch0++;
-	}else{
-		$update_ownership_ch->execute($file_total_churn, $author, $path, $release) or die;
-	}
-}
-
-$get_dev_area_rtr_info->finish;
-$get_file_info->finish;
-
-$update_ownership_ch->finish;
-$update_ownership_cm->finish;
-$dbh_ref->disconnect;
-
-__END__
-
-see file_info.sql

### 2013-12-01 scripts/reports/cumul.pl

@@ -1,46 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
-
-my $rel_churn_ownper = $dbh_ref->prepare(q{
-	select author, count(path) as files, sum(churn) as tch, round(cast(sum(owned) as numeric)/cast(count(path) as numeric),2)*100 as wp 
-	from dev_area_merge 
-	where release='linuxv2.6.13' 
-	group by author order by author;
-});
-my $insert = $dbh_ref->prepare(q{insert into dev_churn_ownp_cumul values(?,?,?,?)});
-
-$rel_churn_ownper->execute() or die;
-
-my $i=0;
-my ($totalFiles,$totalChurn,$totalOwnPercent) = 0;
-while(my($author,$files,$tch,$wp) = $rel_churn_ownper->fetchrow_array){
-	$i++;
-	$totalChurn = $totalChurn + $tch;
-	$totalFiles = $totalFiles + $files;
-	$totalOwnPercent = $totalOwnPercent + $wp;
-	if($i%10==0){
-		$insert->execute($i,$totalFiles/10,$totalOwnPercent/10,$totalChurn/10);
-	}
-}
-
-$rel_churn_ownper->finish;
-$insert->finish;
-$dbh_ref->disconnect;
-
-__END__

### 2013-12-01 scripts/reports/cumulative_dev_churn_file_ownp.r

@@ -1,8 +1,0 @@
-relDCOP <- read.csv("~/Documents/git/rupak/scripts/reports/cumulative_dev_churn_file_ownp.rpt")
-
-xrange <- range(relDCOP$devs)
-
-plot(relDCOP$devs, relDCOP$churns, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of developers", ylab="")
-lines(relDCOP$devs, relDCOP$ownp, type="l", lwd=1.5, lty=2, col="blue")
-
-legend(xrange[1],150000,c("churns","ownership"), col=c("red","blue"),lty=c("solid","dashed"))

### 2013-12-02 paper1/paper1.tex
RQ6, only remaings are Jaccard Distance between areas having increased attention, conclusion, abstract

@@
 This will give us a sense of the nature of work during release time.
-\item How long a commit take to get pushed into the main kernel? Does it differ in different periods of release?
+\item How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?
 In distributed development environment developers work in different branches they commit their codes to the branches they are associated to.
@@
 \subsection{Time for commits to go live}
-\textit{How long a commit take to get pushed into the main kernel? Does it differ in different periods of release?}
+\textit{How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?}
 
@@
 From figure 10 we can understand it easily that rather quick fixes are made during the release period.
-With the small sets of bug fixes, important wuick enhancements candidate releases are pushed and once the kernel seems to me more stable with all the new features that's been merged at the beginning of the release cycle, stable release is published.
+With the small sets of bug fixes, important quick enhancements candidate releases are pushed continuously within short period lengths of time and once the kernel seems to be more stable with all the new features that has been merged during the beginning of the release cycle, the stable release is published.
 Comperatively lag for the feature development commits is quite high.
@@
 \textit{Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?}
-Answer to the following questions are going to be looked for to answer this research question:
+
+To answer this research question we are interested to find answer to the following questions first.
 \renewcommand{\labelenumi}{q\theenumi:}
 \begin{enumerate}
-\item{How many times a file has been committed during merge period?}
-\item{How many authors made those commits?}
-\item{How many churns were made to the files during each commit?}
-\item{What is the time interval for the commits for a file?}
-\item{How many files each developer deals with during merge period?}
+\item{How many churns were made to the files during release periods?}
+\item{How many files get churns exceptionally high in number? Do we see this in every release cycles?}
 \item{How many files each developer deals with during release development period?}
-\item{What is the jaccard distance J(mp1, rdp1), J(rdp1, rdp0) and J(rdp0, mp1)?}
+\item{How many files developer deal with large number of files during release development period?
+What is the percentage of ownership of them while working for a large number of files in a release period?}
+\item{If there is any area that requires increased attention in the system, then what is the jaccard distance of those areas throught different releases?
+Are they being focused iteratively by releases?}
 \end{enumerate}
-We found the relation J(mp1, rdp1) > J(rdp1, rdp0) < J(rdp0, mp1) for the minor releases is significant but among the micro stable releases this relation is not significant at all.
+
+During the time of rc releases after all the merging jobs are done developers generally work for minor fixing and serious quick enhancements.
+In all these 39 release cycles of Linux Kernel development wee see in an average 3077 churns are made around the releases.
+The minimum value is 1691 and maximum is 8669.
+Median and mean values are closer enough (2668 and 3077) to say that almost similar kind of churns are made in all the release periods except couple of exceptions.
+If we look at figure 11 then where the normalized distribution of this data is represented then we can easily understand.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{churnRPnorm.png}
+\caption{\small \sl Normal distribution of churns per Release Period}
+\end{center}
+\end{figure}
+
+We analyzed in several releases and found that for the release ``linuxv2.6.13'' 2938 files got churned.
+Among them only five files had exceptionally high number of churns four of them have more than 10,000 churns.
+Similar picture we see for other releases also.
+Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high and being marked as outliars as shown in figure 12.
+For almost every release cycle during the release period around 2.846 files get highly increased attention having over 5000 churns and 16.78 files having over 1000 churns as shown in figure 13.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{fileChurnRPbox.png}
+\caption{\small \sl Files churned in release periods}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3in]{fileChurnRPExp1000vs5000box.png}
+\caption{\small \sl Files churned more than 1000 times and more than 5000 times during release period}
+\end{center}
+\end{figure}
+
+During the release period developers deal with various files came from different authors working in different development branches in merge window.
+Although the number of files developers deal with during release period is too low (mean 5.52) there is a large number of developers work for around 50 files.
+To look for how many developers work for fairly large number of files we decided to see which developers work for more than 100 files in the release periods.
+
+We found that there are 29 releases out of the 39 where developers are working in comperatively large number of files during the release period?
+Among them we noted that 5 developers in 5 different release periods worked for extremely high number of files as listed in table 6.
+In this table we also have represented what is the percentage of working with owned files for each developer.
+
+\begin{table}[ht]
+\caption{Developers making churn in extremely high number of files during Release Periods}  % title of Table
+\centering 						% used for centering table
+\begin{tabular}{c c c c}				% centered columns (4 columns)
+\hline\hline						%inserts double horizontal lines
+% table heading
+Author 						& Linuxv		& Owned 			& Total \\
+							& 			& Files				& Churned \\ [1ex]
+\hline 							% single horizontal line
+% inserting body of the table
+Greg Kroah-Hartman			& 3.8		& 70\%				& 1114\\
+David Howells				& 2.6.19		& 38\%				& 1140\\
+Russell King					& 2.6.27		& 70\%				& 2426\\
+Lucas De Marchi				& 2.6.39		& 64\% 				& 2466\\
+Tejun Heo					& 2.6.34		& 34\% 				& 4222\\
+[1ex]							% adds vertical space
+\hline 							% inserts single line
+\end{tabular}
+\label{table:nonlin} 				% is used to refer this table in the text
+\end{table}
+
+So, we can say that there are certain areas of the system that takes certainly increased attention also there are few developers who deals with extremely large number of files at the time of release.
+Some of them work less than 40\% files that they own and some developers work around 70\% of files that they own.
+Now we would like to see if these areas having increased attention get the similar attention in other releases.
+In this occassion we would like find the Jaccard distance for these areas in consicutive releases.
 
@@
 \bibliography{paper1}
-\appendix
-%Appendix A
-\section{Headings in Appendices}
-Apendix section will be written later with the following subsections may be:
-\subsection{Introduction}
-...
-\subsection{Background and Motivation}
-\subsubsection{Related Works}
-...
-\subsubsection{Methodology and Data}
-...
-\subsection{Conclusions}
-...
-\subsection{Acknowledgments}
-...
-
-\subsection{References}
-... ...
 

### 2013-12-02 images/cumulFileOwnP.r

@@ -1,0 +1,14 @@
+relDCOP <- read.table("~/Documents/git/rupak/scripts/reports/cumul_churn_ownp.rpt",sep="|",header=T)
+
+plot(relDCOP$d_mp, relDCOP$f_mp, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of developers", ylab="")
+lines(relDCOP$d_mp, relDCOP$ownp_mp, type="l", lwd=1.5, lty=2, col="orange")
+lines(relDCOP$d_mp, relDCOP$f_rp, type="l", lwd=1.5, lty=3, col="blue")
+lines(relDCOP$d_mp, relDCOP$ownp_rp, type="l", lwd=1.5, lty=4, col="green")
+
+legend("bottomright", lty=c(1,2,3,4), col = c("red","orange","green","blue"), legend = c("files MP","ownership MP","files RP","ownership RP"))
+
+-------
+plot(relDCOP$f_mp, relDCOP$ownp_mp, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of files", ylab="")
+lines(relDCOP$f_mp, relDCOP$ownp_rp, type="l", lwd=1.5, lty=2, col="orange")
+
+legend("bottomright", lty=c(1,2), col = c("red","orange"), legend = c("ownership MP","ownership RP"))

### 2013-12-02 scripts/reports/rq34/cumul_churn_ownp.r

@@ -1,0 +1,15269 @@
+  ownp  
+   0.00
+ 100.00
+   0.00
+  25.00
+  52.00
+  40.00
+  31.00
+  50.00
+   0.00
+   0.00
+  14.00
+   0.00
+  50.00
+   0.00
+   0.00
+   0.00
+ 100.00
+  80.00
+   0.00
+   0.00
+   0.00
+  33.00
+  50.00
+  90.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+ 100.00
+  15.00
+   0.00
+   7.00
+   0.00
+   0.00
+  38.00
+   0.00
+  50.00
+  33.00
+   0.00
+  27.00
+ 100.00
+  55.00
+   0.00
+   0.00
+   0.00
+   0.00
+  46.00
+   0.00
+   0.00
+  33.00
+  43.00
+  53.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+ 100.00
+   9.00
+  24.00
+   0.00
+   5.00
+   0.00
+   0.00
+  42.00
+  50.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+  33.00
+  25.00
+  37.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   9.00
+   0.00
+   0.00
+   0.00
+  33.00
+   0.00
+   0.00
+  33.00
+  17.00
+  83.00
+   0.00
+   0.00
+  24.00
+  42.00
+   0.00
+  23.00
+ 100.00
+ 100.00
+  28.00
+   0.00
+  41.00
+  35.00
+   0.00
+  50.00
+   0.00
+   5.00
+  33.00
+   7.00
+ 100.00
+   0.00
+  24.00
+   0.00
+  48.00
+   0.00
+   0.00
+ 100.00
+ 100.00
+   0.00
+   0.00
+ 100.00
+ 100.00
+  27.00
+   0.00
+   0.00
+   0.00
+  62.00
+   0.00
+  33.00
+  50.00
+  57.00
+   0.00
+   0.00
+   0.00
+   0.00
+  40.00
+   0.00
+  22.00
+   0.00
+   0.00
+   0.00
+ 100.00
+   0.00
+  60.00
+ 100.00
+  27.00
+   0.00
+  19.00
+   0.00
[…]

### 2013-12-02 scripts/reports/rq34/cumul_churn_ownp_mp.pl

@@ -1,0 +1,49 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $rel_churn_ownp = $dbh_ref->prepare(q{
+	select
+		author, count(path) as files, sum(churn) as tch,
+		round(cast(sum(owned) as numeric)/cast(count(path) as numeric),2)*100 as ownp 
+	from 	dev_area_merge 
+
+	group 	by author
+	order 	by author;
+});
+my $insert = $dbh_ref->prepare(q{insert into cumul_churn_ownp_mp values(?,?,?,?)});
+
+$rel_churn_ownp->execute() or die;
+
+my $i=0;
+my ($totalFiles,$totalChurn,$totalOwnPercent) = 0;
+while(my($author,$files,$tch,$ownp) = $rel_churn_ownp->fetchrow_array){
+	$i++;
+	$totalChurn = $totalChurn + $tch;
+	$totalFiles = $totalFiles + $files;
+	$totalOwnPercent = $totalOwnPercent + $ownp;
+	if($i%10==0){
+		$insert->execute($i,$totalFiles,$totalOwnPercent,$totalChurn);
+	}
+}
+
+$rel_churn_ownp->finish;
+$insert->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-12-02 scripts/reports/rq34/cumul_churn_ownp_rp.pl

@@ -1,0 +1,49 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $rel_churn_ownp = $dbh_ref->prepare(q{
+	select
+		author, count(path) as files, sum(churn) as tch,
+		round(cast(sum(owned) as numeric)/cast(count(path) as numeric),2)*100 as ownp 
+	from 	dev_area_dev 
+
+	group 	by author
+	order 	by author;
+});
+my $insert = $dbh_ref->prepare(q{insert into cumul_churn_ownp_rp values(?,?,?,?)});
+
+$rel_churn_ownp->execute() or die;
+
+my $i=0;
+my ($totalFiles,$totalChurn,$totalOwnPercent) = 0;
+while(my($author,$files,$tch,$ownp) = $rel_churn_ownp->fetchrow_array){
+	$i++;
+	$totalChurn = $totalChurn + $tch;
+	$totalFiles = $totalFiles + $files;
+	$totalOwnPercent = $totalOwnPercent + $ownp;
+	if($i%10==0){
+		$insert->execute($i,$totalFiles,$totalOwnPercent,$totalChurn);
+	}
+}
+
+$rel_churn_ownp->finish;
+$insert->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-12-02 scripts/reports/rq5/lag.r

@@ -1,0 +1,10 @@
+rplag <- read.table('~/Documents/git/rupak/scripts/reports/rq5/rp_lag.rpt', sep = '|', header = T)
+mplag <- read.table('~/Documents/git/rupak/scripts/reports/rq5/mp_lag.rpt', sep = '|', header = T)
+summary(rplag)
+summary(mplag)
+wilcox.test(mplag$lag, rplag$lag)
+qqnorm(rplag$lag)
+qqnorm(mplag$lag)
+boxplot(rplag$lag+1, mplag$lag+1, log = 'y')
+length(rplag$lag)
+length(mplag$lag)

### 2013-12-02 paper1/paper1.tex
all rq finished

@@
 We are expecting this would be the RTR in a release cycle which may introduce technical debts.
-\item Do developers work in others' code in a high proportion during the rush period?
+\item Do developers work in others' code in a high proportion during the rush period?\newline
 Developers work on various files during release period.
@@
 This will give us a sense of the nature of work during release time.
-\item How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?
+\item How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?\newline
 In distributed development environment developers work in different branches they commit their codes to the branches they are associated to.
@@
 \item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)? \newline
-To answer this question we will look into the frequency of file churns made into files. Difference or distance of the files between normal development period and the release period of a release.
+To answer this question we will look into the files getting churned extremely high in number.
+We will try to figure out the difference between those highly churned or highly focused sets of files in different releases to understand if they require contantly high focus or they are only for one particular release.
 \end{enumerate}
@@
 Now we would like to see if these areas having increased attention get the similar attention in other releases.
-In this occassion we would like find the Jaccard distance for these areas in consicutive releases.
+In this occassion we would like find the Jaccard similarity index for these areas in consicutive releases.
+First we collected the sets of files those are having highly increasing focus during the release periods of different release cycles.
+Then we calculated the union and intersection operation between two consicutive sets as well as randomly.
+We applied equation 2 to find  out the similarity among the sets and we see there is no similarity between those sets except for couple of pairs of releases like linuxv2.6.14~linuxv2.6.15,  linuxv2.6.29~linuxv2.6.30, linuxv2.6.30~linuxv2.6.31 and linuxv2.6.34~linuxv2.6.35 where the similarity index is too low to say similar; they are 0.038, 0.066, 0.025 and 0.181 respectively as shown in figure 14.
+From this we understand that developers working for different and various features, developing new staffs for linux kernel working in many different files and merging them into the main kernel during merge window.
+In release period small number of developers who are allowed to work in release period are reviewing those nely arrived codes and doing quick fixes and enhancements, some of them may require very high attention and more work to do.
+In the next release some other different new developments arrive in merge window and thus in release period developer do their candidate releases focusing on those newly arrived code files which are not related to the code files those had to get high focus in the previous release.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{jdRPHighFocusFiles.png}
+\caption{\small \sl Jaccard similarity index between consicutive sets of files having highly increased focus in different releases}
+\end{center}
+\end{figure}
 

### 2013-12-02 scripts/reports/rq6/jd_rd_high_files.pl

@@ -1,0 +1,77 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 0});
+
+my ($prev_release, $release);
+
+#************* Calculate Jaccard Distance Between Merge Period and Development Period *******#
+#****************************** For ALl Releases ********************************************#
+my $union = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
+		UNION
+		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
+	) as e
+});
+my $intersection = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
+		INTERSECT
+		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
+	) as f
+});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select release from stable_releases;
+});
+
+$get_releases->execute or die;
+($prev_release) = $get_releases->fetchrow_array;
+my $i=0;
+print "release_pair | Jaccard_index\n";
+while (($release) = $get_releases->fetchrow_array) {
+	my $jac = 0;
+	if(not $prev_release eq $release){
+
+		$union->execute($prev_release, $release) or die;
+		my $aub = $union->fetchrow_array;
+
+		$intersection->execute($prev_release, $release) or die;
+		my $anb = $intersection->fetchrow_array;
+		
+		if($aub > 0){
+			$jac = $anb / $aub;
+			print "$prev_release~$release | $jac\n";
+		}else{
+			print "a u b is <= 0\n";
+		}
+	}
+	$prev_release = $release;
+	$i++;
+}
+
+$union->finish;
+$intersection->finish;
+$get_releases->finish;
+$dbh_ref->commit;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-12-03 paper1/paper1.tex
updating paper. started writing conclusion

@@
 In this paper we study how RTR may effect project organization and introduce technical debt.
-We want to propose a method to observe, analyze and summarize the results of revisions found around releases.
+We want to propose a method to observe, analyze and summarize the results found around different parts of a release cycle.
 We intend to infer behavior of the developers related to the process around release time.
@@
 We attempt to identify the project's different release times and calculate the difference between different development periods within a releases cycle to identify which new areas are being worked on and what is the behavior of the developers between normal development period and the period when RTR is prompted.
-The historical data from git that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release as well as different periods in a stable release period.
-This information will help us to identify the criteria of the resources, their roles and behaviors, code ownerships of the domains they are working in.
+The historical data from git that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release as well as different parts in a stable release cycle.
+This information will help us to identify the criteria of the resources, their roles and behaviors, code ownerships of the domains they are working in, density of work, nature of dealing with files around the time of release etc.
 
@@
 First couple of research questions are to understand the basic structure and strategies of the development and release and merging process practiced by Linux Kernel development team.
-Rest of the questions are to understand the distribution of developers' working areas and the behavior of developers in different segments of a release period.
+Rest of the questions are to understand the distribution of developers' working areas and the behavior of developers in different segments of a release cycle.
 
-\renewcommand{\labelenumi}{Q\theenumi:}
+\renewcommand{\labelenumi}{RQ\theenumi:}
 \begin{enumerate}
@@
 We will be giving a qualitative description of Linux Kernel development in brief to give anser to this question.
-\item How many developers are allocated troughout different segments of a release period? What significant difference can be observed between the segments of an entire release period? \newline
-Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different periods within a stable release period.
-We will calculate Jaccard Distance to differentiate the behavior of developers during release period and development period.
+\item How many developers are allocated troughout different segments of a release cycle? What significant difference can be observed between the segments of a release cycle? \newline
+Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different parts within a stable release.
 \item Do developers work on different areas of the system around the time of release? \newline
 We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the release period or rc period.
+We are going to introduce an algorithm to traverse through the git DAG to find out commits associated to a particular release.
+This can be useful for any other data collected from distributed version control system like git.
 We are expecting this would be the RTR in a release cycle which may introduce technical debts.
@@
 \item How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?\newline
-In distributed development environment developers work in different branches they commit their codes to the branches they are associated to.
-Developers in that case do not directly push their changes to the main branch.
+In distributed development environment developers work in different branches.
+They commit their codes to the branches they are associated to.
+While core development is going on developers  do not directly push their changes to the main branch.
 We would like to see how much time it takes for a commit to the local branch to get pushed to the main branch.
@@
 \subsection{Finding Commits for Releases}
-We have to sort out and accumulate all the commits together those are belonging to any of the releases that we have.
-We have all 400441 commits in our hand but though we can't plot them into a single time domain to assign different set of commits to different release periods because development goes in parallel on different branches in git so commits also go in parallel.
+We have to sort out and accumulate all the commits together those are belonging to any of the releases.
+We have all 400441 commits in our hand but though we can't plot them into a single time domain to assign different set of commits to different release periods because development goes in parallel on different branches in git, so commits also go in parallel.
 If there are multiple branches, surely there are multiple merges and the commits prior to a crisscross merge are all ancestors of the heads of all subsequent branches \cite{bird_git}.
@@
 We could do this using Git DAG Traversing (GDT) algorithm as shown in Algorithm 1.
-After applying GDT we collected 381152 out of 400441 commits those are well organized in the git DAG for Linux Kernel development.
+After applying GDT we collected 381152 out of 400441 commits those are well organized in the git DAG of Linux Kernel development.
 As we mentioned earlier that we have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12''.
-We are choping out them because we don't have complete release commit data for version 2.6.12-rc as well as 3.12-rc releases.
+We are choping them out because we don't have complete commit records for version 2.6.12-rc releases as well as 3.12-rc releases.
 Out of 400441 commits 19289 are belonging to those releases.
-So finally we have 381152 commits for 340 releases in our database to progress our work on.
+Therefore, finally we have 381152 commits for 331 releases in our database to progress our work on.
 
@@
 \begin{table}[ht]
-\caption{Code Ownership in RP}  % title of Table
+\caption{Code Ownership in Release Period}  % title of Table
 \centering 						% used for centering table
@@
 The highest picks are the merge periods then the smaller picks between the highest ones are representing the rc releases.
-For more clear view we have plotted only 100 releases of all 340 releases including rc candidates.
+For more clear view we have plotted only 100 releases of all 331 releases including rc candidates.
 
@@
 
-\subsection{Difference between release segments}
+\subsection{Difference Between Release Segments}
 \textit{How many developers are allocated troughout different segments of a release period? What significant differ-ence can be observed between the segments of an entire release period?}
@@
 In order to see how many developers contribute to the new featcher developments and how many contribute in merging and fixing, review and accepting codes from the community during the merge period, we observed the developers' area in Merge Period and developers' area in Release Period.
-Out of all 381152 commits belonging to all 340 releases 292926 commits were made during the time of merge period which is 76.85\% (more than 2/3) of the total.
+Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of merge period which is 76.85\% (more than 2/3) of the total.
 These commits were made by 14621 individual developers.
@@
 For calculating Jaccard Distance between two releases we are considering the files that have been worked for, in a particular release.
-If set A is the set of files worked in MP and files worked for in another release is set B then In figure 6 the Jaccard distances between MP and RP for each release can be represented.
+If set A is the set of files worked in MP and files worked for in another release is set B then In figure 6 the Jaccard distances between Merge Period and Release Period for each release can be represented.
 The average jaccard distance between merge period and release period for all the release cycles is 0.85 and we see the jaccard distance is also going upward by releases except the only exception at release 2.6.34.
@@
 
-\subsection{Developers' contributions around the time of release}
+\subsection{Developers' Contributions Around the Time of Release}
 \textit{Do developers work on different areas of the system around the time of release?}\newline
@@
 
-\subsection{Time for commits to go live}
+\subsection{Time for Commits to Go Live}
 \textit{How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?}
@@
 
-\subsection{Developers' focus on code-base around the time of release}
+\subsection{Developers' Focus on Code-Base Around the Time of Release}
 \textit{Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?}
@@
 
-So, we can say that there are certain areas of the system that takes certainly increased attention also there are few developers who deals with extremely large number of files at the time of release.
+So, we can say that there are certain areas of the system that takes certainly increased attention also there are few developers who deal with extremely large number of files at the time of release.
 Some of them work less than 40\% files that they own and some developers work around 70\% of files that they own.
 Now we would like to see if these areas having increased attention get the similar attention in other releases.
+This finding also supports our fourth research question \textit{RQ4} strongly.
 In this occassion we would like find the Jaccard similarity index for these areas in consicutive releases.
@@
 \section{Conclusions}
-This section will be written at the end.
+The results have been reported with respect to our research questions in this case study. We reported following items specifically:
+\renewcommand{\labelenumi}{\theenumi:}
+\begin{enumerate}
+\item{The basic structure and the development process of Linux Kernel}
+\item{The distribution of developers in two different segments in a complete release cycle}
+\item{Role of developers during merge period and the significance of release period}
+\item{Developers' focus around the time of release, percentage of working with native code during merge period and release period.}
+\end{enumerate}
 %\end{document}  % This is where a 'short' article might terminate

### 2013-12-04 paper1/paper1.tex
finished writing all sections.

@@
 
-\title{Re-Allocation of Resources during Releases \titlenote{Copyright note}}
+\title{On Reallocation of Resources during Releases \titlenote{Pelmission to make digital or hard copies of all or part of this work for
+personal or classrooms use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+To copy, to republish, to post on servers or to redistribute to lists,
+requires prior specific permission and/or a fee. Copyright \copyright 2013}}
 \numberofauthors{2}
@@
 \begin{abstract}
-This section will be written at the end.
+Software projects often suffer from lesions in our software industries due to disruptive events what may occur naturally or because of managerial directions.
+Keeping this in mind we have taken an approach to examine the development process of a large software project to understand the nature and behavior of the process and distribution of resources within the different areas of the system.
+By using the historical data from the distributed version control (DVC) system used by that large project we quantify aspects of developers' distribution, code ownership, different release periods, focus on the areas of the code-base, percentage of working with owned files during different periods withing a release cycle for this project.
+This study reveals a unique process performing well extraction of data from Git for the releases of such a large project by which we can perceive significant points of information that can lead us to further decisional analysis aiming novel solutions to the disruptive events for the practitioners of software development.
+
 \end{abstract}
@@
 During the merge window, developers are free to provide any change that is ready for release.
-During the release candinate period, we would expect to see fixs on the files that were changed during the previous merge window.
+During the release candidate period, we would expect to see fixes on the files that were changed during the previous merge window.
 We measure this by comparing the Jaccard distance of merge window with the subsequent rc period, compared with the merge window and subsequent merge window.
@@
 Section 4 will describe methodology of our work and explanation of the data we are working with for this research.
-In section 5 we will dicuss the results of the findings.
-Finally section 6 will conclude the paper.
+In section 5 we will discuss the results of the findings.
+We are describing our limitations and threats to validity in section 6 and finally section 7 will conclude the paper.
 
@@
 We will be giving a qualitative description of Linux Kernel development in brief to give anser to this question.
-\item How many developers are allocated troughout different segments of a release cycle? What significant difference can be observed between the segments of a release cycle? \newline
-Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different parts within a stable release.
+\item How many developers are allocated throughout different segments of a release cycle? What significant difference can be observed between the segments of a release cycle? \newline
+Answer to this question will give us a big picture of Linux Kernel development community as well as the contribution of developers in different parts within a stable release.
 \item Do developers work on different areas of the system around the time of release? \newline
@@
 Developers work on various files during release period.
-We will try to find out what is the percentage of dealing with files that developers own or they are most familier to.
+We will try to find out what is the percentage of dealing with files that developers own or they are most familiar to.
 This will give us a sense of the nature of work during release time.
@@
 To answer this question we will look into the files getting churned extremely high in number.
-We will try to figure out the difference between those highly churned or highly focused sets of files in different releases to understand if they require contantly high focus or they are only for one particular release.
+We will try to figure out the difference between those highly churned or highly focused sets of files in different releases to understand if they require constantly high focus or they are only for one particular release.
 \end{enumerate}
@@
 They have characterized a project's behavior around the time of major and minor releases.
-This is done by partitioning the observed activities like the artiffect check-ins around the dates of major and minor releases, then look for reasonable patterns.
+This is done by partitioning the observed activities like the artifact check-ins around the dates of major and minor releases, then look for reasonable patterns.
 Hindle divided the revisions in each release in 4 different classes, Source Code, Testing, Building, and Documentations.
@@
 We are going to present the steps involved in this process and then we will follow up with an application of our methodology in a case study.
-In order to address our research questions, we obtain key measures of project evolution from the archival data collected from the distributed version contron (DVC) system of Git where all information of the OSS project ``Linux Kernel Development'' is recorded in electronic form.
+In order to address our research questions, we obtain key measures of project evolution from the archival data collected from the distributed version control (DVC) system of Git where all information of the OSS project ``Linux Kernel Development'' is recorded in electronic form.
 Many other OSS projects archive similar data, so the techniques used here can be replicated on any such project.
@@
 A Linux kernel development release version having maximum length of information does look like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
-If a release versioning looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release  in the seriese of the 6th major release of kernel version 2.
+If a release version looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release in the series of the 6th major release of kernel version 2.
 ``linuxv2.6.13\textbf{-rc1}'' says that after the 12th stable minor release had published, development for the next release has been started and rc1 is the first candidate on the way to the next release.
@@
 We have all 400441 commits in our hand but though we can't plot them into a single time domain to assign different set of commits to different release periods because development goes in parallel on different branches in git, so commits also go in parallel.
-If there are multiple branches, surely there are multiple merges and the commits prior to a crisscross merge are all ancestors of the heads of all subsequent branches \cite{bird_git}.
-Figure 1 shows how a git DAG looks like having so many crisscross merges in a busy branching snap-shot of the git DAG of Linux Kernel development.
 \begin{figure}
@@
 \end{figure}
+If there are multiple branches, surely there are multiple merges and the commits prior to a crisscross merge are all ancestors of the heads of all subsequent branches \cite{bird_git}.
+Figure 1 shows how a git DAG looks like having so many crisscross merges in a busy branching snap-shot of the git DAG of Linux Kernel development.
+
 So it is possible to make a commit months ago from today while several releases may have already been made in the mean time but that commit can belong to any future release.
@@
 As we mentioned earlier that we have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12''.
-We are choping them out because we don't have complete commit records for version 2.6.12-rc releases as well as 3.12-rc releases.
+We are chopping them out because we don't have complete commit records for version 2.6.12-rc releases as well as 3.12-rc releases.
 Out of 400441 commits 19289 are belonging to those releases.
 Therefore, finally we have 381152 commits for 331 releases in our database to progress our work on.
-
 \begin{algorithm}
@@
 \end{algorithm}
-
 \subsection{Time-Span of Releases}
 Another information that we require is what are the durations of the releases of Linux kernel development.
-To achieve that we joined the table ``git\_refs\_tags'' where all the releases are stored including the splitted release numbers and the table ``git\_commit'' to give us all the dates of commits for each and every releases, so that we can easily find out the duration between two consecutive releases (including release candidates RC).
+To achieve that we joined the table ``git\_refs\_tags'' where all the releases are stored including the exploited release numbers and the table ``git\_commit'' to give us all the dates of commits for each and every releases, so that we can easily find out the duration between two consecutive releases (including release candidates ``rc'').
 This information will significantly help us because we need to see what is the development period and what are the release periods within a release cycle.
@@
 Table 1 shows a small portion of this information.
-Preior to calculate the developers' areas in secion 4.4 we require this information.
+Prior to calculate the developers' areas in section 4.4 we require this information.
 
@@
 At that time, code which is deemed to be sufficiently stable (and which is accepted by the development community) is merged into the mainline kernel.
-The bulk of changes for a new development cycle (and all of the major changes) will be merged during this time, at a rate approaching 1,000 changes ("patches," or "changesets") per day.
-Strategically linux starts a new kernel release with the merging to get their development branch ready to start development for the next release.
-So there are two main segments in a release period, one is merge window or merge period (MP) where all the developments works get merged together from different branches.
+The bulk of changes for a new development cycle (and all of the major changes) will be merged during this time, at a rate approaching 1,000 changes ("patches," or "change-sets") per day.
+Strategically Linux starts a new kernel release with the merging to get their development branch ready to start development for the next release.
+So there are two main segments in a release period, one is merge window or development period (DP) where all the developments works get merged together from different branches.
 So we can say this is the main development period of a release.
-A merge period remains opened exactly for two weeks \cite{linux_kernel}, many developers are working in many other branches to develop new features once they are ready to push it to the main kernel then they wait for the upcoming merge window and once it's merge period they all contribute their works for the next release during this Merge Period.
+A development period remains opened exactly for two weeks \cite{linux_kernel}, many developers are working in many other branches to develop new features once they are ready to push it to the main kernel then they wait for the upcoming merge window and once it's development period they all contribute their works for the next release during this Development Period.
 Some developers who are mainly responsible to merge new developments verify and accept the new changes and merge them into the main kernel.
@@
 Once all the fixing and enhancements are done for all the codes that had been merged into the main kernel, the release is published.
-We are calling this period of development as the release period (RP) because no new feature development works do not get accepted during this time, it is just the period prior to publishing a new release.
+We are calling this part of a release cycle as the release period (RP) because no new feature development works get accepted during this time, it is just the period prior to publishing a new release.
 
-\subsubsection{Developers' Area in a Merge Period}
-Merge Perid can be determined from the previous release date (of any of major, minor or micro releases) to the date of rc-1 (i.e.\ date of the first candidate release).
-For example if the date of release for ``linuxv2.6.12''  is 2005-06-17 and date of pushing the rc-1 for the next release ``linuxv2.6.13'' is 2005-06-29 then this time period of of 12 days is going to be being called the merge window.
+\subsubsection{Developers' Area in a Development Period}
+Development Period can be determined from the previous release date (of any of major, minor or micro releases) to the date of rc1 (i.e.\ date of the first candidate release).
+For example if the date of release for ``linuxv2.6.12'' is 2005-06-17 and date of pushing the rc1 for the next release ``linuxv2.6.13'' is 2005-06-29 then this time period of of 12 days is going to be called as the merge window or development period.
 Thousands of commits get pushed in the main branch during this period.
-Table 2 shows merge periods of some releases.
+Table 2 shows the development periods of some releases.
 
 \begin{table}[ht]
-\caption{Release Merging Periods}  % title of Table
+\caption{Development Periods (Merge Window)}  % title of Table
 \centering 						% used for centering table
@@
 \begin{table}[ht]
-\caption{Developers' Areas in Merge Period}  % title of Table
+\caption{Developers' Areas in Development Period}  % title of Table
 \centering 						% used for centering table
@@
 
-In this table we see in a merge period within a release cycle D.
+In this table we see in a development period within a release cycle D.
 S.
 Miller has made change in pci.h file only once where he has made 8 churns.
-In the similar approach we calculate developers' areas in release period and also for merge period.
+In the similar approach we calculate developers' areas in release period and also for development period.
 
 \subsubsection{Developers' Areas in Release Period}
-As like merge period we can extract developers working in code files during release period.
+As like development period we can extract developers working in code files during release period.
 Release Period here in Linux Kernel development process is being considered as since the date of rc1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the date of the next stable release.
@@
 \subsection{Finding Code Ownership}
-So many developers are working from different development communities throught different development branches.
+So many developers are working from different development communities throughout different development branches.
 We tried to investigate the "code ownership" \cite{mockus_case_study} evolved in Linux Kernel development.
@@
 This information yet does not tell about the ownership, we need to find out ownership for each developer in different development areas in a release cycle.
-We already have the collection of developers working in merge period and release period within a release cycle and stored them with corresponding files they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
+We already have the collection of developers working in development period and release period within a release cycle and stored them with corresponding files they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
 We now update those information with the ownership information.
@@
 Gutwin did \cite{gutwin_awareness} for finding out the main developers' group for a project.
-We calculate code ownership for both Merge Period and Release Period.
-We also canculate general ownership for all the developers for all the files they have worked ever.
+We calculate code ownership for both Development Period and Release Period.
+We also calculate general ownership for all the developers for all the files they have worked ever.
 Table 6 represents a part of the data which shows the ownerships of the developers in each release cycle.
@@
 The example given above is calculated for finding ownerships of developers worked for different files in different releases.
-Ownership is calculated for all the developers in release periods as well as in merge period.
-In addition we have calculated which file is owned by which developer and also the percentage of working with owned files during merge meriod and release period seperately.
+Ownership is calculated for all the developers in release periods as well as in development period.
+In addition we have calculated which file is owned by which developer and also the percentage of working with owned files during development and release period separately.
 These extractions will help us drawing the results from our findings to answer our 3rd and 4th research questions.
@@
 From the figure we can see the average duration of each stable release is 62.47 although ``linuxv2.6.24'' was significantly hight as exception, it took 92.8 days.
-The bottom line which is much steady than the upper one is representing the durations of merge period in each stable release.
-If we put the releases in a time domain we can see a picture shown in figure 3 where we see that the stable releases are all going on maintaining almost a similar frequency and similar pattern.
-The highest picks are the merge periods then the smaller picks between the highest ones are representing the rc releases.
+The bottom line which is much steady than the upper one is representing the durations of development period in each stable release.
+If we put the releases in a time domain we can see a picture shown in figure 2 where we see that the stable releases are all going on maintaining almost a similar frequency and similar pattern.
+The highest picks are the development periods then the smaller picks between the highest ones are representing the rc releases.
 For more clear view we have plotted only 100 releases of all 331 releases including rc candidates.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{relTimeDomain100.png}
+\caption{\small \sl Time Domain for Releases}
+\end{center}
+\end{figure}
 
@@
 Usually every micro release (ex.\ linuxv2.6.x) is a major kernel release with new features, internal API changes, and more.
-A minor release (ex.\ linuxv3.11) can have around  10 thousand changesets with several hundred thousands of churned lines of  codes (LOC).
-At the beginning of each stable release the merge window i.e.\ merge period gets opened and all the accepted and stable codes from the community are merged having around 1000 of churns everyday.
-Merge period approximately for 14 days as shown in the figure 2.
+A minor release (ex.\ linuxv3.11) can have around 10 thousand change-sets with several hundred thousands of churned lines of codes (LOC).
+At the beginning of each stable release the merge window i.e.\ development period gets opened and all the accepted and stable codes from the community are merged having around 1000 of churns everyday.
+Development period approximately for 14 days as shown in the figure 3.
 The bottom line is representing the merge windows of every releases.
-We don't have the merge period data for the very first one that's why it's starting from 0.
-
-After getting all the major works merged development period for the next release is announced to be opened.
-If the next release is going to be linuxv2.6.14 then the release pushed at the end of the merge window will be called linuxv2.6.14-rc1.
-\textbf{-rc1} release indecates that the time to stabilize the next kernel has begun.
-These candidate releases continu to be pushed for once a week.
-If there is any bug fix or any high-priority change only then that goes to the main line during this period.
-With the continuous rc releases when the new kernel seems to be stable then the it goes for the stable release.
-Again after the core features are pushed to the main line, merge window gets opened and accepts all other feature developments, patchsets from other branches.
+We don't have the development period data for the very first one that's why it's starting from 0.
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{relTimeDomain100.png}
-\caption{\small \sl Time Domain for Releases}
-\end{center}
-\end{figure}
+After getting all the major works merged, release period for the next release is announced to be opened.
+If the next release is going to be linuxv2.6.14 then the release pushed out at the end of the merge window will be called linuxv2.6.14-rc1.
+\textbf{-rc1} indicates that all the new features or developments are merged now the time to stabilize the next kernel has begun.
+These candidate releases continue to be pushed for once a week.
+If there is any bug fix or any high-priority change only then that goes to the main line during this period.
+With the continuous rc releases when the new kernel seems to be stable then it goes to publish the next stable release.
+Again merge window gets opened and accepts more new features, patch-sets from different branches.
 
-As a summary, the description above helps to address some of the questions about how Linux Kernel development is organized.
+As a summary, the description above helps us to address some of the questions about how Linux Kernel development is organized.
 Answer to this first research question provides essential background for understanding our quantitative results.
@@
 \subsection{Difference Between Release Segments}
-\textit{How many developers are allocated troughout different segments of a release period? What significant differ-ence can be observed between the segments of an entire release period?}
+\textit{How many developers are allocated troughout different segments of a release period? What significant difference can be observed between the segments of an entire release period?}
 
-In order to see how many developers contribute to the new featcher developments and how many contribute in merging and fixing, review and accepting codes from the community during the merge period, we observed the developers' area in Merge Period and developers' area in Release Period.
-Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of merge period which is 76.85\% (more than 2/3) of the total.
+In order to see how many developers contribute to the new feature developments and how many contribute in merging and fixing, review and accepting codes from the community during the development period, we observed the developers' area in Development Period and developers' area in Release Period.
+Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of development period which is 76.85\% (more than 2/3) of the total.
 These commits were made by 14621 individual developers.
-We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for thse releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later.
-11209 developers work in merge period and 7625 developers work around the release period.
+We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for these releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later.
+11209 developers work in development period and 7625 developers work around the release period.
 
-In figure 4 we see the boxplot showing that a very large number of developers contribute during the merge period which is in a sense the main development period because all the development branches get merged together during this time, all the new features come into the main branch of the kernel.
+In figure 4 we see the boxplot showing that a very large number of developers contribute during the development period which is in a sense the main development period because all the development branches get merged together during this time, all the new features come into the main branch of the kernel.
 In release period significantly small number of developers work and this number looks pretty steady for all the releases only a couple of high number appeared in two releases as we see in figure 4.
@@
 \includegraphics[height=1.7in,width=3.4in]{devsMPRPbox.png}
-\caption{\small \sl Developers working in MP \& RP}
+\caption{\small \sl Developers working in DP \& RP}
 \end{center}
@@
 
-Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ Merge Period MP and Release Period RP).
+Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ Development Period DP and Release Period RP).
 To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by equation 3.
@@
 Here A and B are two sets.
-For calculating Jaccard Distance between two releases we are considering the files that have been worked for, in a particular release.
-If set A is the set of files worked in MP and files worked for in another release is set B then In figure 6 the Jaccard distances between Merge Period and Release Period for each release can be represented.
-The average jaccard distance between merge period and release period for all the release cycles is 0.85 and we see the jaccard distance is also going upward by releases except the only exception at release 2.6.34.
+For calculating Jaccard distance between two releases we are considering the files that have been worked for, in a particular release.
+If set A is the set of files worked in DP and files worked for in another release is set B then In figure 6 the Jaccard distances between Development Period and Release Period for each release can be represented.
+The average jaccard distance between development period and release period for all the release cycles is 0.85 and we see the Jaccard distance is also going upward by releases except the only exception at release 2.6.34.
 
@@
 \includegraphics[height=1.7in,width=3.4in]{jdMPRP.png}
-\caption{\small \sl Jaccard Distance between the Merge Period and Release Period}
+\caption{\small \sl Jaccard Distance between the Development Period and Release Period}
 \end{center}
@@
 How many of them they really own and how many files they work that they do not own.
-We also want to know about the code ownership of the developers around the time of release as well as around the time of main development works that get merged during merge meriod.
+We also want to know about the code ownership of the developers around the time of release as well as around the time of main development works that get merged during development period.
 
-In order to understand the distribution of the developers around the system we also found that during these release periods 11209 developers have experience of working in the merge meriod and 7625 developers worked in the release period as we already mentioned earlier but we noted that 4908 developers contribute in both merge period and the release period that means near about half (43.78\%) of the developers work during the merge period are shared that means they work for core developments and also bug fixing or minor enhancement works.
+In order to understand the distribution of the developers around the system we also found that during these release periods 11209 developers have experience of working in the development period and 7625 developers worked in the release period as we already mentioned earlier but we noted that 4908 developers contribute in both development period and the release period that means near about half (43.78\%) of the developers work during the development period are shared that means they work for core developments and also bug fixing or minor enhancement works.
 Figure 7 representing the venn diagram.
@@
 \includegraphics[height=1.3in,width=2.3in]{devDistMPRPvenn.png}
-\caption{\small \sl Developers' Distribution in Merge Period and Development Period}
+\caption{\small \sl Developers' Distribution in Development Period and Release Period}
 \end{center}
@@
 
-From release ``linuxv2.6.13'' to ``linuxv3.11'' We examine the contribution in writing code by the developers to understand the behaviour during the two vital segments in a release cycle.
-Figure 8 plots the cumulative representation of the percentage of working with owned files ($\omega$\textit{MP}) during the merge period and the percentage of working with owned files ($\omega$\textit{RP}) during release period of ``linuxv2.6.13''.
+From release ``linuxv2.6.13'' to ``linuxv3.11'' We examine the contribution in writing code by the developers to understand the behavior during the two vital segments in a release cycle.
+Figure 8 plots the cumulative representation of the percentage of working with owned files ($\omega$\textit{MP}) during the development period and the percentage of working with owned files ($\omega$\textit{RP}) during release period of ``linuxv2.6.13''.
 From the figure It can be observed that with the increase of every 10 files that developers working in, $\omega$\textit{RP} is going down apart from the line of $\omega$\textit{MP}.
@@
 \includegraphics[height=1.7in,width=3.4in]{cumulFileOwnP.png}
-\caption{\small \sl Cumulative percentage of working with owned files in MP and RP of release 2.3.13}
+\caption{\small \sl Cumulative percentage of working with owned files in DP and RP of release 2.3.13}
 \end{center}
@@
 
-If we simply compare the percentage of working in owned files during merge period ($\omega$\textit{MP}) and the percentage of working in owned files during release period ($\omega$\textit{RP}) for each developer then we see a significant difference of the mean lines as shown in figure 9.
+If we simply compare the percentage of working in owned files during development period ($\omega$\textit{MP}) and the percentage of working in owned files during release period ($\omega$\textit{RP}) for each developer then we see a significant difference of the mean lines as shown in figure 9.
 In release period developers work with less number of files that they own.
 
-So we can say that in Linux Kernel development developers work in more unfamilier files during the release period.
-Before the release period main development works are accepted from different branches and they get merged together with main kernel, so, core feature developers finishes their duty for a particular feature development for a particular release within the time of merge period althoug some contributors still work during the release period where basically they work on fixing, testing and minor enhancement related work on the codes that have been merged and accepted from various developers from other branches.
+So we can say that in Linux Kernel development developers work in more unfamiliar files during the release period.
+Before the release period main development works are accepted from different branches and they get merged together with main kernel, so, core feature developers finishes their duty for a particular feature development for a particular release within the time of development period although some contributors still work during the release period where basically they work on fixing, testing and minor enhancement related work on the codes that have been merged and accepted from various developers from other branches.
 It is clear now that during the release period developers work mostly on others' works, the proportion of working with owned files is lower around the release than the proportion during normal development time.
@@
 \includegraphics[height=1.7in,width=3in]{ownpMPRPbox.png}
-\caption{\small \sl Percentage of working in owned files during Merge Period and Release Period}
+\caption{\small \sl Percentage of working in owned files during Development Period and Release Period}
 \end{center}
@@
 
-So, finally we can say that in merge periods developers work in more native codes while during the regular release development period the percentage of working with native code is very low in number although this percentage of working in owned code during merge period does not significantly relate to other co-factors.
+So, finally we can say that in development periods developers work in more native codes while during the regular release development period the percentage of working with native code is very low in number although this percentage of working in owned code during development period does not significantly relate to other co-factors.
 
@@
 
-There are thousands of commits goes to the main kernel during the merge meriod.
+There are thousands of commits goes to the main kernel during the merge window.
 All they are to be considered as the normal development commits or regular development or core development commits for developing new features to the kernel.
-Merge period remains opened for two weeks only, the development works that are supposed to go for a particular release are not developed during this couple of weeks.
+Merge window remains opened for two weeks only, the development works that are supposed to go for a particular release are not developed during this couple of weeks.
 These have been developed since many days ago on a different development branch by any developer.
-For a particular feature that is going to the current release there are hundreds of commits, obviously all these commits are not made during the merge period of the current release 90-100\% commits must have been made before the opening of the merge period of current release.
+For a particular feature that is going to the current release there are hundreds of commits, obviously all these commits are not made during the merge window of the current release 90-100\% commits must have been made before the opening of the merge window of current release.
 As described in section 4.3, we have sorted up the releases according to the git DAG.
@@
 Comperatively lag for the feature development commits is quite high.
-Median for the lags for the commits during this time is 5.57 while median for the lags for the commits goes to the main kernel during merge period is 26.15 which is a significant different between these two periods of a release cycle.
+Median for the lags for the commits during this time is 5.57 while median of the lags for the commits going to the main kernel of the development  period is 26.15, which is a significant different between these two parts of a release cycle.
 
@@
 What is the percentage of ownership of them while working for a large number of files in a release period?}
-\item{If there is any area that requires increased attention in the system, then what is the jaccard distance of those areas throught different releases?
+\item{If there is any area that requires increased attention in the system, then what is the Jaccard distance of those areas throughout different releases?
 Are they being focused iteratively by releases?}
@@
 Similar picture we see for other releases also.
-Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high and being marked as outliars as shown in figure 12.
+Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high and being marked as outliers as shown in figure 12.
 For almost every release cycle during the release period around 2.846 files get highly increased attention having over 5000 churns and 16.78 files having over 1000 churns as shown in figure 13.
@@
 
-We found that there are 29 releases out of the 39 where developers are working in comperatively large number of files during the release period?
+We found that there are 29 releases out of the 39 where developers are working in comparatively large number of files during the release period?
 Among them we noted that 5 developers in 5 different release periods worked for extremely high number of files as listed in table 6.
@@
 This finding also supports our fourth research question \textit{RQ4} strongly.
-In this occassion we would like find the Jaccard similarity index for these areas in consicutive releases.
+In this occasion we would like find the Jaccard similarity index for these areas in consecutive releases.
 First we collected the sets of files those are having highly increasing focus during the release periods of different release cycles.
-Then we calculated the union and intersection operation between two consicutive sets as well as randomly.
+Then we calculated the union and intersection operation between two consecutive sets as well as randomly.
 We applied equation 2 to find out the similarity among the sets and we see there is no similarity between those sets except for couple of pairs of releases like linuxv2.6.14~linuxv2.6.15, linuxv2.6.29~linuxv2.6.30, linuxv2.6.30~linuxv2.6.31 and linuxv2.6.34~linuxv2.6.35 where the similarity index is too low to say similar; they are 0.038, 0.066, 0.025 and 0.181 respectively as shown in figure 14.
-From this we understand that developers working for different and various features, developing new staffs for linux kernel working in many different files and merging them into the main kernel during merge window.
-In release period small number of developers who are allowed to work in release period are reviewing those nely arrived codes and doing quick fixes and enhancements, some of them may require very high attention and more work to do.
+From this we understand that developers working for different and various features, developing new staffs for Linux kernel working in many different files and merging them into the main kernel during merge window.
+In release period small number of developers who are allowed to work in release period are reviewing those newly arrived codes and doing quick fixes and enhancements, some of them may require very high attention and more work to do.
 In the next release some other different new developments arrive in merge window and thus in release period developer do their candidate releases focusing on those newly arrived code files which are not related to the code files those had to get high focus in the previous release.
@@
 \includegraphics[height=1.7in,width=3.4in]{jdRPHighFocusFiles.png}
-\caption{\small \sl Jaccard similarity index between consicutive sets of files having highly increased focus in different releases}
+\caption{\small \sl Jaccard similarity index between consecutive sets of files having highly increased focus in different releases}
 \end{center}
+
 \end{figure}
+\section{Threats to Validity}
+Throught the paper we have done number of measurements to analyze the structure of an OSS software project development, behavior of the developers in different parts of the system, allocation and re-allocation of resources around the time of release and around the time of development.
+The results have been reported with respect to our research questions in this case study.
+We reported following items by our measurements:
+\renewcommand{\labelenumi}{\theenumi.}
+\begin{enumerate}
+\item{The basic structure and the development process of Linux Kernel.}
+\item{The distribution of developers in two different segments in a complete release cycle.}
+\item{Role of developers during development period and the significance of release period.}
+\item{Developers' focus around the time of release, percentage of working with native code during development period and release period.}
+\end{enumerate}
+Now, are these measurements and findings really meaningful, are they quantifying what we want them to?\newline\newline
+\textbf{Construct Validity} To study the distribution and allocation of developers or resources around the development system for a large project, the very initial step should be understanding the project development strategy which project data we are studying on.
+Looking for the answer to our first research question is an obvious in this context where we clearly understood the history and flow of the development process of Linux Kernel, what are the durations of every release how can we distinguish different parts within a release cycle and so on.
+Once we get the different segments or distinguishable parts of a release cycle we feel the urgency to understand their external and internal behaviors also the relation of the resources, role of developers around them.
+Our second research question tells us every details on these and our third, fourth and fifth research questions take us more into the deep of this analysis to discover some core points of information from where we may start thinking of something different that may help us to progress our work farther more by setting any goal based on new hypothesis to come up with any decision.
+Our last research question is really giving us some meaningful discoveries to plot the critical true scenario of developers with code-base of a project.\newline\newline
+\textbf{Internal Validity} Is there any cause and effect relation between the changes in certain attributes and the results that we represented?
+In our methodology we actually picked few attributes like version of the release, sable release and candidate release, release commits, different periods within a release cycle like merge window or development period and release period, ownership, lag for commits in different periods, percentage of working with owned files during development and release periods, file churns, highly increasingly focused files, Jaccard distance between the sets of files of these types.
+The first attribute ``versions'' may vary with many other software projects so the data extraction model that we have used may not me similar to other projects but the GDT algorithm that we have used for acqumulating the commits associated to releases will be useful for other software projects having Git as the version control system.\newline\newline
+\textbf{External Validity} As our aim is to understand the allocation and re-allocations of the resources around the release of a software project we wanted to make a study with a large project and so we started our study with Linux Kernel development where we got approximately 400441 commit records made by thousands of developers for 340 releases (including stable and candidates).
+Can we generalize our results to other software projects?
+Although we looked into a large open source software, this is only one system we looked into.
+We need to analyze the development strategy and distribution of resources for others software projects also.
+We have plan to go for similar kind of analysis on other historical projects both OSS and non-OSS to generalize our findings and results by cross-validation across projects.\newline\newline
+\textbf{Reliability} The data we used for our study is highly reliable.
+It has been derived from the version control system that Linux Kernel development using.
+Other projects using similar version control system can easily run the same experiments to produce findings specific to those projects and to compare with our findings.\newline\newline
+\textbf{Limitations} The results and findings of our study is currently based on a single project due to the limited access to such rich historical data.
+We hope to study more other OSS projects as well as non-OSS projects to ensure the validity and generality of our findings in the future.
 
 \section{Conclusions}
-The results have been reported with respect to our research questions in this case study. We reported following items specifically:
-\renewcommand{\labelenumi}{\theenumi:}
-\begin{enumerate}
-\item{The basic structure and the development process of Linux Kernel}
-\item{The distribution of developers in two different segments in a complete release cycle}
-\item{Role of developers during merge period and the significance of release period}
-\item{Developers' focus around the time of release, percentage of working with native code during merge period and release period.}
-\end{enumerate}
+Software development in a large team is really a complex process to deal with.
+Resource re-allocation is an important phenomenon in regard of software development especially in a large development environment.
+We were aiming to find out some points of crucial information that may lead us to move forward to come up with any new hypothesis or any decision about the rush period of release and the distribution of developers having in-equal hold on the code-base of the system which is strongly related to the disruptive events occur in software development industries.
+We also were concerned about the dead areas of the system that often creates technical debts and we could see in our results that files having highly focus around the release periods are being handled by developers who may have high percentage of familiarity with them or may have pretty low but we did not find those files to be worked on in further releases.
+This may be due to those codes files are developed in such a way that they never require any fix or any new feature cannot be implemented based on them or new developers have no idea about those files which makes them not to touch those files rather make them interested to create new files for new works.
+We would like to investigate these matters in future to come up with more significant discoveries possibly with new decisional ideas about the disruptive events of software systems.
+
 %\end{document}  % This is where a 'short' article might terminate

### 2013-12-05 paper1/paper1.tex
updating paper and added presentation slide, directory structure changed

@@
 So we are having 340 releases including major, minor, micro and rc; 39 stable releases from ``linuxv2.6.11'' to ``linuxv3.11'' having complete data with us.
-We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers.
+We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 13926 developers' commit history among 14621 distinct developers.
 Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once.
@@
 Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of development period which is 76.85\% (more than 2/3) of the total.
-These commits were made by 14621 individual developers.
+These commits were made by 13926 individual developers.
 We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for these releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later.
@@
 \includegraphics[height=1.7in,width=3.4in]{devsMPRP.png}
-\caption{\small \sl Increasing contribution in RDP}
+\caption{\small \sl Increasing contribution in DP}
 \end{center}
@@
 \includegraphics[height=1.7in,width=3in]{fileChurnRPbox.png}
-\caption{\small \sl Files churned in release periods}
+\caption{\small \sl Number of Files churned in release periods}
 \end{center}

### 2013-12-10 paper1/latex/paper1.tex
rescructuring directories, completed paper for the course

--- 2013-12-05 paper1/paper1.tex
@@
 
-\title{On Reallocation of Resources during Releases \titlenote{Pelmission to make digital or hard copies of all or part of this work for
+\title{On Reallocation of Resources during Releases \titlenote{Permission to make digital or hard copies of all or part of this work for
 personal or classrooms use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
@@
        \affaddr{Montreal, QC H3G 1M8}\\
-       \affaddr{438-932-2288, +1}\\
        \email{mdt\_rahm@encs.concordia.ca}
@@
        \affaddr{Montreal, QC H3G 1M8}\\
-       \affaddr{514-848-2424, +1}\\
        \email{peter.rigby@concordia.ca}
@@
 \begin{abstract}
-Software projects often suffer from lesions in our software industries due to disruptive events what may occur naturally or because of managerial directions.
+Software projects often suffer from lesions in software industries due to disruptive events what may occur naturally or because of managerial directions.
 Keeping this in mind we have taken an approach to examine the development process of a large software project to understand the nature and behavior of the process and distribution of resources within the different areas of the system.
 By using the historical data from the distributed version control (DVC) system used by that large project we quantify aspects of developers' distribution, code ownership, different release periods, focus on the areas of the code-base, percentage of working with owned files during different periods withing a release cycle for this project.
-This study reveals a unique process performing well extraction of data from Git for the releases of such a large project by which we can perceive significant points of information that can lead us to further decisional analysis aiming novel solutions to the disruptive events for the practitioners of software development.
+This study reveals a unique process performing well extraction of data from Git for the development of a large open source project by which we can perceive significant points of information that can lead us to further decisional analysis aiming novel solutions to the disruptive events for the practitioners of software development.
 
@@
 Software projects are notorious for going over budget and schedule.
-Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{brooks_mythical}.
-This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor.
+Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study ``The Mythical Man Month'' \cite{brooks_mythical}.
+This ``Rush To Release (RTR)'' can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor.
 Alternatively, the rush may simply be due to inappropriate or unrealistic scheduling.
@@
 \item What is the release process used by the project? \newline
-We will be giving a qualitative description of Linux Kernel development in brief to give anser to this question.
+We will be giving a qualitative description of Linux Kernel development in brief to answer this question.
 \item How many developers are allocated throughout different segments of a release cycle? What significant difference can be observed between the segments of a release cycle? \newline
-Answer to this question will give us a big picture of Linux Kernel development community as well as the contribution of developers in different parts within a stable release.
+Answer to this question will give us a brief information of Linux Kernel development community as well as the contribution of developers in different parts within a stable release.
 \item Do developers work on different areas of the system around the time of release? \newline
-We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the release period or rc period.
+We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the release period.
 We are going to introduce an algorithm to traverse through the git DAG to find out commits associated to a particular release.
@@
 
-\section{Methodology and Data}
+\section{Methodology}
 This section presents our methodology for discovering information which can give us the idea to get the answers to our research questions.
@@
 \subsection{Data Extraction}
-We went for the VCS of a target project and either mirror the repository or download every revision and commit log history data.
+We collected data from the version control system of a target project and either mirror the repository or download every revision and commit log history data.
 From DVCSs such as Git we extract the revisions and release information.
-We wrote Perl scripts to extract date that was further processed to obtain details.
-Manual inspection was used to resolve problems and things like that in cases where all automated techniques failed.
-We then put them into a database.
-We have used PSQL database to create tables in, to store our extracted data.
+We wrote Perl scripts to extract date and managed them in Postgre SQL database to create tables in, to store our extracted data.
 These extracted data will be analyzed by us later on.
-Per each revision the information extracted includes the commit id, tree id, author of the revision, date of revision, the name of the revised file, parent and child info for the revision and the detail log information.
+For each revision the information extracted includes the commit id, tree id, author of the revision, date of revision, the name of the revised file, parent and child info for the revision and the detail log information.
 Once extraction is completed we are ready to partition the version numbers (Section 4.3) and duration  of each release (Section 4.4).
@@
 We stored the extracted git commit log data into the tables git\_commit and git\_revision where all the basic and detail log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
-By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can determine which commit belongs to which version and release, and also what type of release that is.
+By joining these tables we can easily get the dates of each version and from the version number we can determine which commit belongs to which version and release, and also what type of release that is.
 
-Commits those are made for pushing a release have release tags associated to them by which we can understand which commit belongs to which version of release; is this a major release or minor or a micro stable release.
+Commits those are made for pushing a release have release tags associated to them by which we can understand which commit is made for a release; is this a major release or minor or a micro stable release.
 Another information we have captured that is \textbf{rc} which indicates that the particular commit was a release candidate.
@@
 \subsection{Finding Commits for Releases}
-We have to sort out and accumulate all the commits together those are belonging to any of the releases.
+We have to sorted out and accumulated all the commits together belonging to any of the releases.
 We have all 400441 commits in our hand but though we can't plot them into a single time domain to assign different set of commits to different release periods because development goes in parallel on different branches in git, so commits also go in parallel.
@@
 So it is possible to make a commit months ago from today while several releases may have already been made in the mean time but that commit can belong to any future release.
-Commits that are being made to a branch may get merged with other branch or the head branch during the release period.
+Commits that are being made to a branch may get merged with any other branch or the head branch during the merge period.
 This is why we had to track all the way down the trees for each of the 340 releases in the git DAG to find out which commit contributes to which release.
-We could do this using Git DAG Traversing (GDT) algorithm as shown in Algorithm 1.
-After applying GDT we collected 381152 out of 400441 commits those are well organized in the git DAG of Linux Kernel development.
-As we mentioned earlier that we have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12''.
-We are chopping them out because we don't have complete commit records for version 2.6.12-rc releases as well as 3.12-rc releases.
+We could do this using Git DAG Traversing (GDT) algorithm as described in Algorithm 1.
+After applying GDT we collected 381152 commits out of 400441 those are well organized in the git DAG of Linux Kernel development.
+As we mentioned earlier that we have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' those we are chopping out because we don't have complete commit records for the release cycle linuxv2.6.12 releases as well as linuxv3.12.
 Out of 400441 commits 19289 are belonging to those releases.
-Therefore, finally we have 381152 commits for 331 releases in our database to progress our work on.
+Therefore, finally we have 381152 commits for 331 releases in our database to progress our work on where 39 release are stable.
 \begin{algorithm}
-\caption{GDT: to find Commits within Releases}
+\caption{GDT: Git Dag Traversing}
 \begin{algorithmic}[1]
@@
 Table 1 shows a small portion of this information.
-Prior to calculate the developers' areas in section 4.4 we require this information.
+Prior to calculate the developers' areas in section 4.4 we need this information.
 
@@
 Our farther works will be proceeded based on these 39 releases only.
-As we don't have the complete release information for 3.12 or later as well as for 2.6.12 and earlier ones.
 
-\subsection{Calculate Developers' Area}
-Developers are working throughout the release time.
-Here ``Developers' Area'' means the files developers work in within a release cycle.
+\subsection{Developers' Area}
+Developers are working throughout the all the time.
+Some are working during the release period, at the same time some people may be working for any new feature development for any future release.
+Here ``Developers' Area'' means the files developers work in those are going to be merged in a release.
 It doesn't refer to the file itself but it is important to understand which files are being touched by which developers.
 We see that authors are committing files almost everyday throughout a release but this does not make sure that these commits are going to the next release because commits are being made in different branches and all branches are not supposed to get merged to the next release.
-We have the commit log data in our hand and we know what is the duration for each and every release (i.e.\ start and end dates).
-Now it is possible to find out which commits were made for which files by which developer within a certain time range of a release.
+Using GDT we have acqumulated all the commits finally went to a particular release.
+Now it is possible to find out which commits were made for which files by which developer for a release.
 
@@
 We have the commits contributed to releases and every record explains us who committed the file when did this get churned.
-If we run an SQL query then we can easily find out for every author and for every particular file how many times a it has been committed by an author and how many churns (addition + deletion = churn) developer has made.
+If we run an SQL query then we can easily find out for every author and for every particular file how many times a it has been committed by an author and how many churns (lines added + lines deleted) a developer has made.
 We calculate developers' working areas and store the information into a table.
@@
 
-In this table we see in a development period within a release cycle D.
+In this table we see, in a development period within a release cycle D.
 S.
-Miller has made change in pci.h file only once where he has made 8 churns.
-In the similar approach we calculate developers' areas in release period and also for development period.
+Miller has made change in ``pci.h'' file only once where he has made 8 churns.
+In the similar approach we calculate developers' areas in release period.
 
@@
 So many developers are working from different development communities throughout different development branches.
-We tried to investigate the "code ownership" \cite{mockus_case_study} evolved in Linux Kernel development.
+We tried to investigate the ``code ownership'' \cite{mockus_case_study} evolved in Linux Kernel development.
 Here code ownership is going to be represented as a percentage of making churns by a developer with respect to the total churns made to a particular file.
-From the data that we have for complete releases (``linuxv2.6.13'' to ``linuxv3.11'') we found 70210 distinct files that have been churned by developers.
+From the data of all 39 releases we found 70210 distinct files have been churned by developers.
 We removed those files where no developer made any churn at all during these 39 releases.
@@
 The highest picks are the development periods then the smaller picks between the highest ones are representing the rc releases.
-For more clear view we have plotted only 100 releases of all 331 releases including rc candidates.
+For more clear view we have plotted only 100 releases of 331 releases including release candidates.
 
@@
 
-Linux Kernel development uses Rolling Release Development Model.
+Linux Kernel development uses ``Rolling Release Development Model''.
 Usually every micro release (ex.\ linuxv2.6.x) is a major kernel release with new features, internal API changes, and more.
@@
 If the next release is going to be linuxv2.6.14 then the release pushed out at the end of the merge window will be called linuxv2.6.14-rc1.
-\textbf{-rc1} indicates that all the new features or developments are merged now the time to stabilize the next kernel has begun.
+\textbf{rc1} indicates that all the new features or developments are merged now the time to stabilize the next kernel has begun.
 These candidate releases continue to be pushed for once a week.
@@
 \subsection{Difference Between Release Segments}
-\textit{How many developers are allocated troughout different segments of a release period? What significant difference can be observed between the segments of an entire release period?}
+\textit{How many developers are allocated troughout different segments of a release period?
+What significant difference can be observed between the segments of an entire release cycle, also between two consecutive releases?}
 
 In order to see how many developers contribute to the new feature developments and how many contribute in merging and fixing, review and accepting codes from the community during the development period, we observed the developers' area in Development Period and developers' area in Release Period.
-Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of development period which is 76.85\% (more than 2/3) of the total.
-These commits were made by 13926 individual developers.
-We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for these releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later.
-11209 developers work in development period and 7625 developers work around the release period.
+Out of all 381152 commits belonging to 331 releases 292926 commits were made during the time of development period which is 76.85\% (more than 2/3) of the total.
+These commits were made by 13926 individual developers, 11209 developers work in development periods and 7625 developers work around the release periods.
 
@@
 
-Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ Development Period DP and Release Period RP).
+Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release cycle.
 To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by equation 3.
@@
 
-If we simply compare the percentage of working in owned files during development period ($\omega$\textit{MP}) and the percentage of working in owned files during release period ($\omega$\textit{RP}) for each developer then we see a significant difference of the mean lines as shown in figure 9.
+If we simply compare the percentage of working in owned files during development period ($\omega$\textit{MP}) and the percentage of working in owned files during release period ($\omega$\textit{RP}) for each developer then we see a significant difference of the mean lines as shown in figure 10.
 In release period developers work with less number of files that they own.
 
+To obseve the similarity of files being worked on in different development periods of releases we can have a look at figure 9.
+Here x axis represents the consecutive release pairs and y axis for the Jaccard similarity index.
+In this figure we see the line which is representing the jaccard similarity index for files being worked in consecutive development periods is upper enough to the line representing jaccard similarity index for files being worked in consecutive release periods.
+Which does make sense that around the time of release developers work in more in different and random files that's why possibility of the similarity with the files that are worked in previous release's RP and the files that are worked in current release is very low.
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{j_file_MPMPvRPRP.png}
+\caption{\small \sl Jaccard similarity index between consecutive releases (for both DP and RP). X-axis: consecutive release pairs, Y-axis: J-index}
+\end{center}
+\end{figure}
 So we can say that in Linux Kernel development developers work in more unfamiliar files during the release period.
-Before the release period main development works are accepted from different branches and they get merged together with main kernel, so, core feature developers finishes their duty for a particular feature development for a particular release within the time of development period although some contributors still work during the release period where basically they work on fixing, testing and minor enhancement related work on the codes that have been merged and accepted from various developers from other branches.
+Before the release period starts main development works are accepted from different branches and they get merged together with the main kernel thus core feature developers finish their duty for a particular feature development for a particular release within the time of development period although some contributors still work during the release period where basically they work on fixing, testing and minor enhancement related work on the codes that have been merged and accepted from various developers from other branches.
 It is clear now that during the release period developers work mostly on others' works, the proportion of working with owned files is lower around the release than the proportion during normal development time.
@@
 
-So, finally we can say that in development periods developers work in more native codes while during the regular release development period the percentage of working with native code is very low in number although this percentage of working in owned code during development period does not significantly relate to other co-factors.
+So, finally we can say that in development periods developers work in more native codes while during the release development period the percentage of working with native code is very low in number although this percentage of working in owned code during development period does not significantly relate to other co-factors.
 
@@
 The duration a commit was made to the local branch to the date it is pushed into the main branch is being called here ``lag'' of commits.
-Figure 10 represents lag of the commits made for regular development and lag of the commits made during the release period.
+Figure 11 represents lag of the commits made for regular development and lag of the commits made during the release period.
 
@@
 
-From figure 10 we can understand it easily that rather quick fixes are made during the release period.
-With the small sets of bug fixes, important quick enhancements candidate releases are pushed continuously within short period lengths of time and once the kernel seems to be more stable with all the new features that has been merged during the beginning of the release cycle, the stable release is published.
+From figure 10 we can understand that quick fixes are made during the release period.
+With the small sets of bug fixes, important quick enhancements candidate releases are pushed continuously within short lengths of time and once the kernel seems to be more stable with all the new features that has been merged during the beginning of the release cycle, the stable release is published.
 Comperatively lag for the feature development commits is quite high.
-Median for the lags for the commits during this time is 5.57 while median of the lags for the commits going to the main kernel of the development  period is 26.15, which is a significant different between these two parts of a release cycle.
+Median for the lags for the commits during this time is 5.57 while median of the lags for the commits going to the main kernel of the development  period is 26.15, which is a significant difference between these two parts of a release cycle.
 
@@
 Median and mean values are closer enough (2668 and 3077) to say that almost similar kind of churns are made in all the release periods except couple of exceptions.
-If we look at figure 11 then where the normalized distribution of this data is represented then we can easily understand.
+If we look at figure 12 where the normalized distribution of this data is represented then we can easily understand this.
 \begin{figure}
@@
 
-We analyzed in several releases and found that for the release ``linuxv2.6.13'' 2938 files got churned.
+We analyzed several release cycles and found that during the release period of ``linuxv2.6.13'' 2938 files got churned.
 Among them only five files had exceptionally high number of churns four of them have more than 10,000 churns.
+Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high.
+For almost every release cycle during the release period around 2.846 files get highly increased attention having over 5000 churns and 16.78 files having over 1000 churns as shown in figure 13.
 Similar picture we see for other releases also.
-Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high and being marked as outliers as shown in figure 12.
-For almost every release cycle during the release period around 2.846 files get highly increased attention having over 5000 churns and 16.78 files having over 1000 churns as shown in figure 13.
+But, if some one renames a file containing thousands of lines of codes and then just commits it then we will see the churn is as many lines as the file contains.
+In Linux Kernel development, the code files related to device drivers are just copied or renamed because these files are mainly reused or just the license informations added.
+In this case they usually get committed once or twice.
+As we see in tha data throught all the releases there are 621 instances where a file has got more than a thousand churns and 466 of them have less than 5 commits and most of those files are for different kinds of device configuration or drivers related files.
+So, to calculate highly focused files we are considering number of commits instead of churns.
+We think at least this will make sense that how many times developers are getting involved to a file around the time of release which describes the focus more than churns.
+
+For each stable releases, number of files having more than 10 commits during the release period can be plotted as we see in figure 14.
+In an average 12.92 files get more than 10 commits around every release period although during few release periods we have seen around 35 even 50 files got commits more than 10 times.
+
 \begin{figure}
@@
 \begin{center}
-\includegraphics[height=1.7in,width=3in]{fileChurnRPExp1000vs5000box.png}
-\caption{\small \sl Files churned more than 1000 times and more than 5000 times during release period}
+\includegraphics[height=1.7in,width=3in]{file_commit_exeptional_rp10box.png}
+\caption{\small \sl Files committed more than 10 times during release period}
 \end{center}
@@
 
-So, we can say that there are certain areas of the system that takes certainly increased attention also there are few developers who deal with extremely large number of files at the time of release.
+So, we can say that there are certain areas of the system that takes certainly increased attention also there are few developers who deal with large number of files at the time of release.
 Some of them work less than 40\% files that they own and some developers work around 70\% of files that they own.
@@
 This finding also supports our fourth research question \textit{RQ4} strongly.
-In this occasion we would like find the Jaccard similarity index for these areas in consecutive releases.
-First we collected the sets of files those are having highly increasing focus during the release periods of different release cycles.
-Then we calculated the union and intersection operation between two consecutive sets as well as randomly.
-We applied equation 2 to find out the similarity among the sets and we see there is no similarity between those sets except for couple of pairs of releases like linuxv2.6.14~linuxv2.6.15, linuxv2.6.29~linuxv2.6.30, linuxv2.6.30~linuxv2.6.31 and linuxv2.6.34~linuxv2.6.35 where the similarity index is too low to say similar; they are 0.038, 0.066, 0.025 and 0.181 respectively as shown in figure 14.
-From this we understand that developers working for different and various features, developing new staffs for Linux kernel working in many different files and merging them into the main kernel during merge window.
-In release period small number of developers who are allowed to work in release period are reviewing those newly arrived codes and doing quick fixes and enhancements, some of them may require very high attention and more work to do.
-In the next release some other different new developments arrive in merge window and thus in release period developer do their candidate releases focusing on those newly arrived code files which are not related to the code files those had to get high focus in the previous release.
+In this occasion we would like to find the Jaccard similarity index for these highly focused areas in between two consecutive releases.
+First we collected the sets of files those are having highly increasing churns during the release periods of different release cycles and also the sets of files that are getting high number of commits.
+Then we calculated the union and intersection operation between two sets for two consecutive releases.
+We applied equation 2 to find out the similarity among the sets.
+For the sets we collected based on churns, we don't see any similarity between them except for couple of pairs of releases where the Jaccard indexes are 0.038, 0.066, 0.025 and 0.181 respectively as shown in figure 15.
 
@@
 \begin{center}
-\includegraphics[height=1.7in,width=3.4in]{jdRPHighFocusFiles.png}
-\caption{\small \sl Jaccard similarity index between consecutive sets of files having highly increased focus in different releases}
+\includegraphics[height=1.7in,width=3.4in]{jdRPChurnHighFocusFiles.png}
+\caption{\small \sl Jaccard similarity index between consecutive sets of files having highly increased focus (based on churns) in different releases}
 \end{center}
+\end{figure}
 
+But for the sets of code files we collected based on commits, we see positive Jaccard indexes for all consecutive release pairs which means some of the files those are receiving increased focus during the release period also receives highly increased focus in the later releases too.
+Figure 16 is representing this behavior.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=1.7in,width=3.4in]{jdRPCommitHighFocusFiles.png}
+\caption{\small \sl Jaccard similarity index between consecutive sets of files receiving highly increased focus (based on commits) in different releases}
+\end{center}
 \end{figure}
+
+After all these results we can say that developers working for different and various features, developing new staffs for Linux kernel working in many different files and merging them into the main kernel during merge window.
+In release period small number of developers who are allowed to work in release period are reviewing those newly merged codes and doing quick fixes and enhancements.
+Some of them may require very high attention and more work to do.
+In the next release more different and new developments arrive in merge window and thus in release period developer keep pushing their candidate releases focusing on those newly arrived code files where there may have some files require more focus may be they received high focus in the previous release too.
+
 \section{Threats to Validity}
-Throught the paper we have done number of measurements to analyze the structure of an OSS software project development, behavior of the developers in different parts of the system, allocation and re-allocation of resources around the time of release and around the time of development.
-The results have been reported with respect to our research questions in this case study.
-We reported following items by our measurements:
-\renewcommand{\labelenumi}{\theenumi.}
-\begin{enumerate}
-\item{The basic structure and the development process of Linux Kernel.}
-\item{The distribution of developers in two different segments in a complete release cycle.}
-\item{Role of developers during development period and the significance of release period.}
-\item{Developers' focus around the time of release, percentage of working with native code during development period and release period.}
-\end{enumerate}
-Now, are these measurements and findings really meaningful, are they quantifying what we want them to?\newline\newline
+Throught the paper we have done number of measurements to analyze the structure of an OSS software project development, behavior of the developers in different parts of the system, allocation and re-allocation of resources around the time of release as well as around the time of development.
+Now, are these measurements and findings really meaningful?
+Are they quantifying what we want them to?\newline\newline
 \textbf{Construct Validity} To study the distribution and allocation of developers or resources around the development system for a large project, the very initial step should be understanding the project development strategy which project data we are studying on.
@@
 Our second research question tells us every details on these and our third, fourth and fifth research questions take us more into the deep of this analysis to discover some core points of information from where we may start thinking of something different that may help us to progress our work farther more by setting any goal based on new hypothesis to come up with any decision.
-Our last research question is really giving us some meaningful discoveries to plot the critical true scenario of developers with code-base of a project.\newline\newline
+Our last research question is really giving us some meaningful discoveries to plot the critical true scenario of developers with code-base of a software project.\newline\newline
 \textbf{Internal Validity} Is there any cause and effect relation between the changes in certain attributes and the results that we represented?
@@
 The first attribute ``versions'' may vary with many other software projects so the data extraction model that we have used may not me similar to other projects but the GDT algorithm that we have used for acqumulating the commits associated to releases will be useful for other software projects having Git as the version control system.\newline\newline
-\textbf{External Validity} As our aim is to understand the allocation and re-allocations of the resources around the release of a software project we wanted to make a study with a large project and so we started our study with Linux Kernel development where we got approximately 400441 commit records made by thousands of developers for 340 releases (including stable and candidates).
+\textbf{External Validity} We wanted to understand the allocation and re-allocations of the resources around the release of a software project we wanted to make a study with a large project and so we started our study with Linux Kernel development where we got approximately 400441 commit records made by thousands of developers for 340 releases (including stable and candidates).
 Can we generalize our results to other software projects?
@@
 We need to analyze the development strategy and distribution of resources for others software projects also.
-We have plan to go for similar kind of analysis on other historical projects both OSS and non-OSS to generalize our findings and results by cross-validation across projects.\newline\newline
+We have plan to go for similar kind of analysis on other historical projects both OSS and non-OSS to generalize our findings and results by cross-validation across projects.
+We believe that the process we used for finding commits associated to a release tag (GDT Algorithm) will be re-usable for other projects using DVC.\newline\newline
 \textbf{Reliability} The data we used for our study is highly reliable.
@@
 Resource re-allocation is an important phenomenon in regard of software development especially in a large development environment.
-We were aiming to find out some points of crucial information that may lead us to move forward to come up with any new hypothesis or any decision about the rush period of release and the distribution of developers having in-equal hold on the code-base of the system which is strongly related to the disruptive events occur in software development industries.
-We also were concerned about the dead areas of the system that often creates technical debts and we could see in our results that files having highly focus around the release periods are being handled by developers who may have high percentage of familiarity with them or may have pretty low but we did not find those files to be worked on in further releases.
-This may be due to those codes files are developed in such a way that they never require any fix or any new feature cannot be implemented based on them or new developers have no idea about those files which makes them not to touch those files rather make them interested to create new files for new works.
+The results have been reported with respect to our research questions in this case study.
+We want to mention as a summary the following items have been reported by our measurements:
+\renewcommand{\labelenumi}{\theenumi.}
+\begin{enumerate}
+\item{The basic structure and the development process of Linux Kernel.}
+\item{The distribution of developers in two different segments in a complete release cycle.}
+\item{Role of developers during development period and the significance of release period.}
+\item{Developers' focus around the time of release, percentage of working with native code during development period and release period.}
+\end{enumerate}
+We intended to find out some points of crucial information that may lead us to move forward to come up with any new hypothesis or any decision about the rush period of release and the distribution of developers having in-equal hold on the code-base of the system which is strongly related to the disruptive events occur in software development industries.
+We have discovered a lot of information with good potentials to progress our research furhter more.
+We also were concerned about the developers' highly increased focus in code areas of the system that may create technical debts and we could see in our results that files having highly focus around the release periods are being handled by developers who may have high percentage of familiarity with them or may not also some of these files accepts increasing attention in the later releases too.
+Calculating the developers' focus on code area during the release period has been more meaningful as we are doing it based on commits instead of high number of churns because during this period high number of churns are made mostly due to the cloning of existing device/drivers configuration codes or due to very minor changes like signature or license statement change.
 We would like to investigate these matters in future to come up with more significant discoveries possibly with new decisional ideas about the disruptive events of software systems.
-
-%\end{document}  % This is where a 'short' article might terminate
 

### 2013-12-10 images/cumulFileOwnP.r

@@ -1,14 +1,0 @@
-relDCOP <- read.table("~/Documents/git/rupak/scripts/reports/cumul_churn_ownp.rpt",sep="|",header=T)
-
-plot(relDCOP$d_mp, relDCOP$f_mp, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of developers", ylab="")
-lines(relDCOP$d_mp, relDCOP$ownp_mp, type="l", lwd=1.5, lty=2, col="orange")
-lines(relDCOP$d_mp, relDCOP$f_rp, type="l", lwd=1.5, lty=3, col="blue")
-lines(relDCOP$d_mp, relDCOP$ownp_rp, type="l", lwd=1.5, lty=4, col="green")
-
-legend("bottomright", lty=c(1,2,3,4), col = c("red","orange","green","blue"), legend = c("files MP","ownership MP","files RP","ownership RP"))
-
--------
-plot(relDCOP$f_mp, relDCOP$ownp_mp, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of files", ylab="")
-lines(relDCOP$f_mp, relDCOP$ownp_rp, type="l", lwd=1.5, lty=2, col="orange")
-
-legend("bottomright", lty=c(1,2), col = c("red","orange"), legend = c("ownership MP","ownership RP"))

### 2013-12-10 images/devsMPRP.r

@@ -1,5 +1,0 @@
-plot(devsMPRP$devs_mp,type="b",lwd=2,xaxt="n",ylim=c(0,20000),col="black",xlab="release",ylab="developers",main="developers during merge period and release periods for releases")
-axis(1,at=1:length(devsMPRP$release),labels=devsMPRP$release)
-lines(devsMPRP$devs_rp,col="red",type="b",lwd=2)
-
-legend("topright",legend=c("Devs in MP","Devs in RP"),lty=1,lwd=2,pch=21,col=c("black","red"),ncol=2,bty="n",cex=0.8,text.col=c("black","red"),inset=0.01)

### 2013-12-10 lectures/l7/r_import_model.r

@@ -1,0 +1,14 @@
+
+fi <- read.table('~/Dropbox/tmp/file_info.in', sep = '|', header= T)
+
+summary(fi)
+
+cor(fi, method = 'spearman')
+cor.text(commits, authors, method='spearman')
+cor.test(time, authors, method='spearman')
+plot(fi)
+
+
+m <- lm(authors ~ commits + time, data = fi)
+summary(m)
+plot(m)

### 2013-12-10 paper1/images/cumulFileOwnP.r

@@ -1,0 +1,13 @@
+cumulOP <- read.table("~/Documents/git/rupak/scripts/reports/rq34/cumul_churn_ownp.rpt",sep="|",header=T)
+
+plot(cumulOP$d_mp, relDCOP$f_mp, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of developers", ylab="")
+lines(cumulOP$d_mp, relDCOP$ownp_mp, type="l", lwd=1.5, lty=2, col="orange")
+lines(cumulOP$d_mp, relDCOP$f_rp, type="l", lwd=1.5, lty=3, col="blue")
+lines(cumulOP$d_mp, relDCOP$ownp_rp, type="l", lwd=1.5, lty=4, col="green")
+
+legend("bottomright", lty=c(1,2,3,4), col = c("red","orange","green","blue"), legend = c("% files DP","% ownership DP","files RP","ownership RP"))
+
+-------
+plot(cumulOP$d_mp, cumulOP$ownp_mp, type="l", lwd=1.5, lty=1, col="red",xlab="Cumulative number of Developers", ylab="")
+lines(cumulOP$d_mp, cumulOP$ownp_rp, type="l", lwd=1.5, lty=2, col="orange")
+legend("bottomright", lty=c(1,2), col = c("red","orange"), legend = c("% ownership DP","% ownership RP"))

### 2013-12-10 paper1/images/devsMPRP.r

@@ -1,0 +1,5 @@
+plot(devsMPRP$devs_mp,type="b",lwd=2,xaxt="n",ylim=c(0,20000),col="black",xlab="release",ylab="developers",main="")
+axis(1,at=1:length(devsMPRP$release),labels=devsMPRP$release)
+lines(devsMPRP$devs_rp,col="red",type="b",lwd=2)
+
+legend("topright",legend=c("Devs in DP","Devs in RP"),lty=1,lwd=2,pch=21,col=c("black","red"),ncol=2,bty="n",cex=0.8,text.col=c("black","red"),inset=0.01)

### 2013-12-10 paper1/images/j_dev_MPMP.r

@@ -1,0 +1,5 @@
+jDevMPMP<-read.table("~/Documents/git/rupak/scripts/reports/rq34/j_dev_mpmp.rpt",sep="|",header=T)
+jDevRPRP<-read.table("~/Documents/git/rupak/scripts/reports/rq34/j_dev_rprp.rpt",sep="|",header=T)
+
+plot(jDevMPMP$release_pair, jDevMPMP$j_index, type="b", lwd=1.5, lty=1, col="red",xlab="release pairs", ylab="")
+lines(jDevMPMP$release_pair, jDevRPRP$j_index, type="b", lwd=1.5, lty=2, col="blue")

### 2013-12-10 paper1/images/j_file_MPMPvRPRP.r

@@ -1,0 +1,6 @@
+jFileMPMP<-read.table("~/Documents/git/rupak/scripts/reports/rq34/j_file_mpmp.rpt",sep="|",header=T)
+jFileRPRP<-read.table("~/Documents/git/rupak/scripts/reports/rq34/j_file_rprp.rpt",sep="|",header=T)
+
+plot(jFileMPMP$release_pair, jFileMPMP$j_index, ylim=c(0,0.40), type="b", lwd=1.5, lty=1, col="red",xlab="release pairs", ylab="")
+lines(jFileMPMP$release_pair, jFileRPRP$j_index, type="b", lwd=1.5, lty=2, col="blue")
+legend("topright", lty=c(1,2), col = c("red","blue"), legend = c("J index for DP","J index for RP"))

### 2013-12-10 paper1/images/jdRPHighFocusFiles.r

@@ -1,0 +1,2 @@
+fcmExRP<-read.table("~/Documents/git/rupak/scripts/reports/rq6/jd_rd_high_files.rpt",sep="|",header=T)
+plot(fcmExRP)

### 2013-12-10 paper1/latex/file_commit_exeptional_rp10box.r

@@ -1,0 +1,2 @@
+boxplot(fCommitEx10$counts,xlab="files having more than 10 commits in a Release Period")
+fCommitEx10<-read.table("~/Documents/git/rupak/scripts/reports/rq6/file_commit_exeptional_rp10.rpt",sep="|",header=T)

### 2013-12-10 paper1/scripts/reports/rq34/cumul_churn_ownp.r

@@ -1,0 +1,15268 @@
+  ownp  
+   0.00
+ 100.00
+   0.00
+  25.00
+  52.00
+  40.00
+  31.00
+  50.00
+   0.00
+   0.00
+  14.00
+   0.00
+  50.00
+   0.00
+   0.00
+   0.00
+ 100.00
+  80.00
+   0.00
+   0.00
+   0.00
+  33.00
+  50.00
+  90.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+ 100.00
+  15.00
+   0.00
+   7.00
+   0.00
+   0.00
+  38.00
+   0.00
+  50.00
+  33.00
+   0.00
+  27.00
+ 100.00
+  55.00
+   0.00
+   0.00
+   0.00
+   0.00
+  46.00
+   0.00
+   0.00
+  33.00
+  43.00
+  53.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+ 100.00
+   9.00
+  24.00
+   0.00
+   5.00
+   0.00
+   0.00
+  42.00
+  50.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+  33.00
+  25.00
+  37.00
+   0.00
+   0.00
+   0.00
+   0.00
+   0.00
+   9.00
+   0.00
+   0.00
+   0.00
+  33.00
+   0.00
+   0.00
+  33.00
+  17.00
+  83.00
+   0.00
+   0.00
+  24.00
+  42.00
+   0.00
+  23.00
+ 100.00
+ 100.00
+  28.00
+   0.00
+  41.00
+  35.00
+   0.00
+  50.00
+   0.00
+   5.00
+  33.00
+   7.00
+ 100.00
+   0.00
+  24.00
+   0.00
+  48.00
+   0.00
+   0.00
+ 100.00
+ 100.00
+   0.00
+   0.00
+ 100.00
+ 100.00
+  27.00
+   0.00
+   0.00
+   0.00
+  62.00
+   0.00
+  33.00
+  50.00
+  57.00
+   0.00
+   0.00
+   0.00
+   0.00
+  40.00
+   0.00
+  22.00
+   0.00
+   0.00
+   0.00
+ 100.00
+   0.00
+  60.00
+ 100.00
+  27.00
+   0.00
+  19.00
+   0.00
[…]

### 2013-12-10 paper1/scripts/reports/rq34/j_dev_mpmp.pl

@@ -1,0 +1,48 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select release from stable_releases
+});
+my $j = $dbh_ref->prepare(q{
+	select
+		cast(p as numeric)/cast(t as numeric) as j
+	from
+		(select count(*) p from (select distinct author from dev_area_merge where release=? intersect select distinct author from dev_area_merge where release=?) b) x1,
+		(select count(*) t from (select distinct author from dev_area_merge where release=? union select distinct author from dev_area_merge where release=?) c) x2;
+});
+$get_releases->execute() or die;
+
+print "jaccard similarity between devs in two consicutive merge periods:\n";
+my $i=0;
+my ($prev_rel) = $get_releases->fetchrow_array;
+while(my($rel) = $get_releases->fetchrow_array){
+	$j->execute($prev_rel,$rel,$prev_rel,$rel);
+	my $jac = $j->fetchrow_array;
+	print "$i | $jac\n";
+	$prev_rel = $rel;
+
+	$i++;
+}
+
+$get_releases->finish;
+$j->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-12-10 paper1/scripts/reports/rq34/j_dev_rprp.pl

@@ -1,0 +1,47 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select release from stable_releases
+});
+my $j = $dbh_ref->prepare(q{
+	select
+		cast(p as numeric)/cast(t as numeric) as j
+	from
+		(select count(*) p from (select distinct author from dev_area_dev where release=? intersect select distinct author from dev_area_dev where release=?) b) x1,
+		(select count(*) t from (select distinct author from dev_area_dev where release=? union select distinct author from dev_area_dev where release=?) c) x2;
+});
+$get_releases->execute() or die;
+
+print "jaccard similarity between devs in two consicutive release periods:\n";
+my $i=0;
+my ($prev_rel) = $get_releases->fetchrow_array;
+while(my($rel) = $get_releases->fetchrow_array){
+	$j->execute($prev_rel,$rel,$prev_rel,$rel);
+	my $jac = $j->fetchrow_array;
+	print "$i | $jac\n";
+	$prev_rel = $rel;
+	$i++;
+}
+
+$get_releases->finish;
+$j->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-12-10 paper1/scripts/reports/rq34/j_file_mpmp.pl

@@ -1,0 +1,48 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select release from stable_releases
+});
+my $j = $dbh_ref->prepare(q{
+	select
+		cast(p as numeric)/cast(t as numeric) as j
+	from
+		(select count(*) p from (select distinct path from dev_area_merge where release=? intersect select distinct path from dev_area_merge where release=?) b) x1,
+		(select count(*) t from (select distinct path from dev_area_merge where release=? union select distinct path from dev_area_merge where release=?) c) x2;
+});
+$get_releases->execute() or die;
+
+print "jaccard similarity between files in two consicutive merge periods:\n";
+my $i=0;
+my ($prev_rel) = $get_releases->fetchrow_array;
+while(my($rel) = $get_releases->fetchrow_array){
+	$j->execute($prev_rel,$rel,$prev_rel,$rel);
+	my $jac = $j->fetchrow_array;
+	print "$i | $jac\n";
+	$prev_rel = $rel;
+
+	$i++;
+}
+
+$get_releases->finish;
+$j->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-12-10 paper1/scripts/reports/rq34/j_file_rprp.pl

@@ -1,0 +1,48 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 1});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select release from stable_releases
+});
+my $j = $dbh_ref->prepare(q{
+	select
+		cast(p as numeric)/cast(t as numeric) as j
+	from
+		(select count(*) p from (select distinct path from dev_area_dev where release=? intersect select distinct path from dev_area_dev where release=?) b) x1,
+		(select count(*) t from (select distinct path from dev_area_dev where release=? union select distinct path from dev_area_dev where release=?) c) x2;
+});
+$get_releases->execute() or die;
+
+print "jaccard similarity between files in two consicutive release periods:\n";
+my $i=0;
+my ($prev_rel) = $get_releases->fetchrow_array;
+while(my($rel) = $get_releases->fetchrow_array){
+	$j->execute($prev_rel,$rel,$prev_rel,$rel);
+	my $jac = $j->fetchrow_array;
+	print "$i | $jac\n";
+	$prev_rel = $rel;
+
+	$i++;
+}
+
+$get_releases->finish;
+$j->finish;
+$dbh_ref->disconnect;
+
+__END__

### 2013-12-10 paper1/scripts/reports/rq6/jd_rd_high_files.pl

@@ -1,0 +1,77 @@
+#!/usr/bin/perl -w
+
+use warnings;
+use strict;
+
+use DBI;
+use Config::General;
+
+my $config_path = shift @ARGV;
+
+if (!defined $config_path) {
+	$config_path = 'config';
+}
+die "Config file \'$config_path\' does not exist" unless (-e $config_path);
+
+my %config =  Config::General::ParseConfig($config_path);
+
+my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 0});
+
+my ($prev_release, $release);
+
+#************* Calculate Jaccard Distance Between Merge Period and Development Period *******#
+#****************************** For ALl Releases ********************************************#
+my $union = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select path from (select path, sum(commits) as t_commit from dev_area_dev where release=? group by path) a where t_commit > 10
+		UNION
+		select path from (select path, sum(commits) as t_commit from dev_area_dev where release=? group by path) a where t_commit > 10
+	) as e
+});
+my $intersection = $dbh_ref->prepare(q{
+	select count(*)
+	from (
+		select path from (select path, sum(commits) as t_commit from dev_area_dev where release=? group by path) a where t_commit > 10
+		INTERSECT
+		select path from (select path, sum(commits) as t_commit from dev_area_dev where release=? group by path) a where t_commit > 10
+	) as f
+});
+
+my $get_releases = $dbh_ref->prepare(q{
+	select release from stable_releases;
+});
+
+$get_releases->execute or die;
+($prev_release) = $get_releases->fetchrow_array;
+my $i=0;
+print "release_pair | Jaccard_index\n";
+while (($release) = $get_releases->fetchrow_array) {
+	my $jac = 0;
+	if(not $prev_release eq $release){
+
+		$union->execute($prev_release, $release) or die;
+		my $aub = $union->fetchrow_array;
+
+		$intersection->execute($prev_release, $release) or die;
+		my $anb = $intersection->fetchrow_array;
+		
+		if($aub > 0){
+			$jac = $anb / $aub;
+			print "$i | $jac\n";
+		}else{
+			print "a u b is <= 0\n";
+		}
+	}
+	$prev_release = $release;
+	$i++;
+}
+
+$union->finish;
+$intersection->finish;
+$get_releases->finish;
+$dbh_ref->commit;
+$dbh_ref->disconnect;
+
+__END__
+

### 2013-12-10 scripts/reports/rq34/cumul_churn_ownp.r

@@ -1,15269 +1,0 @@
-  ownp  
-   0.00
- 100.00
-   0.00
-  25.00
-  52.00
-  40.00
-  31.00
-  50.00
-   0.00
-   0.00
-  14.00
-   0.00
-  50.00
-   0.00
-   0.00
-   0.00
- 100.00
-  80.00
-   0.00
-   0.00
-   0.00
-  33.00
-  50.00
-  90.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
- 100.00
-  15.00
-   0.00
-   7.00
-   0.00
-   0.00
-  38.00
-   0.00
-  50.00
-  33.00
-   0.00
-  27.00
- 100.00
-  55.00
-   0.00
-   0.00
-   0.00
-   0.00
-  46.00
-   0.00
-   0.00
-  33.00
-  43.00
-  53.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
- 100.00
-   9.00
-  24.00
-   0.00
-   5.00
-   0.00
-   0.00
-  42.00
-  50.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-  33.00
-  25.00
-  37.00
-   0.00
-   0.00
-   0.00
-   0.00
-   0.00
-   9.00
-   0.00
-   0.00
-   0.00
-  33.00
-   0.00
-   0.00
-  33.00
-  17.00
-  83.00
-   0.00
-   0.00
-  24.00
-  42.00
-   0.00
-  23.00
- 100.00
- 100.00
-  28.00
-   0.00
-  41.00
-  35.00
-   0.00
-  50.00
-   0.00
-   5.00
-  33.00
-   7.00
- 100.00
-   0.00
-  24.00
-   0.00
-  48.00
-   0.00
-   0.00
- 100.00
- 100.00
-   0.00
-   0.00
- 100.00
- 100.00
-  27.00
-   0.00
-   0.00
-   0.00
-  62.00
-   0.00
-  33.00
-  50.00
-  57.00
-   0.00
-   0.00
-   0.00
-   0.00
-  40.00
-   0.00
-  22.00
-   0.00
-   0.00
-   0.00
- 100.00
-   0.00
-  60.00
- 100.00
-  27.00
-   0.00
-  19.00
-   0.00
-   0.00
-   0.00
-   0.00
-  37.00
[…]

### 2013-12-10 scripts/reports/rq6/jd_rd_high_files.pl

@@ -1,77 +1,0 @@
-#!/usr/bin/perl -w
-
-use warnings;
-use strict;
-
-use DBI;
-use Config::General;
-
-my $config_path = shift @ARGV;
-
-if (!defined $config_path) {
-	$config_path = 'config';
-}
-die "Config file \'$config_path\' does not exist" unless (-e $config_path);
-
-my %config =  Config::General::ParseConfig($config_path);
-
-my $dbh_ref = DBI->connect("dbi:Pg:database=$config{db_name}", '', '', {AutoCommit => 0});
-
-my ($prev_release, $release);
-
-#************* Calculate Jaccard Distance Between Merge Period and Development Period *******#
-#****************************** For ALl Releases ********************************************#
-my $union = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
-		UNION
-		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
-	) as e
-});
-my $intersection = $dbh_ref->prepare(q{
-	select count(*)
-	from (
-		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
-		INTERSECT
-		select path from (select path, sum(churn) as t_churn from dev_area_dev where release=? group by path) a where t_churn > 1000
-	) as f
-});
-
-my $get_releases = $dbh_ref->prepare(q{
-	select release from stable_releases;
-});
-
-$get_releases->execute or die;
-($prev_release) = $get_releases->fetchrow_array;
-my $i=0;
-print "release_pair | Jaccard_index\n";
-while (($release) = $get_releases->fetchrow_array) {
-	my $jac = 0;
-	if(not $prev_release eq $release){
-
-		$union->execute($prev_release, $release) or die;
-		my $aub = $union->fetchrow_array;
-
-		$intersection->execute($prev_release, $release) or die;
-		my $anb = $intersection->fetchrow_array;
-		
-		if($aub > 0){
-			$jac = $anb / $aub;
-			print "$prev_release~$release | $jac\n";
-		}else{
-			print "a u b is <= 0\n";
-		}
-	}
-	$prev_release = $release;
-	$i++;
-}
-
-$union->finish;
-$intersection->finish;
-$get_releases->finish;
-$dbh_ref->commit;
-$dbh_ref->disconnect;
-
-__END__
-

### 2013-12-12 paper1/latex/paper1.tex
updated paper, updated presentation slide

@@
 \terms{Experiment, Human Factors, Resource Management, Reallocation}
-\keywords{Resource Reallocation, Code Ownership, Defect Density, Software Releases} % NOT required for Proceedings
+\keywords{Resource Reallocation, Code Ownership, Software Releases} % NOT required for Proceedings
 \section{Introduction}
@@
 Regardless of the causes, the rush to release stresses developers and often requires developers to work on unusual, high priority or critical areas of the system.
-In this paper we study how RTR may effect project organization and introduce technical debt.
+In this paper we study how RTR may effect project organization to introduce technical debt.
 We want to propose a method to observe, analyze and summarize the results found around different parts of a release cycle.
@@
 
-During the merge window, developers are free to provide any change that is ready for release.
-During the release candidate period, we would expect to see fixes on the files that were changed during the previous merge window.
-We measure this by comparing the Jaccard distance of merge window with the subsequent rc period, compared with the merge window and subsequent merge window.
-
-We observe the developers' working areas to understand the allocation of the resources within an open source software development project to understand the reallocation or distribution takes place in a software development process which may cause disruptive events.
-We attempt to identify the project's different release times and calculate the difference between different development periods within a releases cycle to identify which new areas are being worked on and what is the behavior of the developers between normal development period and the period when RTR is prompted.
-The historical data from git that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release as well as different parts in a stable release cycle.
-This information will help us to identify the criteria of the resources, their roles and behaviors, code ownerships of the domains they are working in, density of work, nature of dealing with files around the time of release etc.
+During the development period, developers are free to make any change that might go for release.
+Around the time of release, we generally would expect fixes on the code files those have been worked on during the development.
+In this study we observe the developers' working areas to understand their allocation and contribution within an open source software development project to understand the development process, nature of reallocation of resources or (i.e.\ developers), change in work strategy during different period of a release cycle especially during the time of release, developers' focus on the code-base in a large software project which may cause disruptive events.
+The historical data that we have worked on for this purpose will help us to extract a lot of information that will help us to understand the role of the developers, code ownerships of the domains they are working in, density of work, nature of dealing with files dealing around the time of release etc.
 
 We have organized this paper as follows.
-In Section 2, we describe some background and motivations followed by the summaries of related works in Section 3.
+In section 2, we describe some background and motivations followed by the summaries of related works in section 3.
 Section 4 will describe methodology of our work and explanation of the data we are working with for this research.
@@
 \subsection{Research Questions}
-We have set our research questions focusing the key properties of software development process, allocation of developers throughout the process, especially for open source software development.
-First couple of research questions are to understand the basic structure and strategies of the development and release and merging process practiced by Linux Kernel development team.
-Rest of the questions are to understand the distribution of developers' working areas and the behavior of developers in different segments of a release cycle.
+We have set our research questions focusing the key properties of software development process, allocation of developers throughout the development and release, especially for open source software development.
+First couple of research questions are to understand the basic structure and strategies of the development and release and merging process practiced by Linux Kernel developers.
+Rest of the questions are to understand the distribution of developers', working areas and the behavior of developers during different segments of a release cycle.
 
@@
 This can be useful for any other data collected from distributed version control system like git.
-We are expecting this would be the RTR in a release cycle which may introduce technical debts.
 \item Do developers work in others' code in a high proportion during the rush period?\newline
@@
 We will try to find out what is the percentage of dealing with files that developers own or they are most familiar to.
-This will give us a sense of the nature of work during release time.
-\item How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?\newline
+This will give us a sense of the nature of work during the release time.
+\item How long a commit takes to get pushed into the master branch? Does it differ in different periods of release?\newline
 In distributed development environment developers work in different branches.
@@
 We would like to see how much time it takes for a commit to the local branch to get pushed to the main branch.
-We also should understand how long it takes for regular development commits and how long it takes for the commits made around the release period.
+We also compare between how long it takes for regular development commits and how long it takes for the commits made during the release period.
 \item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)? \newline
 To answer this question we will look into the files getting churned extremely high in number.
-We will try to figure out the difference between those highly churned or highly focused sets of files in different releases to understand if they require constantly high focus or they are only for one particular release.
+We will try to figure out the difference between those highly churned or highly focused sets of files in different releases to understand if they require constantly high focus or they are for a particular release only.
 \end{enumerate}
@@
 Another example can be placed, if a lead developer who owns an important part of the code-base leaves and if steps to train other developers were not taken, it will become a dead area of the system and will be difficult to modify and maintain.
-Also often management reorganizes the developers on a company's projects during the rush period around the release time, with the result that developers move to code-bases for which they have less experience.
+Also often management reorganizes the developers on a company's projects during the rush period around the release time, as a result that developers move to code areas for which they have less experience.
 The reorganization introduces new perspectives and expertise that can lead to faster release; however, it can also result in a drop in productivity and the unnecessary re-writing of large portions of the system that the new developers do not understand.
-In this paper, we plan to take the measures on this last example among them mentioned above.
+In our study, we plan to take the measures on this last example among all mentioned above.
 
@@
 On the other hand Cook did an interesting job, he inserted sensors and monitors into the development process but Hindle analyzed the data to understand what happened in the past \cite{cook_automating}.
-Basically Hindle worked in a reverse way than Cook did.
+Basically Hindle worked in a reversed way than Cook did.
+
 Another research work we would like to mention was done by  Damian where they have worked on the role of domain knowledge and cross functional communication among the OOS development teams \cite{damian_domain}.
 Posnett did some dual ecological measures of focus in software development \cite{posnett_ecological}.
-Posnett's measure was for the more general view that unifies developer focus and artifact ownership.
-He analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from ehology to produce a novel and iii) conceptually unified view of measuring focus and ownership.
+Posnett's measure was for the more general view that unifies developers' focus and artifact ownership.
+He analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from echology to produce a novel and iii) conceptually unified view of measuring focus and ownership.
 Another study was done by F.
-Rahman about the authorship of the code-bases in OSS development \cite{rahman_ownership}.
+Rahman about the authorship of the code-base in OSS development \cite{rahman_ownership}.
+This is one of the main focuses of our method for this study.
+We have used code ownership to understand the hold of the developers on the system.
+Not only code ownership but we also focused on the percentage of working with owned files during the release time and what is the percentage of working with owned files when developers provide increased attention to the code files around the time of release.
 
@@
 This section presents our methodology for discovering information which can give us the idea to get the answers to our research questions.
-We have collected the development history data of Linux kernel.
+We have collected the development historical data of Linux Kernel.
 It is a data source containing the the historical data of Linux kernel development since 2005.
-We are going to present the steps involved in this process and then we will follow up with an application of our methodology in a case study.
+We are going to present the steps involved in this process and then we will follow up with an application of our methodology as a case study.
 In order to address our research questions, we obtain key measures of project evolution from the archival data collected from the distributed version control (DVC) system of Git where all information of the OSS project ``Linux Kernel Development'' is recorded in electronic form.
-Many other OSS projects archive similar data, so the techniques used here can be replicated on any such project.
-We used the data elements extracted from the archival source to construct a number of measures on the commit log records to understand the behavior of the developers.
+Many other OSS projects archive similar data, so the techniques being used by us can be replicated on other projects as well.
+We used the data elements extracted from the archival source to construct a number of measures on the commit log records to understand the distribution and behavior of the developers.
 
@@
 \subsection{Data Extraction}
-We collected data from the version control system of a target project and either mirror the repository or download every revision and commit log history data.
+We collected the data downloading every revision and commit log history data.
 From DVCSs such as Git we extract the revisions and release information.
@@
 \subsubsection{Explanation}
-A Linux kernel development release version having maximum length of information does look like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
-If a release version looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release in the series of the 6th major release of kernel version 2.
-``linuxv2.6.13\textbf{-rc1}'' says that after the 12th stable minor release had published, development for the next release has been started and rc1 is the first candidate on the way to the next release.
-It also ensures that next release is going to be another minor release which is ``linuxv2.6.13''.
+A Linux kernel development release version constructed with maximum length of information does look like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
+If a release version looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th micro release in the series of the 6th minor release of kernel version 2.
+``linuxv2.6.13\textbf{-rc1}'' says that after the 12th stable minor release published, development for the next release has been ended all new files are merged and rc1 is the first candidate release that starts working on the next release, basically it starts the release period.
 We have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
-So we are having 340 releases including major, minor, micro and rc; 39 stable releases from ``linuxv2.6.11'' to ``linuxv3.11'' having complete data with us.
+So we are having 340 releases including major, minor, micro and rc.
+39 stable releases from ``linuxv2.6.11'' to ``linuxv3.11'' having complete data with us.
 We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 13926 developers' commit history among 14621 distinct developers.
@@
 We stored the extracted git commit log data into the tables git\_commit and git\_revision where all the basic and detail log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
-By joining these tables we can easily get the dates of each version and from the version number we can determine which commit belongs to which version and release, and also what type of release that is.
+By joining these two tables we can easily get the dates of each release version and from the version number we can determine which commit belongs to which version and release, and also what type of release that is.
 
-Commits those are made for pushing a release have release tags associated to them by which we can understand which commit is made for a release; is this a major release or minor or a micro stable release.
+Commits those are made for pushing a release have release tags associated to them by which makes us understand which commit is made for a release and also if it is a major or minor or a micro stable release.
 Another information we have captured that is \textbf{rc} which indicates that the particular commit was a release candidate.
-These information and splitting off release numbers will help us accumulating commits for different releases.
+These information and splitting off the release numbers will help us accumulating commits associated to different releases.
 
 \subsection{Finding Commits for Releases}
-We have to sorted out and accumulated all the commits together belonging to any of the releases.
+We have sorted out and accumulated all the commits together belonging to any of the releases.
 We have all 400441 commits in our hand but though we can't plot them into a single time domain to assign different set of commits to different release periods because development goes in parallel on different branches in git, so commits also go in parallel.
@@
 
-So it is possible to make a commit months ago from today while several releases may have already been made in the mean time but that commit can belong to any future release.
-Commits that are being made to a branch may get merged with any other branch or the head branch during the merge period.
+It is possible to make a commit months ago while several releases may have already been made in the mean time but that commit can belong to any future release.
+Commits that are being made to a development branch may get merged with the head branch during the merge period.
 This is why we had to track all the way down the trees for each of the 340 releases in the git DAG to find out which commit contributes to which release.
@@
 Another information that we require is what are the durations of the releases of Linux kernel development.
-To achieve that we joined the table ``git\_refs\_tags'' where all the releases are stored including the exploited release numbers and the table ``git\_commit'' to give us all the dates of commits for each and every releases, so that we can easily find out the duration between two consecutive releases (including release candidates ``rc'').
+To achieve that we joined the table ``git\_refs\_tags'' where all the releases are stored including the release numbers and the table ``git\_commit'' to give us all the dates of commits for each and every releases, so that we can easily find out the duration between two consecutive releases (including release candidates ``rc'').
 This information will significantly help us because we need to see what is the development period and what are the release periods within a release cycle.
@@
 From the extraction we found complete records for releases ``linuxv2.6.13'' to ``linuxv2.6.39'' then it is ``linuxv3.0'' to ``linuxv3.11''.
-Our farther works will be proceeded based on these 39 releases only.
+Our farther works will be proceeded based on these 39 stable releases.
 
@@
 We see that authors are committing files almost everyday throughout a release but this does not make sure that these commits are going to the next release because commits are being made in different branches and all branches are not supposed to get merged to the next release.
-Using GDT we have acqumulated all the commits finally went to a particular release.
+Using GDT algorithm we have acqumulated all the commits finally went to a particular release.
 Now it is possible to find out which commits were made for which files by which developer for a release.

### 2013-12-17 msr/latex/paper1.tex
tarted working on reviews from Peter.

--- 2013-12-05 paper1/paper1.tex
@@
 \documentclass{acm_proc_article-sp}
-\usepackage{algorithmic}
-\usepackage{algorithm}
-\usepackage{listings}
-\usepackage{booktabs}
-\usepackage{graphicx}
+
 \begin{document}
-
-\title{On Reallocation of Resources during Releases \titlenote{Pelmission to make digital or hard copies of all or part of this work for
+\title{On Reallocation of Resources during Releases \titlenote{Permission to make digital or hard copies of all or part of this work for
 personal or classrooms use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
@@
 \maketitle
+
 \begin{abstract}
-Software projects often suffer from lesions in our software industries due to disruptive events what may occur naturally or because of managerial directions.
-Keeping this in mind we have taken an approach to examine the development process of a large software project to understand the nature and behavior of the process and distribution of resources within the different areas of the system.
-By using the historical data from the distributed version control (DVC) system used by that large project we quantify aspects of developers' distribution, code ownership, different release periods, focus on the areas of the code-base, percentage of working with owned files during different periods withing a release cycle for this project.
-This study reveals a unique process performing well extraction of data from Git for the releases of such a large project by which we can perceive significant points of information that can lead us to further decisional analysis aiming novel solutions to the disruptive events for the practitioners of software development.
+Different software projects practices different release models to compete in the field of software development.
+From the historical data of a large project we quantify aspects of developers' distribution, code ownership, different release periods, focus on the areas of the code-base, percentage of working with owned files during different periods within a release cycle for this project.
+This study reveals a unique process performing well extraction of data from Git for the development of a large open source project by which we can perceive well understanding on the release process and distribution of developers throughout the release providing us significant points of information that can lead us to further decisional analysis aiming novel solutions to the disruptive events for the practitioners of software development.
+\end{abstract}
 
-\end{abstract}
 \category{K.6.3}{Software Management}{Software Development, Software Resource Management, Resource Reallocation}
 \terms{Experiment, Human Factors, Resource Management, Reallocation}
-\keywords{Resource Reallocation, Code Ownership, Defect Density, Software Releases} % NOT required for Proceedings
-\section{Introduction}
-Software projects are notorious for going over budget and schedule.
-Rush periods are often get seen before a major release that turn the developers into dinosaurs as Frederick Brooks likens in his benchmark study "The Mythical Man Month" \cite{brooks_mythical}.
-This "Rush To Release (RTR)" can be prompted either by external forces such as decisions by management to include new features in the release or to release earlier to beat a competitor.
-Alternatively, the rush may simply be due to inappropriate or unrealistic scheduling.
-Whatever the reason is it is an obvious.
-Regardless of the causes, the rush to release stresses developers and often requires developers to work on unusual, high priority or critical areas of the system.
-In this paper we study how RTR may effect project organization and introduce technical debt.
-We want to propose a method to observe, analyze and summarize the results found around different parts of a release cycle.
-We intend to infer behavior of the developers related to the process around release time.
-The key research questions that we expect to answer with our methodology are described in section 1.1.
+\keywords{Resource Reallocation, Code Ownership, Software Releases} % NOT required for Proceedings
 
-During the merge window, developers are free to provide any change that is ready for release.
-During the release candidate period, we would expect to see fixes on the files that were changed during the previous merge window.
-We measure this by comparing the Jaccard distance of merge window with the subsequent rc period, compared with the merge window and subsequent merge window.
-
-We observe the developers' working areas to understand the allocation of the resources within an open source software development project to understand the reallocation or distribution takes place in a software development process which may cause disruptive events.
-We attempt to identify the project's different release times and calculate the difference between different development periods within a releases cycle to identify which new areas are being worked on and what is the behavior of the developers between normal development period and the period when RTR is prompted.
-The historical data from git that we are working on for this purpose will help us to extract a lot of information like calculating the developers' working areas and time-frame of each release as well as different parts in a stable release cycle.
-This information will help us to identify the criteria of the resources, their roles and behaviors, code ownerships of the domains they are working in, density of work, nature of dealing with files around the time of release etc.
-
-We have organized this paper as follows.
-In Section 2, we describe some background and motivations followed by the summaries of related works in Section 3.
-Section 4 will describe methodology of our work and explanation of the data we are working with for this research.
-In section 5 we will discuss the results of the findings.
-We are describing our limitations and threats to validity in section 6 and finally section 7 will conclude the paper.
-
-\subsection{Research Questions}
-We have set our research questions focusing the key properties of software development process, allocation of developers throughout the process, especially for open source software development.
-First couple of research questions are to understand the basic structure and strategies of the development and release and merging process practiced by Linux Kernel development team.
-Rest of the questions are to understand the distribution of developers' working areas and the behavior of developers in different segments of a release cycle.
-
-\renewcommand{\labelenumi}{RQ\theenumi:}
-\begin{enumerate}
-\item What is the release process used by the project? \newline
-We will be giving a qualitative description of Linux Kernel development in brief to give anser to this question.
-\item How many developers are allocated throughout different segments of a release cycle? What significant difference can be observed between the segments of a release cycle? \newline
-Answer to this question will give us a big picture of Linux Kernel development community as well as the contribution of developers in different parts within a stable release.
-\item Do developers work on different areas of the system around the time of release? \newline
-We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the release period or rc period.
-We are going to introduce an algorithm to traverse through the git DAG to find out commits associated to a particular release.
-This can be useful for any other data collected from distributed version control system like git.
-We are expecting this would be the RTR in a release cycle which may introduce technical debts.
-\item Do developers work in others' code in a high proportion during the rush period?\newline
-Developers work on various files during release period.
-We will try to find out what is the percentage of dealing with files that developers own or they are most familiar to.
-This will give us a sense of the nature of work during release time.
-\item How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?\newline
-In distributed development environment developers work in different branches.
-They commit their codes to the branches they are associated to.
-While core development is going on developers do not directly push their changes to the main branch.
-We would like to see how much time it takes for a commit to the local branch to get pushed to the main branch.
-We also should understand how long it takes for regular development commits and how long it takes for the commits made around the release period.
-\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)? \newline
-To answer this question we will look into the files getting churned extremely high in number.
-We will try to figure out the difference between those highly churned or highly focused sets of files in different releases to understand if they require constantly high focus or they are only for one particular release.
-\end{enumerate}
-
-\section{Background}
-There may have lower developers productivity \cite{cataldo_identification, damian_awareness} which may cause inefficient run in the rush moments in a release period.
-There is a substantial and important body of literature on risk in software engineering.
-Boehm identified the most important risks encountered by software project managers and described successful risk management practices \cite{boehm_software_risk, keil_framework, boehm_agile}.
-Some of the risks identified are related to disruptive events, such as the introduction of a new technology, but most are macro risks associated with running a project, such as developing the wrong functionality.
-General risk mitigation strategies can be difficult to apply to specific disruptive events.
-There may be various kinds of disruptive events for example, as a release approaches; developers take shortcuts that introduces technical debt.
-If it is not repaired, the long term quality of the system will suffer.
-Another example can be placed, if a lead developer who owns an important part of the code-base leaves and if steps to train other developers were not taken, it will become a dead area of the system and will be difficult to modify and maintain.
-Also often management reorganizes the developers on a company's projects during the rush period around the release time, with the result that developers move to code-bases for which they have less experience.
-The reorganization introduces new perspectives and expertise that can lead to faster release; however, it can also result in a drop in productivity and the unnecessary re-writing of large portions of the system that the new developers do not understand.
-In this paper, we plan to take the measures on this last example among them mentioned above.
-
-\section{Related Works}
-Hindle worked on release pattern discovery via partitioning \cite{hindle_release_pattern} to propose an approach to characterize a project's behavior around the time of major and minor releases while we are trying to study the behavior of the development resources around the time of release.
-In this research they proposed a method of observing, analyzing and summarizing the results of metrics of revisions found near releases.
-They have characterized a project's behavior around the time of major and minor releases.
-This is done by partitioning the observed activities like the artifact check-ins around the dates of major and minor releases, then look for reasonable patterns.
-Hindle divided the revisions in each release in 4 different classes, Source Code, Testing, Building, and Documentations.
-On the other hand Cook did an interesting job, he inserted sensors and monitors into the development process but Hindle analyzed the data to understand what happened in the past \cite{cook_automating}.
-Basically Hindle worked in a reverse way than Cook did.
-Another research work we would like to mention was done by  Damian where they have worked on the role of domain knowledge and cross functional communication among the OOS development teams \cite{damian_domain}.
-Posnett did some dual ecological measures of focus in software development \cite{posnett_ecological}.
-Posnett's measure was for the more general view that unifies developer focus and artifact ownership.
-He analyzed i) developer artifact contribution to network to a predator-prey food web ii) drew upon ideas from ehology to produce a novel and iii) conceptually unified view of measuring focus and ownership.
-Another study was done by F.
-Rahman about the authorship of the code-bases in OSS development \cite{rahman_ownership}.
-
-\section{Methodology and Data}
-This section presents our methodology for discovering information which can give us the idea to get the answers to our research questions.
-We have collected the development history data of Linux kernel.
-It is a data source containing the the historical data of Linux kernel development since 2005.
-We are going to present the steps involved in this process and then we will follow up with an application of our methodology in a case study.
-In order to address our research questions, we obtain key measures of project evolution from the archival data collected from the distributed version control (DVC) system of Git where all information of the OSS project ``Linux Kernel Development'' is recorded in electronic form.
-Many other OSS projects archive similar data, so the techniques used here can be replicated on any such project.
-We used the data elements extracted from the archival source to construct a number of measures on the commit log records to understand the behavior of the developers.
-
-Our methodology can be summarized as: Extracting Data for revisions and releases (Section 4.1); Partitioning the release version numbers (Section 4.2); Finding the commits associated to a version of Kernel (Section 4.3); Get time-span between each release (Section 4.4); Calculate developer areas (Section 4.5); Finding code ownership (Section 4.6).
-
-\subsection{Data Extraction}
-We went for the VCS of a target project and either mirror the repository or download every revision and commit log history data.
-From DVCSs such as Git we extract the revisions and release information.
-We wrote Perl scripts to extract date that was further processed to obtain details.
-Manual inspection was used to resolve problems and things like that in cases where all automated techniques failed.
-We then put them into a database.
-We have used PSQL database to create tables in, to store our extracted data.
-These extracted data will be analyzed by us later on.
-Per each revision the information extracted includes the commit id, tree id, author of the revision, date of revision, the name of the revised file, parent and child info for the revision and the detail log information.
-Once extraction is completed we are ready to partition the version numbers (Section 4.3) and duration  of each release (Section 4.4).
-
-\subsubsection{Explanation}
-A Linux kernel development release version having maximum length of information does look like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric.
-If a release version looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release in the series of the 6th major release of kernel version 2.
-``linuxv2.6.13\textbf{-rc1}'' says that after the 12th stable minor release had published, development for the next release has been started and rc1 is the first candidate on the way to the next release.
-It also ensures that next release is going to be another minor release which is ``linuxv2.6.13''.
-We have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation.
-So we are having 340 releases including major, minor, micro and rc; 39 stable releases from ``linuxv2.6.11'' to ``linuxv3.11'' having complete data with us.
-We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 13926 developers' commit history among 14621 distinct developers.
-Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once.
-So we found them in our released wise datasets.
-
- \subsection{Partitioning Release Numbers}
-We stored the extracted git commit log data into the tables git\_commit and git\_revision where all the basic and detail log information for a particular commit was mentioned in the first table and second one containing which commit belongs to which version of Linux kernel development and change details like path modified, new path created due to the change, how many addition and how many deletion occurred in a particular commit etc.
-By joining these tables we can easily get the dates of each version and from the version number which is a combination of different types of releases we can determine which commit belongs to which version and release, and also what type of release that is.
-
-Commits those are made for pushing a release have release tags associated to them by which we can understand which commit belongs to which version of release; is this a major release or minor or a micro stable release.
-Another information we have captured that is \textbf{rc} which indicates that the particular commit was a release candidate.
-These information and splitting off release numbers will help us accumulating commits for different releases.
-
-\subsection{Finding Commits for Releases}
-We have to sort out and accumulate all the commits together those are belonging to any of the releases.
-We have all 400441 commits in our hand but though we can't plot them into a single time domain to assign different set of commits to different release periods because development goes in parallel on different branches in git, so commits also go in parallel.
-\begin{figure}
-\begin{center}
-\includegraphics[height=2.5in,width=2.5in]{gitdag.png}
-\caption{\small \sl Branching in git DAG for linux kernel development.}
-\end{center}
-\end{figure}
-If there are multiple branches, surely there are multiple merges and the commits prior to a crisscross merge are all ancestors of the heads of all subsequent branches \cite{bird_git}.
-Figure 1 shows how a git DAG looks like having so many crisscross merges in a busy branching snap-shot of the git DAG of Linux Kernel development.
-
-So it is possible to make a commit months ago from today while several releases may have already been made in the mean time but that commit can belong to any future release.
-Commits that are being made to a branch may get merged with other branch or the head branch during the release period.
-This is why we had to track all the way down the trees for each of the 340 releases in the git DAG to find out which commit contributes to which release.
-We could do this using Git DAG Traversing (GDT) algorithm as shown in Algorithm 1.
-After applying GDT we collected 381152 out of 400441 commits those are well organized in the git DAG of Linux Kernel development.
-As we mentioned earlier that we have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12''.
-We are chopping them out because we don't have complete commit records for version 2.6.12-rc releases as well as 3.12-rc releases.
-Out of 400441 commits 19289 are belonging to those releases.
-Therefore, finally we have 381152 commits for 331 releases in our database to progress our work on.
-\begin{algorithm}
-\caption{GDT: to find Commits within Releases}
-\begin{algorithmic}[1]
-\REQUIRE
-\STATE commit id for all releases
-\ENSURE
-\FOR{all commits}
-\STATE start from new commit, release R
-\STATE store commit in ``git\_commit\_release''
-\IF{has parent commit}
-	\FOR{each parent commit}
-		\IF{if parent commit has a release tag}
-			\STATE repeat step 1
-		\ELSIF{parent commit already stored}
-			\STATE compare release versions
-			\IF{release version not smaller than R}
-				\STATE update existing\_release $\gets$ R
-			\ENDIF
-		\ELSE
-			\STATE store parent commit in ``git\_commit\_release''
-			\STATE commit id $\gets$ parent commit id
-			\STATE repeat step 3
-		\ENDIF
-	\ENDFOR
-\ELSIF{no parent commit}
-	\STATE repeat step 1
-\ENDIF
-\ENDFOR
-\end{algorithmic}
-\end{algorithm}
-\subsection{Time-Span of Releases}
-Another information that we require is what are the durations of the releases of Linux kernel development.
-To achieve that we joined the table ``git\_refs\_tags'' where all the releases are stored including the exploited release numbers and the table ``git\_commit'' to give us all the dates of commits for each and every releases, so that we can easily find out the duration between two consecutive releases (including release candidates ``rc'').
-This information will significantly help us because we need to see what is the development period and what are the release periods within a release cycle.
-We also need to understand how developers are working, what is the impact of their changes made in the code-base during a particular release period later on.
-Table 1 shows a small portion of this information.
-Prior to calculate the developers' areas in section 4.4 we require this information.
-
-\begin{table}[ht]
-\caption{Different Releases}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Release & Type & Start Date & End Date \\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-linuxv2.6.12-rc2 & rc       & - & 2005-04-16 \\
-linuxv2.6.12-rc3 & rc       & 2005-04-16 & 2005-04-20 \\
-linuxv2.6.12-rc4 & rc       & 2005-04-20 & 2005-05-07 \\
-linuxv2.6.12-rc5 & rc       & 2005-05-07 & 2005-05-24 \\
-linuxv2.6.12-rc6 & rc       & 2005-05-24 & 2005-06-06 \\
-linuxv2.6.12        & micro & 2005-06-06 & 2005-06-17 \\
-linuxv2.6.13-rc1 & rc       & 2005-06-17 & 2005-06-29 \\
-linuxv2.6.13-rc2 & rc       & 2005-06-29 & 2005-07-05 \\
-linuxv2.6.13-rc3 & rc       & 2005-07-05 & 2005-07-13 \\
-...			     & ...	   & ... 		     & ...\\
-...			     & ...	   & ... 		     & ... \\
-...			     & ...	   & ... 		     & ... \\
-linuxv3.11            & minor & 2013-08-25 & 2013-09-02 \\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-
-Note that the very first row has no information for the ``Start Date'' because we don't have the  complete information prior to stable release ``linuxv2.6.12'' and we have chopped them out.
-This will not affect our methodology and measurements.
-From the extraction we found complete records for releases ``linuxv2.6.13'' to ``linuxv2.6.39'' then it is ``linuxv3.0'' to ``linuxv3.11''.
-Our farther works will be proceeded based on these 39 releases only.
-As we don't have the complete release information for 3.12 or later as well as for 2.6.12 and earlier ones.
-
-\subsection{Calculate Developers' Area}
-Developers are working throughout the release time.
-Here ``Developers' Area'' means the files developers work in within a release cycle.
-It doesn't refer to the file itself but it is important to understand which files are being touched by which developers.
-We see that authors are committing files almost everyday throughout a release but this does not make sure that these commits are going to the next release because commits are being made in different branches and all branches are not supposed to get merged to the next release.
-We have the commit log data in our hand and we know what is the duration for each and every release (i.e.\ start and end dates).
-Now it is possible to find out which commits were made for which files by which developer within a certain time range of a release.
-
-A relatively straightforward discipline of Linux Kernel Development team is followed with regard to the merging of patches for each release \cite{linux_kernel}.
-At the beginning of each development cycle, the "merge window" is said to be opened.
-At that time, code which is deemed to be sufficiently stable (and which is accepted by the development community) is merged into the mainline kernel.
-The bulk of changes for a new development cycle (and all of the major changes) will be merged during this time, at a rate approaching 1,000 changes ("patches," or "change-sets") per day.
-Strategically Linux starts a new kernel release with the merging to get their development branch ready to start development for the next release.
-So there are two main segments in a release period, one is merge window or development period (DP) where all the developments works get merged together from different branches.
-So we can say this is the main development period of a release.
-A development period remains opened exactly for two weeks \cite{linux_kernel}, many developers are working in many other branches to develop new features once they are ready to push it to the main kernel then they wait for the upcoming merge window and once it's development period they all contribute their works for the next release during this Development Period.
-Some developers who are mainly responsible to merge new developments verify and accept the new changes and merge them into the main kernel.
-Another perod in a release cycle is the period of candidate releases which gets opened once the merge window is closed where mainly the bug fixing of minor enhancement works are to be worked on and pushes by small candidate releases.
-Once all the fixing and enhancements are done for all the codes that had been merged into the main kernel, the release is published.
-We are calling this part of a release cycle as the release period (RP) because no new feature development works get accepted during this time, it is just the period prior to publishing a new release.
-
-\subsubsection{Developers' Area in a Development Period}
-Development Period can be determined from the previous release date (of any of major, minor or micro releases) to the date of rc1 (i.e.\ date of the first candidate release).
-For example if the date of release for ``linuxv2.6.12'' is 2005-06-17 and date of pushing the rc1 for the next release ``linuxv2.6.13'' is 2005-06-29 then this time period of of 12 days is going to be called as the merge window or development period.
-Thousands of commits get pushed in the main branch during this period.
-Table 2 shows the development periods of some releases.
-
-\begin{table}[ht]
-\caption{Development Periods (Merge Window)}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Release 			& Start Date		& End Date \\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-linuxv2.6.13		& 2005-06-17	& 2005-06-29 \\
-linuxv2.6.14		& 2005-08-28	& 2005-09-12 \\
-linuxv2.6.15		& 2005-10-27	& 2005-11-11 \\
-linuxv2.6.16		& 2006-01-02	& 2006-01-17 \\
-linuxv2.6.17		& 2006-03-20	& 2006-04-02 \\
-linuxv2.6.18		& 2006-06-17	& 2006-07-06 \\
-linuxv2.6.19		& 2006-09-19	& 2006-10-04 \\
-linuxv2.6.20  		& 2006-11-29	& 2006-12-13 \\
-linuxv2.6.21		& 2007-02-04	& 2007-02-20 \\
-linuxv2.6.22		& 2007-04-25	& 2007-05-12 \\
-linuxv2.6.23		& 2007-07-08	& 2007-07-22 \\
-linuxv2.6.24		& 2007-10-09	& 2007-10-23 \\
-linuxv2.6.25		& 2008-01-24	& 2008-02-10 \\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-
-We have the commits contributed to releases and every record explains us who committed the file when did this get churned.
-If we run an SQL query then we can easily find out for every author and for every particular file how many times a it has been committed by an author and how many churns (addition + deletion = churn) developer has made.
-We calculate developers' working areas and store the information into a table.
-A part of that table is shown in table 3.
-
-\begin{table}[ht]
-\caption{Developers' Areas in Development Period}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Author		& File Path			& Commits		& Churn \\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-D. S. Miller	& include/.../pci.h		& 1				& 8 \\
-V. Hanquez	& arch/.../cpu.c		& 1				& 14 \\
-A. Bunk		& drivers/.../shmem.c	& 1				& 2 \\
-J. Juhl		& arch/.../generic.c		& 1				& 3 \\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-
-In this table we see in a development period within a release cycle D.
-S.
-Miller has made change in pci.h file only once where he has made 8 churns.
-In the similar approach we calculate developers' areas in release period and also for development period.
-
-\subsubsection{Developers' Areas in Release Period}
-As like development period we can extract developers working in code files during release period.
-Release Period here in Linux Kernel development process is being considered as since the date of rc1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the date of the next stable release.
-For example if the date of rc1 for ``linuxv2.6.13'' after releasing ``linuxv2.6.12'' is 2005-06-29 and the date of publishing the release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the Release Period.
-Table 4 is showing some development periods of different releases.
-
-\begin{table}[ht]
-\caption{Release Periods}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Release 			& Start Date		& End Date \\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-linuxv2.6.13		& 2005-06-29	& 2005-08-28 \\
-linuxv2.6.14		& 2005-09-12	& 2005-10-27 \\
-linuxv2.6.15		& 2005-11-11	& 2006-01-02 \\
-linuxv2.6.16		& 2006-01-17	& 2006-03-20 \\
-linuxv2.6.17		& 2006-04-02	& 2006-06-17 \\
-linuxv2.6.18		& 2006-07-06	& 2006-09-19 \\
-linuxv2.6.19		& 2006-10-04	& 2006-11-29 \\
-linuxv2.6.20  		& 2006-12-13	& 2007-02-04 \\
-linuxv2.6.21		& 2007-02-20	& 2007-04-25 \\
-linuxv2.6.22		& 2007-05-12	& 2007-07-08 \\
-linuxv2.6.23		& 2007-07-22	& 2007-10-09 \\
-linuxv2.6.24		& 2007-10-23	& 2008-01-24 \\
-linuxv2.6.25		& 2008-02-10	& 2008-04-16 \\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-
-These information above will greatly help us to answer our first couple of research questions and to progress our further works.
-
-\subsection{Finding Code Ownership}
-So many developers are working from different development communities throughout different development branches.
-We tried to investigate the "code ownership" \cite{mockus_case_study} evolved in Linux Kernel development.
-Here code ownership is going to be represented as a percentage of making churns by a developer with respect to the total churns made to a particular file.
-From the data that we have for complete releases (``linuxv2.6.13'' to ``linuxv3.11'') we found 70210 distinct files that have been churned by developers.
-We removed those files where no developer made any churn at all during these 39 releases.
-We investigate the total number of churns for each and every file, we also investigate how many developers contributed for these commits and changes.
-This information yet does not tell about the ownership, we need to find out ownership for each developer in different development areas in a release cycle.
-We already have the collection of developers working in development period and release period within a release cycle and stored them with corresponding files they have worked on, how many commits a developer made to a particular file and how many changes he/she has made.
-We now update those information with the ownership information.
-Equation 1 is the base for calculating ownership.
-\begin{equation}\omega=\frac{n}{N}*100\end{equation}
-Where $\omega$ is the ownership and n is the number of total changes made by an atuthor of a file, N is the total number of changes made for a particular file.
-To determine a developer be a owner of a file we are considering that if the developer makes changes more than 80\% of the total churn that has been made by all contributors so far for that file, then that developer can be called as a owner of that file, similarly as C.
-Gutwin did \cite{gutwin_awareness} for finding out the main developers' group for a project.
-We calculate code ownership for both Development Period and Release Period.
-We also calculate general ownership for all the developers for all the files they have worked ever.
-Table 6 represents a part of the data which shows the ownerships of the developers in each release cycle.
-
-\begin{table}[ht]
-\caption{Code Ownership in Release Period}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Author 				& Linuxv		& Path				& $\omega$ (\%) \\ [0.5ex]
-\hline 							% single horizontal line
-% inserting body of the table
-Thomas Gleixner		& 2.6.24		& .../numa\_64.h	& 0.0000\\
-Jeff Kirsher			& 3.1		& .../ethtool.c		& 0.0000\\
-Sathya Perla			& 2.6.29		& .../hwlib.h		& 100.00\\
-Roel Kluin			& 2.6.24		& .../innovator.h 	& 100.00\\
-David S. Miller		& 2.6.24		& .../visasm.h 		& 100.00\\
-Stephen Hemminger	& 2.6.24		& .../qla3xxx.c	 	& 12.083\\
-Randy Dunlap			& 2.6.24		& ...\_core.c 		& 100.00\\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-The example given above is calculated for finding ownerships of developers worked for different files in different releases.
-Ownership is calculated for all the developers in release periods as well as in development period.
-In addition we have calculated which file is owned by which developer and also the percentage of working with owned files during development and release period separately.
-These extractions will help us drawing the results from our findings to answer our 3rd and 4th research questions.
-
-\section{Results}
-In this section we present results from several quantitative analysis of the archival data from the Linux Kernel development project.
-The measures we derive from these data are well-suited to answer our research questions.
-
-\textit{What is the release process used by the project?}
-
-In the early 1990's the Linux kernel development was not so busy affair \cite{linux_kernel}.
-There were very small number of users and developers involved at that time.
-Developers use a loosely time-based release process.
-Linux publishes it's major kernel release in every two or three months.
-If we look at figure 2 the upper Line represents how the stable releases are going on since 2005.
-From the figure we can see the average duration of each stable release is 62.47 although ``linuxv2.6.24'' was significantly hight as exception, it took 92.8 days.
-The bottom line which is much steady than the upper one is representing the durations of development period in each stable release.
-If we put the releases in a time domain we can see a picture shown in figure 2 where we see that the stable releases are all going on maintaining almost a similar frequency and similar pattern.
-The highest picks are the development periods then the smaller picks between the highest ones are representing the rc releases.
-For more clear view we have plotted only 100 releases of all 331 releases including rc candidates.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{relTimeDomain100.png}
-\caption{\small \sl Time Domain for Releases}
-\end{center}
-\end{figure}
-
-Linux Kernel development uses Rolling Release Development Model.
-Usually every micro release (ex.\ linuxv2.6.x) is a major kernel release with new features, internal API changes, and more.
-A minor release (ex.\ linuxv3.11) can have around 10 thousand change-sets with several hundred thousands of churned lines of codes (LOC).
-At the beginning of each stable release the merge window i.e.\ development period gets opened and all the accepted and stable codes from the community are merged having around 1000 of churns everyday.
-Development period approximately for 14 days as shown in the figure 3.
-The bottom line is representing the merge windows of every releases.
-We don't have the development period data for the very first one that's why it's starting from 0.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{linxrelmergfreq.png}
-\caption{\small \sl Durations of Merge Window and Release Cycle}
-\end{center}
-\end{figure}
-
-After getting all the major works merged, release period for the next release is announced to be opened.
-If the next release is going to be linuxv2.6.14 then the release pushed out at the end of the merge window will be called linuxv2.6.14-rc1.
-\textbf{-rc1} indicates that all the new features or developments are merged now the time to stabilize the next kernel has begun.
-These candidate releases continue to be pushed for once a week.
-If there is any bug fix or any high-priority change only then that goes to the main line during this period.
-With the continuous rc releases when the new kernel seems to be stable then it goes to publish the next stable release.
-Again merge window gets opened and accepts more new features, patch-sets from different branches.
-
-As a summary, the description above helps us to address some of the questions about how Linux Kernel development is organized.
-Answer to this first research question provides essential background for understanding our quantitative results.
-We will look into more detail of the development process, distribution of developers among the release segments as well as will try to find answers for our other research questions in the next sections.
-
-\subsection{Difference Between Release Segments}
-\textit{How many developers are allocated troughout different segments of a release period? What significant difference can be observed between the segments of an entire release period?}
-
-In order to see how many developers contribute to the new feature developments and how many contribute in merging and fixing, review and accepting codes from the community during the development period, we observed the developers' area in Development Period and developers' area in Release Period.
-Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of development period which is 76.85\% (more than 2/3) of the total.
-These commits were made by 13926 individual developers.
-We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for these releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later.
-11209 developers work in development period and 7625 developers work around the release period.
-
-In figure 4 we see the boxplot showing that a very large number of developers contribute during the development period which is in a sense the main development period because all the development branches get merged together during this time, all the new features come into the main branch of the kernel.
-In release period significantly small number of developers work and this number looks pretty steady for all the releases only a couple of high number appeared in two releases as we see in figure 4.
-The number of contributions during the main development period over releases looks going up in an increasing manner as shown in figure 5.
-On the other hand the bottom line for the release developers is pretty steady for all the releases.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{devsMPRPbox.png}
-\caption{\small \sl Developers working in DP \& RP}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{devsMPRP.png}
-\caption{\small \sl Increasing contribution in DP}
-\end{center}
-\end{figure}
-
-Once we found different releases and the release periods as well as we calculate the developers' areas and code ownerships for developers we also would like to know what is the difference being created by making changes between the two main segments within an entire release development cycle (i.e.\ Development Period DP and Release Period RP).
-To observe this we want to calculate the difference using Jaccard Similarity Coefficient \cite{jaccard_alpine} which is represented by equation 3.
-\begin{equation} J(A, B) =\frac{|A \cap B|}{|A \cup B|} \end{equation}
-The Jaccard Distance can be obtained by subtracting the Jaccard Coefficient from 1.
-\begin{equation} d_j(A, B) = 1 - J(A, B) = \frac{|A \cup B|-|A \cap B|}{|A \cup B|} \end{equation}
-Here A and B are two sets.
-For calculating Jaccard distance between two releases we are considering the files that have been worked for, in a particular release.
-If set A is the set of files worked in DP and files worked for in another release is set B then In figure 6 the Jaccard distances between Development Period and Release Period for each release can be represented.
-The average jaccard distance between development period and release period for all the release cycles is 0.85 and we see the Jaccard distance is also going upward by releases except the only exception at release 2.6.34.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{jdMPRP.png}
-\caption{\small \sl Jaccard Distance between the Development Period and Release Period}
-\end{center}
-\end{figure}
-
-\subsection{Developers' Contributions Around the Time of Release}
-\textit{Do developers work on different areas of the system around the time of release?}\newline
-\textit{Do developers work in others' code in a high proportion during the rush period?}
-
-We are supposed to find the answers for the two research questions together in this section.
-Developers work for the software continuously.
-Some are working for the core development some people are for the fixing and minor enhancements and some for feature developments, planning to merge new features with any up coming release but we would like to understand what number of files they change during the time of development and merging period and how many during the release period.
-How many of them they really own and how many files they work that they do not own.
-We also want to know about the code ownership of the developers around the time of release as well as around the time of main development works that get merged during development period.
-
-In order to understand the distribution of the developers around the system we also found that during these release periods 11209 developers have experience of working in the development period and 7625 developers worked in the release period as we already mentioned earlier but we noted that 4908 developers contribute in both development period and the release period that means near about half (43.78\%) of the developers work during the development period are shared that means they work for core developments and also bug fixing or minor enhancement works.
-Figure 7 representing the venn diagram.
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.3in,width=2.3in]{devDistMPRPvenn.png}
-\caption{\small \sl Developers' Distribution in Development Period and Release Period}
-\end{center}
-\end{figure}
-
-From release ``linuxv2.6.13'' to ``linuxv3.11'' We examine the contribution in writing code by the developers to understand the behavior during the two vital segments in a release cycle.
-Figure 8 plots the cumulative representation of the percentage of working with owned files ($\omega$\textit{MP}) during the development period and the percentage of working with owned files ($\omega$\textit{RP}) during release period of ``linuxv2.6.13''.
-From the figure It can be observed that with the increase of every 10 files that developers working in, $\omega$\textit{RP} is going down apart from the line of $\omega$\textit{MP}.
-Up to a certain number may be around 2200 files developers mostly work with owned files.
-We see the similar picture for other releases too.
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{cumulFileOwnP.png}
-\caption{\small \sl Cumulative percentage of working with owned files in DP and RP of release 2.3.13}
-\end{center}
-\end{figure}
-
-If we simply compare the percentage of working in owned files during development period ($\omega$\textit{MP}) and the percentage of working in owned files during release period ($\omega$\textit{RP}) for each developer then we see a significant difference of the mean lines as shown in figure 9.
-In release period developers work with less number of files that they own.
-
-So we can say that in Linux Kernel development developers work in more unfamiliar files during the release period.
-Before the release period main development works are accepted from different branches and they get merged together with main kernel, so, core feature developers finishes their duty for a particular feature development for a particular release within the time of development period although some contributors still work during the release period where basically they work on fixing, testing and minor enhancement related work on the codes that have been merged and accepted from various developers from other branches.
-It is clear now that during the release period developers work mostly on others' works, the proportion of working with owned files is lower around the release than the proportion during normal development time.
-When they feel the confidence that everything is tested and can be pushed out for the release, they publish the stable release.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3in]{ownpMPRPbox.png}
-\caption{\small \sl Percentage of working in owned files during Development Period and Release Period}
-\end{center}
-\end{figure}
-
-So, finally we can say that in development periods developers work in more native codes while during the regular release development period the percentage of working with native code is very low in number although this percentage of working in owned code during development period does not significantly relate to other co-factors.
-
-\subsection{Time for Commits to Go Live}
-\textit{How long a commit takes to get pushed into the main kernel? Does it differ in different periods of release?}
-
-There are thousands of commits goes to the main kernel during the merge window.
-All they are to be considered as the normal development commits or regular development or core development commits for developing new features to the kernel.
-Merge window remains opened for two weeks only, the development works that are supposed to go for a particular release are not developed during this couple of weeks.
-These have been developed since many days ago on a different development branch by any developer.
-For a particular feature that is going to the current release there are hundreds of commits, obviously all these commits are not made during the merge window of the current release 90-100\% commits must have been made before the opening of the merge window of current release.
-As described in section 4.3, we have sorted up the releases according to the git DAG.
-This helps us to calculate how many days in past the first commit of this particular feature had been made which is going to be pushed into the current release.
-The duration a commit was made to the local branch to the date it is pushed into the main branch is being called here ``lag'' of commits.
-Figure 10 represents lag of the commits made for regular development and lag of the commits made during the release period.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3in]{lagMPRPbox.png}
-\caption{\small \sl Time takes for development commits and commits around release periods to get released}
-\end{center}
-\end{figure}
-
-From figure 10 we can understand it easily that rather quick fixes are made during the release period.
-With the small sets of bug fixes, important quick enhancements candidate releases are pushed continuously within short period lengths of time and once the kernel seems to be more stable with all the new features that has been merged during the beginning of the release cycle, the stable release is published.
-Comperatively lag for the feature development commits is quite high.
-Median for the lags for the commits during this time is 5.57 while median of the lags for the commits going to the main kernel of the development  period is 26.15, which is a significant different between these two parts of a release cycle.
-
-\subsection{Developers' Focus on Code-Base Around the Time of Release}
-\textit{Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?}
-
-To answer this research question we are interested to find answer to the following questions first.
-\renewcommand{\labelenumi}{q\theenumi:}
-\begin{enumerate}
-\item{How many churns were made to the files during release periods?}
-\item{How many files get churns exceptionally high in number? Do we see this in every release cycles?}
-\item{How many files each developer deals with during release development period?}
-\item{How many files developer deal with large number of files during release development period?
-What is the percentage of ownership of them while working for a large number of files in a release period?}
-\item{If there is any area that requires increased attention in the system, then what is the Jaccard distance of those areas throughout different releases?
-Are they being focused iteratively by releases?}
-\end{enumerate}
-
-During the time of rc releases after all the merging jobs are done developers generally work for minor fixing and serious quick enhancements.
-In all these 39 release cycles of Linux Kernel development wee see in an average 3077 churns are made around the releases.
-The minimum value is 1691 and maximum is 8669.
-Median and mean values are closer enough (2668 and 3077) to say that almost similar kind of churns are made in all the release periods except couple of exceptions.
-If we look at figure 11 then where the normalized distribution of this data is represented then we can easily understand.
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3in]{churnRPnorm.png}
-\caption{\small \sl Normal distribution of churns per Release Period}
-\end{center}
-\end{figure}
-
-We analyzed in several releases and found that for the release ``linuxv2.6.13'' 2938 files got churned.
-Among them only five files had exceptionally high number of churns four of them have more than 10,000 churns.
-Similar picture we see for other releases also.
-Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high and being marked as outliers as shown in figure 12.
-For almost every release cycle during the release period around 2.846 files get highly increased attention having over 5000 churns and 16.78 files having over 1000 churns as shown in figure 13.
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3in]{fileChurnRPbox.png}
-\caption{\small \sl Number of Files churned in release periods}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3in]{fileChurnRPExp1000vs5000box.png}
-\caption{\small \sl Files churned more than 1000 times and more than 5000 times during release period}
-\end{center}
-\end{figure}
-
-During the release period developers deal with various files came from different authors working in different development branches in merge window.
-Although the number of files developers deal with during release period is too low (mean 5.52) there is a large number of developers work for around 50 files.
-To look for how many developers work for fairly large number of files we decided to see which developers work for more than 100 files in the release periods.
-
-We found that there are 29 releases out of the 39 where developers are working in comparatively large number of files during the release period?
-Among them we noted that 5 developers in 5 different release periods worked for extremely high number of files as listed in table 6.
-In this table we also have represented what is the percentage of working with owned files for each developer.
-
-\begin{table}[ht]
-\caption{Developers making churn in extremely high number of files during Release Periods}  % title of Table
-\centering 						% used for centering table
-\begin{tabular}{c c c c}				% centered columns (4 columns)
-\hline\hline						%inserts double horizontal lines
-% table heading
-Author 						& Linuxv		& Owned 			& Total \\
-							& 			& Files				& Churned \\ [1ex]
-\hline 							% single horizontal line
-% inserting body of the table
-Greg Kroah-Hartman			& 3.8		& 70\%				& 1114\\
-David Howells				& 2.6.19		& 38\%				& 1140\\
-Russell King					& 2.6.27		& 70\%				& 2426\\
-Lucas De Marchi				& 2.6.39		& 64\% 				& 2466\\
-Tejun Heo					& 2.6.34		& 34\% 				& 4222\\
-[1ex]							% adds vertical space
-\hline 							% inserts single line
-\end{tabular}
-\label{table:nonlin} 				% is used to refer this table in the text
-\end{table}
-
-So, we can say that there are certain areas of the system that takes certainly increased attention also there are few developers who deal with extremely large number of files at the time of release.
-Some of them work less than 40\% files that they own and some developers work around 70\% of files that they own.
-Now we would like to see if these areas having increased attention get the similar attention in other releases.
-This finding also supports our fourth research question \textit{RQ4} strongly.
-In this occasion we would like find the Jaccard similarity index for these areas in consecutive releases.
-First we collected the sets of files those are having highly increasing focus during the release periods of different release cycles.
-Then we calculated the union and intersection operation between two consecutive sets as well as randomly.
-We applied equation 2 to find out the similarity among the sets and we see there is no similarity between those sets except for couple of pairs of releases like linuxv2.6.14~linuxv2.6.15, linuxv2.6.29~linuxv2.6.30, linuxv2.6.30~linuxv2.6.31 and linuxv2.6.34~linuxv2.6.35 where the similarity index is too low to say similar; they are 0.038, 0.066, 0.025 and 0.181 respectively as shown in figure 14.
-From this we understand that developers working for different and various features, developing new staffs for Linux kernel working in many different files and merging them into the main kernel during merge window.
-In release period small number of developers who are allowed to work in release period are reviewing those newly arrived codes and doing quick fixes and enhancements, some of them may require very high attention and more work to do.
-In the next release some other different new developments arrive in merge window and thus in release period developer do their candidate releases focusing on those newly arrived code files which are not related to the code files those had to get high focus in the previous release.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=1.7in,width=3.4in]{jdRPHighFocusFiles.png}
-\caption{\small \sl Jaccard similarity index between consecutive sets of files having highly increased focus in different releases}
-\end{center}
-
-\end{figure}
-\section{Threats to Validity}
-Throught the paper we have done number of measurements to analyze the structure of an OSS software project development, behavior of the developers in different parts of the system, allocation and re-allocation of resources around the time of release and around the time of development.
-The results have been reported with respect to our research questions in this case study.
-We reported following items by our measurements:
-\renewcommand{\labelenumi}{\theenumi.}
-\begin{enumerate}
-\item{The basic structure and the development process of Linux Kernel.}
-\item{The distribution of developers in two different segments in a complete release cycle.}
-\item{Role of developers during development period and the significance of release period.}
-\item{Developers' focus around the time of release, percentage of working with native code during development period and release period.}
-\end{enumerate}
-Now, are these measurements and findings really meaningful, are they quantifying what we want them to?\newline\newline
-\textbf{Construct Validity} To study the distribution and allocation of developers or resources around the development system for a large project, the very initial step should be understanding the project development strategy which project data we are studying on.
-Looking for the answer to our first research question is an obvious in this context where we clearly understood the history and flow of the development process of Linux Kernel, what are the durations of every release how can we distinguish different parts within a release cycle and so on.
-Once we get the different segments or distinguishable parts of a release cycle we feel the urgency to understand their external and internal behaviors also the relation of the resources, role of developers around them.
-Our second research question tells us every details on these and our third, fourth and fifth research questions take us more into the deep of this analysis to discover some core points of information from where we may start thinking of something different that may help us to progress our work farther more by setting any goal based on new hypothesis to come up with any decision.
-Our last research question is really giving us some meaningful discoveries to plot the critical true scenario of developers with code-base of a project.\newline\newline
-\textbf{Internal Validity} Is there any cause and effect relation between the changes in certain attributes and the results that we represented?
-In our methodology we actually picked few attributes like version of the release, sable release and candidate release, release commits, different periods within a release cycle like merge window or development period and release period, ownership, lag for commits in different periods, percentage of working with owned files during development and release periods, file churns, highly increasingly focused files, Jaccard distance between the sets of files of these types.
-The first attribute ``versions'' may vary with many other software projects so the data extraction model that we have used may not me similar to other projects but the GDT algorithm that we have used for acqumulating the commits associated to releases will be useful for other software projects having Git as the version control system.\newline\newline
-\textbf{External Validity} As our aim is to understand the allocation and re-allocations of the resources around the release of a software project we wanted to make a study with a large project and so we started our study with Linux Kernel development where we got approximately 400441 commit records made by thousands of developers for 340 releases (including stable and candidates).
-Can we generalize our results to other software projects?
-Although we looked into a large open source software, this is only one system we looked into.
-We need to analyze the development strategy and distribution of resources for others software projects also.
-We have plan to go for similar kind of analysis on other historical projects both OSS and non-OSS to generalize our findings and results by cross-validation across projects.\newline\newline
-\textbf{Reliability} The data we used for our study is highly reliable.
-It has been derived from the version control system that Linux Kernel development using.
-Other projects using similar version control system can easily run the same experiments to produce findings specific to those projects and to compare with our findings.\newline\newline
-\textbf{Limitations} The results and findings of our study is currently based on a single project due to the limited access to such rich historical data.
-We hope to study more other OSS projects as well as non-OSS projects to ensure the validity and generality of our findings in the future.
-
-\section{Conclusions}
-Software development in a large team is really a complex process to deal with.
-Resource re-allocation is an important phenomenon in regard of software development especially in a large development environment.
-We were aiming to find out some points of crucial information that may lead us to move forward to come up with any new hypothesis or any decision about the rush period of release and the distribution of developers having in-equal hold on the code-base of the system which is strongly related to the disruptive events occur in software development industries.
-We also were concerned about the dead areas of the system that often creates technical debts and we could see in our results that files having highly focus around the release periods are being handled by developers who may have high percentage of familiarity with them or may have pretty low but we did not find those files to be worked on in further releases.
-This may be due to those codes files are developed in such a way that they never require any fix or any new feature cannot be implemented based on them or new developers have no idea about those files which makes them not to touch those files rather make them interested to create new files for new works.
-We would like to investigate these matters in future to come up with more significant discoveries possibly with new decisional ideas about the disruptive events of software systems.
-
-%\end{document}  % This is where a 'short' article might terminate
-
-\bibliographystyle{abbrv}
-\bibliography{paper1}
-
-\balancecolumns
 \end{document}

### 2013-12-17 paper1/latex/paper1.tex
tarted working on reviews from Peter.

@@
 Figure 8 plots the cumulative representation of the percentage of working with owned files ($\omega$\textit{MP}) during the development period and the percentage of working with owned files ($\omega$\textit{RP}) during release period of ``linuxv2.6.13''.
-From the figure It can be observed that with the increase of every 10 files that developers working in, $\omega$\textit{RP} is going down apart from the line of $\omega$\textit{MP}.
+From the figure it can be observed that with the increase of every 10 files that developers working in, $\omega$\textit{RP} is going down apart from the line of $\omega$\textit{MP}.
 Up to a certain number may be around 2200 files developers mostly work with owned files.
